### 2017-08-05 Source/Examples/form_triplet_motifs.Rmd
Add all current files

---
title: "Form Triplet Motifs"
author: "Ignatius Pang"
date: "8 May 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
library(plyr)
library(dplyr)
library(purrr)
library(tibble)
library(tidyr)

## Load the root base directory for the entire project
source( "./Common/parameters_file.R")

data_directory <- file.path( base_directory, "Data/Triplet_Motifs_R_data")

load( file.path(data_directory, "network_data_library.Rdata"))

source( file.path(base_directory, "Source/Common", "count_triplet_motifs_helper.R"))

```

```{r}

# Genetic interactions network table

filtered_costanzo_stringent <- filtered_costanzo_stringent_2016 %>% 
								dplyr::select( one_of( c( "query_oln_id_edited", "array_oln_id_edited", "genetic_interaction_score"))) %>%
								dplyr::rename( node_a = query_oln_id_edited, node_b= array_oln_id_edited )

# Re-arrange the edges such that the ID of node A is always greater than ID of node B
# This removes the symmetry in the triplet motif dataset 
a_gt_b <- dplyr::filter( filtered_costanzo_stringent, node_a >= node_b   )

b_gt_a <- dplyr::filter( filtered_costanzo_stringent, node_b > node_a   ) %>%
		  dplyr::rename( node_a=node_b, node_b=node_a )

# If the genetic interaction has been screen more than once, get the least negative score for that interaction
filtered_costanzo_stringent <- dplyr::union( a_gt_b, b_gt_a) %>%
							   dplyr::group_by( node_a, node_b) %>%
							   dplyr::summarise(max_gi_score = max(genetic_interaction_score) ) %>%
							   dplyr::rename( genetic_interaction_score=max_gi_score) %>%
							   dplyr::ungroup()

head( filtered_costanzo_stringent )

# Count the unique number of proteins in triplet motifs
length ( unique(  c(as.vector(as.data.frame(filtered_costanzo_stringent)[, "node_a"]) , 
					as.vector (as.data.frame( filtered_costanzo_stringent)[, "node_b"] )) ) )

```

```{r}
# All other biological networks, protein-protein, kinase-substrate, transcription factor-target gene
head( interactions_combined)

# Rename the tables
interactions_combined_1 <- interactions_combined %>%
							dplyr::rename( node_a = oln_id_a, 
										   node_c= oln_id_b, 
										   type_ac_long = interaction_type,
										   type_ac = interaction_type_abbrev)

interactions_combined_2 <- interactions_combined %>%
							dplyr::rename( node_b = oln_id_a, 
										   node_c= oln_id_b, 
										   type_bc_long = interaction_type,
										   type_bc = interaction_type_abbrev )

```

Total number of proteins in the integrated network
```{r}

list_of_proteins_genetic_interactions <-	filtered_costanzo_stringent  %>% 
	tidyr::gather( "node", "oln_id", 1:2) %>%
	dplyr::select ( -node) %>%
	dplyr::select ( -genetic_interaction_score) %>%
	distinct()

list_of_proteins_physical_interactions <- interactions_combined  %>% 
	tidyr::gather( "node", "oln_id", 1:2) %>%
	dplyr::select ( -node) %>%
	dplyr::select ( -interaction_type) %>%
	dplyr::select ( -interaction_type_abbrev) %>%
	distinct()

total_number_of_proteins_integrated_biological_newtork <-    list_of_proteins_genetic_interactions %>% 
	rbind ( list_of_proteins_physical_interactions ) %>%
	distinct () %>%
	count()

total_number_of_proteins_integrated_biological_newtork

```

```{r}
## Join the networks together to find triplets where at least one edge is a negative genetic interaction

				  # Join the genetic interaction to the other biological networks
triplet_motifs <- dplyr::inner_join( filtered_costanzo_stringent, interactions_combined_1, by="node_a" )  %>%
						# Closing the triplets with a third edge from the other biological networks 	
					    dplyr::inner_join( interactions_combined_2, by=c("node_b"= "node_b", "node_c"= "node_c") ) %>%
						# Select the corresponding columns
					    dplyr::select ( one_of( c("node_a", "node_b", "node_c", "type_ac", "type_bc", 
					    						  "type_ac_long", "type_bc_long", "genetic_interaction_score"))) %>%

						# Remove special cases where Node A == Node C or Node B == Node C
						dplyr::filter ( node_a != node_c) %>%
						dplyr::filter ( node_b != node_c) %>%

						# Remove duplicates
					    dplyr::distinct() %>%

						# Arrange the columns in the order that I want 
					    dplyr::arrange( node_a, node_b, node_c, type_bc, type_ac)

triplet_motifs

## Count the number of motifs
nrow( triplet_motifs)

triplet_motifs %>%
	dplyr::select( one_of ( c( "node_a", "node_b", "node_c", "type_ac", "type_bc", "genetic_interaction_score"))) %>%
	write.table ( file.path( list_of_triplets_directory,  "triplet_motifs_costanzo_2016.txt"), sep="\t", quote=FALSE, row.names = FALSE )

```

```{r}

# Count the number of each type of triplet motifs

# Count the cases where type_ac is greater than type_bc (e.g. string comparison)
a_ge_b <- filter( triplet_motifs, type_ac >= type_bc ) %>%
		group_by( type_ac, type_bc) %>%
		summarise(counts=n())

# Count the cases where type_bc is greater than type_ac (e.g. string comparison)
b_gt_a <- filter( triplet_motifs, type_bc > type_ac ) %>%
		group_by( type_ac, type_bc) %>%
		summarise(counts=n()) %>%
		rename ( type_ac= type_bc, type_bc = type_ac) %>%
		select( one_of( c("type_ac", "type_bc", "counts") ))

# Merge the above results together
triplet_motif_counts <- dplyr::union( a_ge_b, b_gt_a)  %>%
		group_by( type_ac, type_bc) %>% 
		summarise(total_count=sum(counts)) %>%
		arrange( type_ac, type_bc)

# Here is the final results
triplet_motif_counts

dim( triplet_motif_counts)

triplet_motif_counts <- as.data.frame(triplet_motif_counts)

triplet_motif_counts  <- mutate( triplet_motif_counts, motif_type = paste(type_ac, type_bc, sep="") )  %>%
						arrange ( desc(total_count))

triplet_motif_counts[, "motif_type"] <- factor ( as.vector(triplet_motif_counts[,"motif_type"]), levels=as.vector(triplet_motif_counts[,"motif_type"]))

library(ggplot2)

ggplot ( triplet_motif_counts, aes(motif_type, total_count)) + 
	geom_point()

```

Find the number of edges of each type in the triplet motifs network
```{r}

ab_interactions <- triplet_motifs %>%
					dplyr::select( one_of(c( "node_a", "node_b")))  %>%
					dplyr::rename( node_x = node_a, node_y = node_b) %>% 
					dplyr::mutate( type="gi")

ac_interactions <- triplet_motifs %>% 
	dplyr::select( one_of(c( "node_a", "node_c", "type_ac"))) %>%
	rename( type= type_ac, node_x = node_a, node_y = node_c)

bc_interactions <- triplet_motifs %>% 
	dplyr::select( one_of(c( "node_b", "node_c", "type_bc"))) %>%
	rename( type= type_bc, node_x = node_b, node_y = node_c)

# This function makes sure all of the interactions are in the same direction.
# This helps with removing duplicates. 
fix_interaction <- function ( interactions_list) {

	interactions_list <- setNames( as.list(as.vector(interactions_list) ), names( interactions_list) )

	if( ( interactions_list$type == 'p'  | interactions_list$type == 'gi'  | interactions_list$type == '') 
		& interactions_list['node_x'] < interactions_list$node_y ) {
		# perform swapping
		temp <- interactions_list$node_y
		interactions_list$node_y <- interactions_list$node_x
		interactions_list$node_x <- temp
	} else if  ( interactions_list$type == 'tu' ) {

		temp <- interactions_list$node_y
		interactions_list$node_y <- interactions_list$node_x
		interactions_list$node_x <- temp
		interactions_list$type <- "td"
	} else if  ( interactions_list$type == 'ku' ) {

		temp <- interactions_list$node_y
		interactions_list$node_y <- interactions_list$node_x
		interactions_list$node_x <- temp
		interactions_list$type <- "kd"
	}

	return( unlist( interactions_list )) ## Need to unlist it
}

ab_interactions_list <- as.list(as.data.frame(t(ab_interactions))) %>%
						map(fix_interaction)

ab_interactions <- ab_interactions_list %>%
					ldply() %>%    ## Convert back to a data.frame
					select ( -(.id)) %>% ## remove the .id column 
					distinct()

ac_interactions_list <- as.list(as.data.frame(t(ac_interactions))) %>%
						map( fix_interaction)

ac_interactions <- ac_interactions_list %>%
					ldply() %>% 
					select ( -(.id))

bc_interactions_list <- as.list(as.data.frame(t(bc_interactions))) %>%
						map( fix_interaction)

bc_interactions <- bc_interactions_list %>%
					ldply() %>% 
					select ( -(.id))

interactions_table <- bind_rows( ac_interactions, bc_interactions, ab_interactions) %>%
					  distinct()

## Total number of unique interactions in the network of triplets. Removing overlapping edges. Ignoring direction of edges
total_number_of_interactions_triplet_network_no_overlap_no_direction <- interactions_table %>% 
												mutate ( type = '') %>%
											    t() %>% as.data.frame() %>% as.list() %>%
												map( fix_interaction) %>%
												ldply() %>% 
												select ( -(.id)) %>% 
												distinct() %>%
												count()
total_number_of_interactions_triplet_network_no_overlap_no_direction

## Number of each type of interactions 
interactions_count_table <- interactions_table %>%
							group_by(type) %>%
							summarise ( num_interactions = n() )

### Total number of proteins 
total_number_of_proteins_in_triplets <-	interactions_table  %>% 
	tidyr::gather( "node", "oln_id", 1:2) %>%
	dplyr::select ( -node) %>%
	dplyr::select ( -type) %>%
	distinct() %>% 
	count()

### Number of proteins in each type of network
all_nodes <- interactions_table %>% 
	tidyr::gather( "node", "oln_id", 1:2) %>%
	dplyr::select ( -node) %>%
	distinct() %>% 
	group_by(type) %>% 
	count()

## Number of kinases in the triplet netwrok
interactions_table %>% 
	dplyr::filter ( type=='kd') %>%
	dplyr::select ( one_of ( c( 'node_x'))) %>%
	distinct()  %>%
	count()

## Number of transcription factors in the triplet netwrok
interactions_table %>% 
	dplyr::filter ( type=='td') %>%
	dplyr::select ( one_of ( c( 'node_x'))) %>%
	distinct()  %>%
	count()

```

Total number of interactions in the integrated network
```{r}

part_a <- filtered_costanzo_stringent %>%
	dplyr::select ( -genetic_interaction_score) %>%
	rename( node_x = node_a, node_y = node_b)

part_b <- interactions_combined %>%
	dplyr::select ( one_of(c('oln_id_a', 'oln_id_b'))) %>%
	rename( node_x = oln_id_a, node_y = oln_id_b)

part_a %>% rbind(part_b) %>% 
												mutate ( type = '') %>%
											    t() %>% as.data.frame() %>% as.list() %>%
												map( fix_interaction) %>%
												ldply() %>% 
												select ( -(.id)) %>% 
												distinct() %>%
												count()

total_number_of_interactions_triplet_network_no_overlap_no_direction <- interactions_table %>% 
												mutate ( type = '') %>%
											    t() %>% as.data.frame() %>% as.list() %>%
												map( fix_interaction) %>%
												ldply() %>% 
												select ( -(.id)) %>% 
												distinct() %>%
												count()
total_number_of_interactions_triplet_network_no_overlap_no_direction

```

Genetic interactions, number of edges, number of proteins
```{r}

filtered_costanzo_stringent_2016_cleaned <- filtered_costanzo_stringent_2016 %>%
	dplyr::select ( query_oln_id_edited, array_oln_id_edited) %>% 
					dplyr::rename( node_x=query_oln_id_edited, node_y = array_oln_id_edited) %>%
					dplyr::mutate( type="gi") %>%
					as.tibble() %>%
					t() %>%
					as.data.frame() %>%
					as.list() %>%
					map(fix_interaction) %>%
					ldply() %>% 
					dplyr::select ( -(.id)) %>%
					distinct()

# Get number of unique edges	
dim( filtered_costanzo_stringent_2016_cleaned)

# Get number of proteins
length( unique( c(filtered_costanzo_stringent_2016_cleaned$node_x,  filtered_costanzo_stringent_2016_cleaned$node_y) ))

```

Kinase substrate network 
```{r}

## Number of interactions in the kinase-substrate network
kinase_network_cleaned <- kinase_network_collated %>% 
	dplyr::filter( interaction_type_abbrev == 'kd') %>%
	dplyr::select( one_of(c('oln_id_a', 'oln_id_b'))) %>%
	distinct()

dim( kinase_network_cleaned)

## count the number of kinases
kinase_list <- kinase_network_cleaned %>%
	dplyr::select ( one_of ( c ( 'oln_id_a'))) %>%
	dplyr::rename( oln_id = oln_id_a) %>%
	distinct()

count(kinase_list )

## count the number of substrates

targets_list <- kinase_network_cleaned %>%
	dplyr::select ( one_of ( c ( 'oln_id_b'))) %>%
	dplyr::rename( oln_id = oln_id_b) %>%
	distinct()

substrates_excluding_kinases <- setdiff( targets_list, kinase_list)

count( substrates_excluding_kinases)

```

Protein interaction network
```{r}

sbi_interactome_cleaned <- sbi_interactome_collated %>% 
	dplyr::filter( oln_id_a > oln_id_b ) %>%
	dplyr::select( one_of(c('oln_id_a', 'oln_id_b'))) %>%
	distinct()

dim( sbi_interactome_cleaned)

length( unique( c(sbi_interactome_cleaned$oln_id_a ,  sbi_interactome_cleaned$oln_id_b )) )

```

Transcriptional regulatory network
```{r}

tf_network_collated

## Number of interactions in the transcriptional regulatory network
tf_network_cleaned <- tf_network_collated %>% 
	dplyr::filter( interaction_type_abbrev == 'td') %>%
	dplyr::select( one_of(c('oln_id_a', 'oln_id_b'))) %>%
	distinct()

dim( tf_network_cleaned)

## count the number of kinases
tf_list <- tf_network_cleaned %>%
	dplyr::select ( one_of ( c ( 'oln_id_a'))) %>%
	dplyr::rename( oln_id = oln_id_a) %>%
	distinct()

count(tf_list )

## count the number of substrates

targets_list <- tf_network_cleaned %>%
	dplyr::select ( one_of ( c ( 'oln_id_b'))) %>%
	dplyr::rename( oln_id = oln_id_b) %>%
	distinct()

targets_excluding_tf <- setdiff( targets_list, tf_list)

count( targets_excluding_tf)

## total number of proteins
length( unique( c ( targets_list$oln_id , tf_list$oln_id) ))

```

```{r}
# Odds ratio enrichment for transcriptional regulatory network.

fisher.test ( matrix (c(3156
,620
,26786
,2281), 2, 2))

1/0.4334889

```

### 2017-08-05 Source/Examples/print_all_motifs.Rmd
Add all current files

---
title: "R Notebook"
output: html_notebook
---

Script: print_all_motifs.R
Author: Ignatius Pang 
Date: 13-7-2016
Description: I want to convert each of the 15 triplet motifs into an edge list, so I can show them in Cytoscape and make pictures.

```{r}
library(RCy3)
library(dplyr)

# source_directory_common <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Common/"
source_directory_common <- "/home/ignatius/Documents/Postdoc/2016/Triplet_Motifs/Source/Common/"

source( file.path ( source_directory_common, 'draw_triplet_motif_network_helper.R') )

```

## Enumerate of all types of triplet motifs.
```{r}
types_of_edges <-  c( 'kd', 'ku', 'p', 'td', 'tu' )

triplet_motifs <- data.frame( type_ac = rep( sort(types_of_edges), 5) , type_bc= sort(rep( types_of_edges, 5) ), stringsAsFactors =FALSE ) %>%
					dplyr::filter( type_ac >= type_bc)

# Sort the motif types
triplet_motifs <- triplet_motifs %>% arrange( type_ac, type_bc)

# Determine the number of columns and rows for the edge list.
num_rows <- length(triplet_motifs[,1]) * 3 # Number of edges among all triplet motifs
num_cols <- 3 ## Total number of columns

## Initiate the matrix for the edge list
triplet_motif_figure <- data.frame(matrix(ncol = num_cols, nrow = num_rows))
colnames( triplet_motif_figure) <- c("gene_a", "gene_b", "interaction_type")

## Generate node names for the 15 types of triplet motifs. 
## On name for each node of the 15 types of motifs. Append letter 'a' to make sure there is enough motifs.
nodes_names <- c( letters, paste ( "a", letters, sep=""))
current_row <- 1

### Loop through the list of all possible motifs to create the edge list.
for ( i in 1:length(triplet_motifs[,1]) ) {

	current_letter_pointer <- (i-1)*3 + 1

	# a -- b edge of the triplet motif
	triplet_motif_figure[current_row, 1] <- nodes_names[current_letter_pointer]
	triplet_motif_figure[current_row, 2] <- nodes_names[current_letter_pointer + 1]
	triplet_motif_figure[current_row, 3] <- "gi"

	current_row <- current_row + 1

	# a --- c edge of the triplet motif
	triplet_motif_figure[current_row, 1] <- nodes_names[current_letter_pointer]
	triplet_motif_figure[current_row, 2] <- nodes_names[current_letter_pointer + 2]
	triplet_motif_figure[current_row, 3] <- as.character ( triplet_motifs[i,1] )

	current_row <- current_row + 1

	# b --- c edge of the triplet motif
	triplet_motif_figure[current_row, 1] <- nodes_names[current_letter_pointer + 1]
	triplet_motif_figure[current_row, 2] <- nodes_names[current_letter_pointer + 2]
	triplet_motif_figure[current_row, 3] <- as.character( triplet_motifs[i,2])

	current_row <- current_row + 1

}

### Use R Cytoscape to add the edges into the Cytoscape network

## Add the list of nodes
list_of_nodes <- unique( c(triplet_motif_figure[,1], triplet_motif_figure[,2]))

graph_nel_object <- new ('graphNEL', edgemode='undirected')

graph_nel_object <- graph::addNode( as.character( list_of_nodes) , graph_nel_object)

#######################################################################################################################

## Add node attributes

# protein A and B
protein_A_attributes <- sapply ( triplet_motif_figure[,3], function(x) { ifelse( x == 'kd', 'kinase', NA ) } )

protein_A_attributes <- sapply ( names(protein_A_attributes), function(x) { ifelse( x == 'td', 'transcription factor', 
																							  	protein_A_attributes[x] ) } )

names( protein_A_attributes) <- triplet_motif_figure[,1]

# protein C

protein_C_attributes <- sapply ( triplet_motif_figure[,3], function(x) { ifelse( x == 'ku', 'kinase', NA ) } )

protein_C_attributes <- sapply ( names(protein_C_attributes), function(x) { ifelse( x == 'tu', 'transcription factor', 
																					protein_C_attributes[x] ) } )

names( protein_C_attributes) <- triplet_motif_figure[,2]

protein_A_attributes <- protein_A_attributes[is.na(protein_A_attributes)==FALSE]

protein_C_attributes <- protein_C_attributes[is.na(protein_C_attributes)==FALSE]

################################### 
# Add Node attributes, whether it is a kinase or a transcription factor.

cw <- CytoscapeWindow ( 'All triplet motifs ', graph=graph_nel_object, overwrite=TRUE)
graph_nel_object <- cw@graph

graph_nel_object <- initNodeAttribute( graph=graph_nel_object, attribute.name='is_kinase', attribute.type='integer', default.value=0)
nodeData (graph_nel_object, unique(names(protein_A_attributes[protein_A_attributes=='kinase'])), 'is_kinase'   ) <- rep( 1, length(unique(names(protein_A_attributes[protein_A_attributes=='kinase'] ))) )
nodeData (graph_nel_object, unique(names(protein_C_attributes[protein_C_attributes=='kinase'])), 'is_kinase'   ) <- rep( 1, length(unique(names(protein_C_attributes[protein_C_attributes=='kinase'] ))) )

graph_nel_object <- initNodeAttribute( graph=graph_nel_object, attribute.name='is_tf', attribute.type='integer', default.value=0)
nodeData (graph_nel_object, unique(names(protein_A_attributes[protein_A_attributes=='transcription factor'])), 'is_tf'   ) <- rep( 1, length(unique(names(protein_A_attributes[protein_A_attributes=='transcription factor'] ))) )
nodeData (graph_nel_object, unique(names(protein_C_attributes[protein_C_attributes=='transcription factor'])), 'is_tf'   ) <- rep( 1, length(unique(names(protein_C_attributes[protein_C_attributes=='transcription factor'] ))) )

#######################################################################################################################

## Add edges

graph_nel_object <- initEdgeAttribute (graph_nel_object, "edgeType", "char", "gi")

gene_a <- as.character( as.vector(t(triplet_motif_figure[, c("gene_a")])) )
gene_b <- as.character( as.vector(t(triplet_motif_figure[, c("gene_b")])) )

graph_nel_object <- graph::addEdge(gene_a, gene_b, graph_nel_object)

edge_type_attributes <- as.character( as.vector(t(triplet_motif_figure[, c("interaction_type")])) )

edgeData( graph_nel_object, gene_a, gene_b, "edgeType") <- edge_type_attributes

#######################################################################################################################

### Create the network visualization

cw <- setGraph(cw, graph_nel_object)

displayGraph(cw)

layoutNetwork(cw, layout.name = "force-directed")

#######################################################################################################################

### Add Network Style

triplet_motif_network_display_style_all_triple_motifs <- function(cw) {

	setEdgeColorRule(cw, 'edgeType',
					 control.points=c( 'ku', 'kd', 'gi', 'tu', 'td', 'p'), 
					 colors=c('#0000ff', '#0000ff', '#00ff00', '#ff0000', '#ff0000', '#000000'), 
					 mode='lookup', default.color='#808080')

	setEdgeSourceArrowRule(cw, 'edgeType',
						   attribute.values=c( 'ku', 'kd', 'gi', 'tu', 'td', 'p'), 
						   arrows=c('ARROW', 'NONE', 'NONE', 'ARROW', 'NONE', 'NONE'), 
						   default='NONE')

	setEdgeTargetArrowRule(cw, 'edgeType',
						   attribute.values=c( 'ku', 'kd', 'gi', 'tu', 'td', 'p'), 
						   arrows=c('NONE', 'ARROW', 'NONE', 'NONE', 'ARROW', 'NONE'),  
						   default='NONE')

	setEdgeSourceArrowColorRule(cw, 'edgeType',
								control.points=c( 'ku', 'kd', 'gi', 'tu', 'td', 'p'), 
								colors=c('#0000ff', '#0000ff', '#00ff00', '#ff0000', '#ff0000', '#000000'), 
								mode='lookup', default.color='#808080')

	setEdgeTargetArrowColorRule(cw, 'edgeType',
								control.points=c( 'ku', 'kd', 'gi', 'tu', 'td', 'p'), 
								colors=c('#0000ff', '#0000ff', '#00ff00', '#ff0000', '#ff0000', '#000000'),  
								mode='lookup', default.color='#808080')
}

triplet_motif_network_display_style_all_triple_motifs (cw)

#######################################################################################################################
```

```{r}
#########################################################################################################  
### Draw the 6 different edge types (gi, p, tu, td, ku, kd), for use as a legend.
#########################################################################################################

## Draw these in another Cytoscape window.
graph_nel_object <- new ('graphNEL', edgemode='undirected')

cw <- CytoscapeWindow ( 'All types of edges', graph=graph_nel_object, overwrite=TRUE)
graph_nel_object <- cw@graph   # Once you created the cw object, it is important to get the graphNEL object back, otherwise the pointer is lost

### Add Nodes
graph_nel_object <- graph::addNode( c( 'BA', 'BB', 'BC', "BD", "BE", "BF", "BG", "BH") , graph_nel_object)

## Add edges
graph_nel_object <- initEdgeAttribute (graph_nel_object, "edgeType", "char", "gi")

gene_a <- c('BA', 'BC', 'BE', 'BG')
gene_b <- c('BB', 'BD', 'BF', 'BH')

graph_nel_object <- graph::addEdge(gene_a, gene_b, graph_nel_object)

## Add edge attributes
edge_type_attributes <- c("p", 'td', 'kd', 'gi')

edgeData( graph_nel_object, gene_a, gene_b, "edgeType") <- edge_type_attributes

edgeData( graph_nel_object, "BA", "BB", "edgeType") <- 'p'
edgeData( graph_nel_object, "BC", "BD", "edgeType") <- 'td'
edgeData( graph_nel_object, "BE", "BF", "edgeType") <- 'kd'
edgeData( graph_nel_object, "BG", "BH", "edgeType") <- 'gi'

## Display the edge types
cw <- setGraph(cw, graph_nel_object)

displayGraph(cw)

layoutNetwork(cw, layout.name = "force-directed")

triplet_motif_network_display_style_all_triple_motifs (cw)

###################################

```

```{r}

### Converting igraph to graphNEL does not work, probably need to e-mail igraph author, RCy3 author to find out why

# g3 <- make_star(10, mode="in")
# V(g3)$name <- letters[1:10]
# GNEL2 <- as_graphnel(g3)
# 
# 
# cw <- RCy3::setGraph(cw, GNEL2)
# 
# 
# RCy3::displayGraph(cw)
# 
# RCy3::layoutNetwork(cw, layout.name = "force-directed")
# plot(GNEL2)

```

### 2017-08-05 Source/Examples/rewire_network.Rmd
Add all current files

---
title: "rewire_network"
author: "Ignatius Pang"
date: "7 May 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(igraph)
library(tibble)
library(dplyr)
library(ggplot2)

 base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/"
# base_directory <- "/home/ignatius/Documents/Postdoc/2016/Triplet_Motifs/"

data_directory <- file.path( base_directory, "Data/Triplet_Motifs_R_data")

load( file.path(data_directory, "network_data_library.Rdata"))

source( file.path(base_directory, "Source/Common", "count_triplet_motifs_helper.R"))

```

## R Markdown

```{r}

# Make a ring with 10 vertices 
g <- make_ring(10, circular = TRUE)

# Plot the ring 
plot(g)

# Count the number of edges in the graph
number_of_edges <- ecount( g)

# Rewire the graphs by swapping edges 10 times, keeping the degree distribution the same
 graph_1 <- g %>%
			rewire(keeping_degseq(loops = FALSE, niter = number_of_edges))

 				# loops : Whether to allow destroying and creating loop edges.
 				# niter : number of rewiring trials to perform

# Plot the graph
 plot(graph_1)

# What happens if I don't keep the edgree distribution the same 
 graph_2 <- g %>%
					 rewire( each_edge(prob=1, loops = FALSE, multiple=FALSE))

 				# loops : Whether to allow destroying and creating loop edges.
 				# multiple : Logical scalar, whether multiple edges are allowed int the generated graph

 plot(graph_2)

```

```{r }

format_degree_distribution_as_table <- function( igraph_object, label) {

	table_of_node_degrees <- table( degree(igraph_object))

	## Add 1 to the values to avoid log(0)
	x_axis <- 	as.numeric( names( table_of_node_degrees ) )+ 1
	y_axis <- as.numeric(t(table_of_node_degrees)) + 1

	# plot( x_axis , y_axis,  log="xy")

	head(y_axis)

	result_table <- data.frame( label=rep(label, length(x_axis)), degrees=x_axis, frequency=y_axis  )

	return(result_table)
}

## Obtain a protein-protein interactions network

head( sbi_interactome_collated)

# Read in the graph object
graph_1 <- graph.data.frame(sbi_interactome_collated[, c("oln_id_a", "oln_id_b")], directed=FALSE, vertices=NULL)

# Tabulate and graph the node degrees of the original network
graph_1_table <- format_degree_distribution_as_table(graph_1, "Original Network")

# Rewire the network using degree-preserving randomization  
# Plot the degree distribution of the network afterwards
graph_2 <- graph_1  %>%
			rewire(keeping_degseq(loops = FALSE, niter = number_of_edges))

graph_2_table <- format_degree_distribution_as_table(graph_2, "Rewired, keeping degree distribution")

# Rewire the network without keeping the degree distribution the same
# Plot the degree distribution of the network afterwards
graph_3 <- graph_1  %>%
			rewire(each_edge(prob=0.4, loops = FALSE, multiple=FALSE))

graph_3_table <- format_degree_distribution_as_table(graph_3, "Random rewiring")

merged_table <- rbind( graph_1_table, graph_2_table, graph_3_table)

ggplot( merged_table, aes( degrees, frequency)) +
	geom_point() +
	facet_grid ( . ~ label) + 
    scale_x_continuous(trans='log2') + 
    scale_y_continuous(trans='log2')

```

### 2017-08-05 Source/Figures/print_triplet_network_specific_network.Rmd
Add all current files

---
title: "R Notebook"
Date: 13-7-2016
output:
  html_document: default
  html_notebook: default
Author: Ignatius Pang
---

Description: I want to visualize the network, which consists of all the triplet motifs. Only edges in triplet motifs are shown.

```{r}
library(RCy3)
library(dplyr)
library(RODBC)
library(sqldf)
```

Read helper functions 
```{r}
# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Poster/'

## Load the root base directory for the entire project
options <- commandArgs(trailingOnly = TRUE)
source( "./Common/parameters_file.R")

setwd ( file.path( base_directory, 'Source/Figures') )

source( file.path ( source_directory_common, 'draw_triplet_motif_network_helper.R') )

```

Read data tables 
```{r}
triplet_motifs_costanzo_2016 <- read.table ( file.path( list_of_triplets_directory, "triplet_motifs_costanzo_2016.txt"), 
											 header =TRUE , stringsAsFactors = FALSE)

triplet_motifs_costanzo_2016 <- triplet_motifs_costanzo_2016 %>% 
								dplyr::rename( oln_id_a = node_a, oln_id_b = node_b, oln_id_c = node_c)

toxic_upon_overexpression <- read.table ( file.path( data_directory, "overexpressed_toxic_genes.txt"), header=TRUE , stringsAsFactors = FALSE)

essential_genes <- read.table ( file.path( data_directory, "essential_genes.txt"), header=TRUE, stringsAsFactors = FALSE)

cell_cycle_peak_times_of_orfs <- read.table ( file.path( data_directory, "periodically_expressed_genes.txt"), header=TRUE, stringsAsFactors = FALSE)

gene_names <- read.table ( file.path(data_directory, "gene_names_table.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
						    na.strings="", quote="")

## Results from Spatial Analysis of Functional Enrichment (SAFE tool)

enriched_functions <- read.table ( file.path( results_directory, "SAFE/safe_exported_reports_20161123.txt-node_properties_annotation-highest.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
						    na.strings="", quote="")

```

Build phenotype master table 
```{r}

toxic_upon_overexpression <- toxic_upon_overexpression %>%
								dplyr::select ( one_of ( c( "oln_id"))) %>%
								dplyr::mutate ( overexpression_toxic = 1)

essential_genes <- essential_genes %>%
						dplyr::mutate ( essential = 1)

cell_cycle_peak_times_of_orfs <- cell_cycle_peak_times_of_orfs %>%
									dplyr::mutate ( periodically_expressed = 1)

essential_periodic_expression_toxic_overexpression <- toxic_upon_overexpression %>%
														full_join ( essential_genes ) %>% 
														full_join (  cell_cycle_peak_times_of_orfs )

essential_periodic_expression_toxic_overexpression [is.na( essential_periodic_expression_toxic_overexpression  ) ] <- 0

essential_periodic_expression_toxic_overexpression <- essential_periodic_expression_toxic_overexpression %>%
 														group_by ( oln_id) %>%
 														summarise( overexpression_toxic = sum( overexpression_toxic), 
 																   essential = sum( essential), 
 																   periodically_expressed = sum( periodically_expressed))

```

Get densely annotated triplets 
```{r}

densely_annotated_triplet_motif <- sqldf( "select motifs.* 
, data_a.essential as essential_a, data_a.periodically_expressed as periodically_expressed_a, data_a.overexpression_toxic as overexpression_toxic_a
, data_b.essential as essential_b, data_b.periodically_expressed as periodically_expressed_b, data_b.overexpression_toxic as overexpression_toxic_b
, data_c.essential as essential_c, data_c.periodically_expressed as periodically_expressed_c, data_c.overexpression_toxic as overexpression_toxic_c

, data_a.essential + data_b.essential + data_c.essential as essential_score
, data_a.periodically_expressed + data_b.periodically_expressed + data_c.periodically_expressed as periodically_expressed_score
, data_a.overexpression_toxic + data_b.overexpression_toxic + data_c.overexpression_toxic as overexpression_toxic_score

, case when data_a.essential = 1 and data_b.essential = 1 and data_c.essential = 1 then 1 else 0 end as essential_abc
, case when data_a.periodically_expressed = 1 and data_b.periodically_expressed = 1 and data_c.periodically_expressed = 1 then 1 else 0 end as periodically_expressed_abc
, case when data_a.overexpression_toxic = 1 and data_b.overexpression_toxic = 1 and data_c.overexpression_toxic = 1 then 1 else 0 end as overexpression_toxic_abc

, case when data_a.essential is not null then data_a.essential else 0 end 
+ case when data_a.periodically_expressed is not null then data_a.periodically_expressed else 0 end 
+ case when data_a.overexpression_toxic is not null then data_a.overexpression_toxic else 0 end 
+ case when data_b.essential is not null then data_b.essential else 0 end   
+ case when data_b.periodically_expressed  is not null then data_b.periodically_expressed else 0 end 
+ case when data_b.overexpression_toxic  is not null then data_b.overexpression_toxic else 0 end  as score_ab

, case when data_c.essential is not null then data_c.essential else 0 end 
+ case when data_c.periodically_expressed is not null then data_c.periodically_expressed else 0 end 
+ case when data_c.overexpression_toxic is not null then data_c.overexpression_toxic else 0 end as score_c

from triplet_motifs_costanzo_2016  motifs
		left outer join essential_periodic_expression_toxic_overexpression data_a
			on data_a.oln_id = oln_id_a
		left outer join essential_periodic_expression_toxic_overexpression data_b
			on data_b.oln_id = oln_id_b
		left outer join essential_periodic_expression_toxic_overexpression data_c
			on data_c.oln_id = oln_id_c;
", stringsAsFactors=FALSE)

```

Network of tightly regulated proteins (involved in spindle pole formation)
```{r}
triplet_motifs_costanzo <- sqldf( "select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p' and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'td' ) 
	or  ( type_ac = 'p' and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and score_ab >=6
	  and score_c >=3 ;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'Tightly regulated proteins' )

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)

triplet_motif_network_display_style(cw)

redraw (cw)

current_example_dir <- file.path( results_directory, "Achilles_heel/Spindle-pole body example")

create_directory_if_not_exists( current_example_dir)

## saveNetwork command currently not working for unknown reasons
#saveNetwork(cw, file.name= file.path( current_example_dir, "spindle-pole body example"), format='cys')

saveImage ( cw, file.name= file.path( current_example_dir, "spindle-pole body example"), image.type='pdf')

```

All three proteins in the motif needs to be essential and periodically expressed 
```{r}

triplet_motifs_costanzo <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p'  and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'td' ) 
	or  ( type_ac = 'p'  and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and essential_a = 1
	  and essential_b = 1
	  and essential_c = 1

	  and periodically_expressed_a = 1
	  and periodically_expressed_b = 1
	  and periodically_expressed_c = 1

except

select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p' and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'td' ) 
	or  ( type_ac = 'p' and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and score_ab >=6;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'essential periodically expressed' )

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)

triplet_motif_network_display_style(cw)

redraw (cw)

current_example_dir <- file.path( results_directory, "Achilles_heel/Essential and periodically expressed")

create_directory_if_not_exists( current_example_dir)

saveImage ( cw, file.name= file.path( current_example_dir, "essential and periodically expressed"), image.type='pdf')

```

Essential and toxic upon overexpression
```{r}

triplet_motifs_costanzo <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p' and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'ku' ) 
	or  ( type_ac = 'p' and type_bc = 'td' ) 
	or  ( type_ac = 'p' and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and essential_a = 1
	  and essential_b = 1
	  and essential_c = 1

	  and overexpression_toxic_a = 1
	  and overexpression_toxic_b = 1
	  and overexpression_toxic_c = 1

except

select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
from densely_annotated_triplet_motif
where ( ( type_ac = 'p'  and type_bc = 'p' )
	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'ku' ) 
	or  ( type_ac = 'p'  and type_bc = 'td' ) 
	or  ( type_ac = 'p'  and type_bc = 'kd' ) 
	or  ( type_ac = 'ku' and type_bc = 'p' ) 
	or  ( type_ac = 'td' and type_bc = 'p' ) 
	or  ( type_ac = 'kd' and type_bc = 'p' ) 	
      ) 
	  and score_ab >=6;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'essential overexpression' )

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)

triplet_motif_network_display_style(cw)

redraw (cw)

current_example_dir <- file.path( results_directory, "Achilles_heel/Essential and toxic upon overexpression")

create_directory_if_not_exists( current_example_dir)

saveImage ( cw, file.name= file.path( current_example_dir, "Essential and toxic upon overexpression"), image.type='pdf')

```

Periodically expressed and toxic upon overexpression
```{r}

triplet_motifs_costanzo <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
									from densely_annotated_triplet_motif
									where ( ( type_ac = 'p' and type_bc = 'p' )
									or  ( type_ac = 'tu' and type_bc = 'tu' ) 
									or  ( type_ac = 'ku' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'td' ) 
									or  ( type_ac = 'p' and type_bc = 'kd' ) 
									or  ( type_ac = 'ku' and type_bc = 'p' ) 
									or  ( type_ac = 'td' and type_bc = 'p' ) 
									or  ( type_ac = 'kd' and type_bc = 'p' ) 	
									) 
									and periodically_expressed_a = 1
									and periodically_expressed_b = 1
									and periodically_expressed_c = 1

									and overexpression_toxic_a = 1
									and overexpression_toxic_b = 1
									and overexpression_toxic_c = 1

									except

									select oln_id_a, oln_id_b, oln_id_c, type_ac, type_bc, genetic_interaction_score 
									from densely_annotated_triplet_motif
									where ( ( type_ac = 'p' and type_bc = 'p' )
									or  ( type_ac = 'tu' and type_bc = 'tu' ) 
									or  ( type_ac = 'ku' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'ku' ) 
									or  ( type_ac = 'p' and type_bc = 'td' ) 
									or  ( type_ac = 'p' and type_bc = 'kd' ) 
									or  ( type_ac = 'ku' and type_bc = 'p' ) 
									or  ( type_ac = 'td' and type_bc = 'p' ) 
									or  ( type_ac = 'kd' and type_bc = 'p' ) 	
									) 
									and score_ab >=6;", stringsAsFactors=FALSE)

triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )

cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'periodically expressed and toxic upon overexpression' )

cw <- add_node_attributes(cw, gene_names , "oln_id")

cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")

displayGraph(cw)

triplet_motif_network_display_style(cw)

redraw (cw)

current_example_dir <- file.path( results_directory, "Achilles_heel/Periodically expressed and toxic upon overexpression")

create_directory_if_not_exists( current_example_dir)

saveImage ( cw, file.name= file.path( current_example_dir, "Periodically expressed and toxic upon overexpression"),
			image.type='pdf')

```

### 2017-08-05 Results/Bootstrap_p_values/Analyze_GI_edges/Job_40/compare_triplet_motif_gi_with_other_networks.R

@@ -1,0 +1,335 @@
+### Script: compare_triplet_motif_gi_with_other_networks.R
+### Author: Ignatius Pang 
+### Date: 22-8-2016
+### Description: Compare the genetic interaction edge in triplet motifs with other types of interactions. 
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# 
+
+#########################################################
+### Parameters 
+### Global Parameters 
+
+options <- commandArgs(trailingOnly = TRUE)
+
+### Source the header file here 
+
+if ( length(options) != 0 
+	 & ( options[1] == 'katana' | options[1] == 'clive')  ) {
+	source( "./parameters_file.R" )
+
+} else {
+	source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+}
+
+### Local Parameters
+observed_results_table_file   <- "observed_results_table_file.tab"
+randomized_results_table_file <- "randomized_results_table.tab"
+# output_enrichment_p_value     <- "enrichment_p_value_fixed.tab"
+# output_depletion_p_value      <- "depletion_p_value_fixed.tab"
+output_full_results_table     <- "full_results_table.tab"
+
+if (is_run_locally) {
+	
+	results_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/Analyze_GI_edges/"
+}
+
+#########################################################
+
+#### Get the actual observed number of triplet motifs
+
+
+#########################################################
+
+fix_edge_attribute_direction <- function (interaction_type_abbrev) {
+	
+	if ( is.na( interaction_type_abbrev ) ) {
+		return (NA)
+	} 	
+	
+	if (interaction_type_abbrev== "tu" ) {
+		return ('td')
+	} else if ( interaction_type_abbrev== "ku") {
+		return ('kd')
+	} else if ( interaction_type_abbrev== "td") {
+		return ('tu')
+	} else if ( interaction_type_abbrev== "kd") {
+		return ('ku')
+	} else if ( interaction_type_abbrev== "p") {
+		return ('p')
+	} 
+	else {
+		stop ('interaction type not supported')
+	}
+}
+
[…]

### 2017-08-05 Results/Bootstrap_p_values/Analyze_GI_edges/Job_40/count_triplet_motifs_helper.R

@@ -1,0 +1,1520 @@
+### Script: count_triplet_motifs_helper.R
+### Author: Ignatius Pang 
+### Date: 20-5-2016
+### Description: Count the observed number of triplet motifs. Randomize the respective networks and count the number triplet motifs, repeat randomization 1000 times.
+### Obtain the bootstrap p-value. This script contain the helper functions for the main script 'count_triplet_motifs_negative_interactions.R'.
+
+## Project space:
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# psql sbi_triplet_motifs 
+
+#########################################################
+## Insert directed network into both directions into the edge list table, so the direction that tables join together won't affect the analyses
+
+## Inputs:
+## input_table - must have 4 columns only, which are: gene_a, gene_b, interaction type, interaction type abbreviation
+## gene_a - column name for input table that cotains gene A of the interaction
+## gene_b - column name for input table that cotains gene B of the interaction
+## interaction_type_forward - information on the type of interaction for A  ---> B 
+## interaction_type_reverse - information on the type of interaction for B <---> A
+## interaction_abbrev_forward - abbereviated information on the type of interaction for A ---> B 
+## interaction_abberv_reverse - abbereviated information on the type of interaction for B ---> A 
+## col_a - column name for gene A in the output table
+## col_b - column name for gene B in the output table
+## col_type - column name for the interaction type in the output table
+## col_abbrev - column name for the interaction type abbreviation in the output table
+
+## Output table:
+## Output table has 4 columns, denoted by col_a, col_b, col_type and col_abbrev mentioned in the inputs description above.
+collate_interactions_from_both_direction <- function (input_table, gene_a, gene_b, 
+													  interaction_type_forward, interaction_type_reverse, 
+													  interaction_abbrev_forward, interaction_abberv_reverse,
+													  col_a, col_b, col_type, col_abbrev) {
+	num_rows <- length(input_table[,1])
+	
+	new_table <- as.data.frame( matrix(ncol=4, nrow=2*num_rows))
+	
[…]

### 2017-08-05 Results/Bootstrap_p_values/Analyze_GI_edges/Job_40/parameters_file.R

@@ -1,0 +1,128 @@
+### Script: count_triplet_motifs_negative_interactions.R
+### Author: Ignatius Pang 
+### Date: 20-5-2016
+### Description: Count the observed number of triplet motifs. Randomize the respective networks and count the number triplet motifs, repeat randomization 1000 times.
+### Obtain the bootstrap p-value
+
+library(igraph)
+library(dplyr)
+library(lazyeval)
+library(parallel)
+library(tidyr)
+
+sessionInfo()
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+
+# Command Line Parameters
+#  script.R <compute location (katana|clive|local)>  <array job ID> <number of randomized trials>
+
+#########################################################
+### Parameters 
+
+is_run_locally 			     <- TRUE
+array_job_id 			     <- NULL 
+random_number_seed 		     <- 1985
+number_of_cores_to_use 		 <- 24
+number_of_randomized_trials  <- 100
+num_iteration_rewire_network <- NULL # Number of times each network is rewired before counting the triplet motifs
+use_costanzo_2010_dataset 	 <- FALSE
+
+data_directory 			<- "./"
+source_directory 		<- "./"
+results_directory 		<- "./"
+source_directory_common <- "./"
+
+if ( length(options) != 0 &
+	! (  options[1] == 'katana' | options[1] == 'clive' | options[1] == 'locally'  )  ) {
+		stop ( 'First command line parameter must either by katana, clive, or local') 
+}
+
+if ( length(options) != 0 
+	 & ( options[1] == 'katana' | options[1] == 'clive')  ) {
+	is_run_locally <- FALSE
+	
+	if ( options[1] == 'katana' ) {
+		
+		number_of_cores_to_use <- 16
+		
+	} else if (options[1] == 'clive' ) {
+		
+		number_of_cores_to_use <- 24
+	}
+}
+
+print (paste ( "is_run_locally = ", is_run_locally) ) 
+
+
+### Get array_job_id and set random number seed 
+if ( is_run_locally == FALSE & length(options) >=2 ) {
+	
+	array_job_id <- as.numeric ( options[2]  )
+	
+	if ( ! is.null(array_job_id) ) {
+		if ( is.numeric(array_job_id) ) { 
+			random_number_seed <- random_number_seed + array_job_id 
+		} else {
+			stop ( "array_job_id is not numeric.")
+		}
+	}
+}
[…]

### 2017-08-05 Results/Bootstrap_p_values/Paralogs/Job_21/count_triplet_motifs_helper.R

@@ -1,0 +1,1473 @@
+### Script: count_triplet_motifs_helper.R
+### Author: Ignatius Pang 
+### Date: 20-5-2016
+### Description: Count the observed number of triplet motifs. Randomize the respective networks and count the number triplet motifs, repeat randomization 1000 times.
+### Obtain the bootstrap p-value. This script contain the helper functions for the main script 'count_triplet_motifs_negative_interactions.R'.
+
+## Project space:
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# psql sbi_triplet_motifs 
+
+#########################################################
+## Insert directed network into both directions into the edge list table, so the direction that tables join together won't affect the analyses
+
+## Inputs:
+## input_table - must have 4 columns only, which are: gene_a, gene_b, interaction type, interaction type abbreviation
+## gene_a - column name for input table that cotains gene A of the interaction
+## gene_b - column name for input table that cotains gene B of the interaction
+## interaction_type_forward - information on the type of interaction for A  ---> B 
+## interaction_type_reverse - information on the type of interaction for B <---> A
+## interaction_abbrev_forward - abbereviated information on the type of interaction for A ---> B 
+## interaction_abberv_reverse - abbereviated information on the type of interaction for B ---> A 
+## col_a - column name for gene A in the output table
+## col_b - column name for gene B in the output table
+## col_type - column name for the interaction type in the output table
+## col_abbrev - column name for the interaction type abbreviation in the output table
+
+## Output table:
+## Output table has 4 columns, denoted by col_a, col_b, col_type and col_abbrev mentioned in the inputs description above.
+collate_interactions_from_both_direction <- function (input_table, gene_a, gene_b, 
+													  interaction_type_forward, interaction_type_reverse, 
+													  interaction_abbrev_forward, interaction_abberv_reverse,
+													  col_a, col_b, col_type, col_abbrev) {
+	num_rows <- length(input_table[,1])
+	
+	new_table <- as.data.frame( matrix(ncol=4, nrow=2*num_rows))
+	
[…]

### 2017-08-05 Results/Bootstrap_p_values/Paralogs/Job_22/count_triplet_motifs_paralogs_not_gi_edge.R

@@ -1,0 +1,153 @@
+### Script: count_triplet_motifs_paralogs_not_gi.R
+### Author: Ignatius Pang 
+### Date: 27-5-2016
+### Description: For each type of triplet motif, count the number of motifs in which the edge with the negative genetic interaction 
+### consist of a pair of paralogous genes . 
+### Repeat the same calculation with randomizated 2000 networks and obtain the bootstrap p-value.
+### Randomization conserves the degree distribution of the network. 
+
+library(igraph)
+library(dplyr)
+library(lazyeval)
+library(parallel)
+
+sessionInfo()
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# 
+
+#########################################################
+### Parameters 
+options <- commandArgs(trailingOnly = TRUE)
+
+### Source the parameters file here 
+if ( length(options) != 0  )  { 
+	if ( options[1] == 'katana' | options[1] == 'clive')   {
+		source( "./parameters_file.R" )
+
+	} else {
+		source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+	}
+}
+
+### Local Parameters
+if (is_run_locally) {
+	results_directory <- paste( base_directory, "Results/Bootstrap_p_values_temp/Paralogs/",  sep="")
+}
+
+observed_counts_orthomcl_paralogs_not_gi_file 	<- "observed_counts_orthomcl_paralogs_not_gi_in_tri_motifs.tab"
+observed_counts_sgd_paralogs_not_gi_file	    <- "observed_counts_sgd_paralogs_not_gi_in_tri_motifs.tab"
+
+randomized_counts_orthomcl_paralogs_not_gi_file <- "randomized_counts_orthomcl_paralogs_not_gi_in_tri_motifs.tab"
+randomized_counts_sgd_paralogs_not_gi_file      <- "randomized_counts_sgd_paralogs_not_gi_in_tri_motifs.tab"
+			  
+full_results_orthomcl_paralogs_not_gi_file    	<- "full_results_table_orthomcl_paralogs_not_gi_in_tri_motifs.tab"		  
+full_results_sgd_paralogs_not_gi_file  		    <- "full_results_table_sgd_paralogs_not_gi_in_tri_motifs.tab"
+
+#########################################################
+
[…]

### 2017-08-05 Source/Analyze_GI_edges/run_triplet_motifs_network_overlap_array_katana.sh

@@ -1,0 +1,83 @@
+#!/bin/bash
+
+#PBS -N TriAlzGI[]
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=100gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+## Clive
+#### PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue_array_jobs.sh
+
+## Katana
+#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue_array_jobs.sh
+
+# Command for running array jobs 
+#PBS -t 1-40
+
+PROJECT_DIRECTORY=Analyze_GI_edges
+MAIN_SCRIPT=compare_triplet_motif_gi_with_other_networks.R
+HPC_CLUSTER="katana"
+NUM_RANDOM_TRIALS=100
+LOG_PREFIX="overlap_network"
+
+if [ $HPC_CLUSTER = 'clive' ] 
+then 
+	## Clive
+	module load openmpi/1.10.3
+	module load R/3.3.1-bioconductor-3.3
+elif [ $HPC_CLUSTER = 'katana' ]
+then 
+	## Katana
+	module load openmpi/1.8.3
+	module load R/3.2.2
+else
+	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
+fi
+
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+DATE=$(date +"%Y%m%d")
+
+
+export PROJECT_DIRECTORY
+
+### Create relevant directories
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}
+fi
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID}
+fi
+
[…]

### 2017-08-05 Source/Cell_Cycle/collate_results_cell_cycle.R

@@ -1,0 +1,59 @@
+library(dplyr)
+library(tidyr)
+library(ggraptR)
+library(ggplot2)
+library(reshape2)
+
+#####################################################################								 
+
+### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
+### This setting is for the poster presentation.
+
+base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
+
+source_directory <- paste( base_directory, "Source/", sep="")
+source_directory_common <- paste( source_directory, "Common/",  sep="")
+source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
+source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
+
+results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Cell_Cycle/", sep="")
+final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+
+	if (! file.exists(final_results_directory)){
+		dir.create(final_results_directory)
+
+	}
+
+################################################################################################################################################
+# Counts of Triplet Motifs Costanzo et al. 2010 dataset
+
+final_results_directory_pattern      <- "Final_Results"
+number_of_randomized_samples         <- 2000
+p_values 							 <- 0.05
+
+## AB
+triplet_motifs_full_results_file     <- "full_results_periodic_gene_counts_a_and_b.tab"
+count_triplet_motifs_randomized_file <- "randomized_results_periodic_gene_counts_a_and_b.tab" 
+
+triplet_motifs_file_pattern      	 <- "^randomized_results_periodic_gene_counts_a_and_b.tab"
+observed_file_pattern        		 <-  "Job_20/observed_a_and_b_periodic_gene_counts.tab"
+
+
+collated_table <- collate_result_files_helper ( results_directory, triplet_motifs_full_results_file, count_triplet_motifs_randomized_file,
+							  triplet_motifs_file_pattern, observed_file_pattern, final_results_directory_pattern,
+							  number_of_randomized_samples, p_values)
+
+#### C
+
+triplet_motifs_full_results_file     <- "full_results_periodic_gene_counts_c.tab"
+count_triplet_motifs_randomized_file <- "randomized_results_periodic_gene_counts_c.tab" 
+
+triplet_motifs_file_pattern      	 <- "^randomized_results_periodic_gene_counts_c.tab"
[…]

### 2017-08-05 Source/Cell_Cycle/count_triplet_motifs_periodic_genes.R

@@ -1,0 +1,174 @@
+### Script: count_triplet_motifs_periodic_genes.R
+### Author: Ignatius Pang 
+### Date: 27-5-2016
+### Description: Count the observed number of periodically expressed genes in triplet motifs. 
+### Randomize the respective networks and count the number of esential genes in triplet motifs. Keep the periodically expressed genes the same, only randomize the edges.
+### Repeat randomization 2000 times.
+### Obtain the bootstrap p-value
+
+library(igraph)
+library(dplyr)
+library(lazyeval)
+library(parallel)
+library(tibble)
+
+sessionInfo()
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# 
+
+#########################################################
+### Parameters 
+options <- commandArgs(trailingOnly = TRUE)
+
+
+### Source the header file here 
+
+if ( length(options) != 0 
+	 & ( options[1] == 'katana' | options[1] == 'clive')  ) {
+	source( "./parameters_file.R" )
+
+} else {
+	source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+}
+
+
+### Local Parameters
+if (is_run_locally) {
+	results_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values_temp/Cell_Cycle/"
+}
+
+# output_observed_triplet_motif_counts <- "results_count_triplet_motifs_costanzo.tab" # "results_count_triplet_motifs_costanzo.tab"
+observed_a_and_b_periodic_gene_counts <- "observed_a_and_b_periodic_gene_counts.tab"
+observed_c_periodic_gene_counts       <- "observed_c_periodic_gene_counts.tab"
+
+randomized_count_a_and_b_table_file   <- "randomized_results_periodic_gene_counts_a_and_b.tab"
+randomized_count_c_table_file         <- "randomized_results_periodic_gene_counts_c.tab"
+			  
+output_full_results_table_count_a_and_b	<- "full_results_periodic_gene_counts_a_and_b.tab"		  
+output_full_results_table_count_c       <- "full_results_periodic_gene_counts_c.tab"
+
+
+#########################################################
+
+#### Get the actual observed number of triplet motifs
+
[…]

### 2017-08-05 Source/Cell_Cycle/run_triplet_motifs_periodic_genes_on_katana_array.sh

@@ -1,0 +1,85 @@
+#!/bin/bash
+
+#PBS -N CellCycle[]
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=100gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+## Clive
+#### PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue_array_jobs.sh
+
+## Katana
+#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue_array_jobs.sh
+
+# Command for running array jobs 
+#PBS -t 1-20
+
+PROJECT_DIRECTORY=Cell_Cycle
+MAIN_SCRIPT="count_triplet_motifs_periodic_genes.R"
+HPC_CLUSTER="katana"
+NUM_RANDOM_TRIALS=100
+LOG_PREFIX="count_triplet_motifs_periodic_genes"
+
+
+if [ $HPC_CLUSTER == 'clive' ] 
+then 
+	## Clive
+	module load openmpi/1.10.3
+	module load R/3.3.1-bioconductor-3.3
+elif [ $HPC_CLUSTER == 'katana' ]
+then 
+	## Katana
+	module load openmpi/1.8.3
+	module load R/3.2.2
+else
+	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
+fi
+
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+DATE=$(date +"%Y%m%d")
+
+
+
+export PROJECT_DIRECTORY
+
+### Create relevant directories
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}
+fi
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID}
+fi
+
[…]

### 2017-08-05 Source/Common/count_triplet_motifs_helper.R

@@ -1,0 +1,1503 @@
+### Script: count_triplet_motifs_helper.R
+### Author: Ignatius Pang 
+### Date: 20-5-2016
+### Description: Count the observed number of triplet motifs. Randomize the respective networks and count the number triplet motifs, repeat randomization 1000 times.
+### Obtain the bootstrap p-value. This script contain the helper functions for the main script 'count_triplet_motifs_negative_interactions.R'.
+
+## Project space:
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# psql sbi_triplet_motifs 
+
+#########################################################
+## Insert directed network into both directions into the edge list table, so the direction that tables join together won't affect the analyses
+
+## Inputs:
+## input_table - must have 4 columns only, which are: gene_a, gene_b, interaction type, interaction type abbreviation
+## gene_a - column name for input table that cotains gene A of the interaction
+## gene_b - column name for input table that cotains gene B of the interaction
+## interaction_type_forward - information on the type of interaction for A  ---> B 
+## interaction_type_reverse - information on the type of interaction for B <---> A
+## interaction_abbrev_forward - abbereviated information on the type of interaction for A ---> B 
+## interaction_abberv_reverse - abbereviated information on the type of interaction for B ---> A 
+## col_a - column name for gene A in the output table
+## col_b - column name for gene B in the output table
+## col_type - column name for the interaction type in the output table
+## col_abbrev - column name for the interaction type abbreviation in the output table
+
+## Output table:
+## Output table has 4 columns, denoted by col_a, col_b, col_type and col_abbrev mentioned in the inputs description above.
+collate_interactions_from_both_direction <- function (input_table, gene_a, gene_b, 
+													  interaction_type_forward, interaction_type_reverse, 
+													  interaction_abbrev_forward, interaction_abberv_reverse,
+													  col_a, col_b, col_type, col_abbrev) {
+	num_rows <- length(input_table[,1])
+	
+	new_table <- as.data.frame( matrix(ncol=4, nrow=2*num_rows))
+	
[…]

### 2017-08-05 Source/Common/draw_triplet_motif_network_helper.R

@@ -1,0 +1,294 @@
+
+# Function: draw_triplet_motif_network
+
+## The input has to following the following format: 
+
+#   oln_id_a oln_id_b oln_id_c type_ac type_bc genetic_interaction_score
+# 1  YBL007C  YAL023C  YKL112W      tu      tu                   -0.1390
+# 2  YBL023C  YAR007C  YDL056W      tu      tu                   -0.1556
+
+draw_triplet_motif_network <- function ( triplet_motifs_costanzo, network_name ) { 
+	
+	#######################################################################################################################
+	
+	## Add the list of nodes 
+	list_of_nodes <- unique( c(triplet_motifs_costanzo[,1], triplet_motifs_costanzo[,2], triplet_motifs_costanzo[,3]))
+	
+	graph_nel_object <- new ('graphNEL', edgemode='undirected')
+	
+	graph_nel_object <- graph::addNode( as.character( list_of_nodes) , graph_nel_object)
+	
+	#######################################################################################################################
+	
+	# Create Cytoscape window
+	cw <- CytoscapeWindow ( network_name, graph=graph_nel_object, overwrite=TRUE)
+	graph_nel_object <- cw@graph
+	
+	#######################################################################################################################
+	
+	## Add edges
+	
+	graph_nel_object <- initEdgeAttribute (graph_nel_object, "edgeType", "char", "gi")
+	
+	gene_a <- as.character( as.vector(c( t(triplet_motifs_costanzo[,1]) ,
+										 t(triplet_motifs_costanzo[,1])    , 
+										 t(triplet_motifs_costanzo[,2]) ) ))
+	
+	gene_b <- as.character( as.vector(c( t(triplet_motifs_costanzo[,2]) ,
+										 t(triplet_motifs_costanzo[,3])    , 
+										 t(triplet_motifs_costanzo[,3]) ) ))
+	
+	graph_nel_object <- graph::addEdge(gene_a, gene_b, graph_nel_object) 
+	
+	edge_type_attributes <- as.character( as.vector( c( 
+		rep( "gi", length(triplet_motifs_costanzo[,1] )),
+		t(triplet_motifs_costanzo[, c("type_ac")]),
+		t(triplet_motifs_costanzo[, c("type_bc")])
+	)  ) ) 
+	
+	edgeData( graph_nel_object, gene_a, gene_b, "edgeType") <- edge_type_attributes
+	
[…]

### 2017-08-05 Source/Common/epilogue.sh

@@ -1,0 +1,14 @@
+#! /bin/bash
+
+echo "epilogue: copy from local scratch to working directory"
+echo "    ${TMPDIR}"
+echo "    ${PBS_O_WORKDIR}"
+echo
+
+rsync -a ${TMPDIR}/*.tab ${PBS_O_WORKDIR}/../Results
+
+rsync -a ${TMPDIR}/*.Rdata ${PBS_O_WORKDIR}/../Results
+
+rsync -a ${TMPDIR}/*.log  ${PBS_O_WORKDIR}/../Log
+
+

### 2017-08-05 Source/Common/epilogue_array_jobs.sh

@@ -1,0 +1,7 @@
+#! /bin/bash
+
+echo "epilogue: copy from local scratch to working directory"
+echo "    ${TMPDIR}"
+echo "    ${PBS_O_WORKDIR}"
+echo
+

### 2017-08-05 Source/Common/parameters_file.R

@@ -1,0 +1,150 @@
+### Script: parameters_file.R
+### Author: Ignatius Pang 
+### Date: 20-5-2016
+### Description: Set the common parameters for the entire project.
+
+library(igraph)
+library(dplyr)
+library(lazyeval)
+library(parallel)
+library(tidyr)
+
+sessionInfo()
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+
+# Command Line Parameters
+#  script.R <compute location (katana|clive|local)>  <array job ID> <number of randomized trials>
+
+#########################################################
+### Parameters 
+
+#############################
+#### Need to update 
+#############################
+
+## Load the root base directory for the entire project
+base_directory <- "/home/ignatius/PostDoc/2017/Triplet_Motifs_Public"
+
+is_run_locally 			     <- TRUE
+array_job_id 			     <- NULL 
+random_number_seed 		     <- 1985
+number_of_cores_to_use 		 <- 24
+number_of_randomized_trials  <- 100
+num_iteration_rewire_network <- NULL # Set to NULL if number of times each network is rewired equals to the size of the network. 
+									 # Otherwise, input is a proportion, representing the proportion of the total number of edges in the network to be rewired.
+use_costanzo_2010_dataset 	 <- FALSE
+
+#############################
+#############################
+
+### Initiate global parameters
+data_directory 			<- "./"
+source_directory 		<- "./"
+results_directory 		<- "./"
+source_directory_common <- "./"
+
+## Deal with parameters when the code are to be ran locally
+if ( length(options) != 0 
+	 & ( options[1] == 'katana' | options[1] == 'clive')  ) {
+	is_run_locally <- FALSE
+}
+
+#############################
+#### Need to update 
+#############################
+if (is_run_locally == TRUE  ) {
+	random_number_seed <- 1985
+	number_of_cores_to_use <- 4
+	number_of_randomized_trials <- 4
+	num_iteration_rewire_network <- 0.001 # Number of times each network is rewired before counting the triplet motifs
+	
+	data_directory <- file.path( base_directory, "Data/Triplet_Motifs_R_data")
+	source_directory <- file.path( base_directory, "Source")
[…]

### 2017-08-05 Source/Common/prologue.sh

@@ -1,0 +1,9 @@
+#! /bin/bash
+ 
+echo "prologue: copy from working directory to local scratch"
+echo "    ${PBS_O_WORKDIR}"
+echo "    ${TMPDIR}"
+echo
+ 
+#rm -rf ${PBS_O_WORKDIR}/Results
+rsync -a ${PBS_O_WORKDIR}/ ${TMPDIR}

### 2017-08-05 Source/Common/save_R_datasets.R

@@ -1,0 +1,246 @@
+
+library(RODBC)
+library(igraph)
+library(dplyr)
+library(lazyeval)
+
+# Author: Ignatius Pang
+# Date: 17-5-2016
+# Description: Transfer data from the SQL database into text file so it can be uploaded into R for data analysis without database connection.
+
+
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/'
+# Rscript --vanilla save_R_datasets.R 
+
+#################################################################################################################
+
+# options <- commandArgs(trailingOnly = TRUE)
+
+data_directory <- "/home/ignatius/PostDoc/2017/Triplet_Motifs_Public/Data/Triplet_Motifs_R_data"
+source_directory <- "/home/ignatius/PostDoc/2017/Triplet_Motifs_Public/Source"
+
+source_directory_common  <- file.path( source_directory, "Common")
+
+source( file.path(source_directory_common, "count_triplet_motifs_helper.R") )
+
+
+#################################################################################################################
+
+input_db     <- "sbi_triplet_motifs"  # The name of the SQL database for the data to be imported into
+user_id      <- "ignatius"
+user_passwd  <- "Sp33dBo@t"
+
+conn_string  <- paste("SERVER=localhost;DRIVER={PostgreSQL};DATABASE=", input_db,
+					 ";PORT=5432;UID=", user_id, ";PWD=", user_passwd ,";LowerCaseIdentifier=0", sep="")
+
+channel      <- odbcDriverConnect( conn_string)
+
+set_encoding <- sqlQuery(channel,"SET client_encoding='LATIN1'")
+
+#################################################################################################################
+
+gene_names_table <- sqlQuery ( channel, "select *
+										   			 from  id_scer_gene_name 
+										   			 where oln_id is not null 
+										   				   and uniprot_acc is not null; ")
+
+write.table (gene_names_table, file.path(data_directory, "gene_names_table.txt"), row.names = FALSE, sep="\t", quote=FALSE )
+
+
+#################################################################################################################
+
+hc_transcriptional_regulatory_network <- sqlQuery(channel, "select * from tf_high_confidence_transcriptional_regulation_network;", stringsAsFactors=FALSE)
+
[…]

### 2017-08-05 Source/Figures/print_triplet_network.R

@@ -1,0 +1,66 @@
+### Script: print_triplet_network.R
+### Author: Ignatius Pang 
+### Date: 13-7-2016
+## Description: I want to visualize the network, which consists of all the triplet motifs. Only edges in triplet motifs are shown.
+
+library(RCy3)
+library(dplyr)
+
+#######################################################################################################################
+
+## Load the root base directory for the entire project
+options <- commandArgs(trailingOnly = TRUE)
+source( "./Common/parameters_file.R")
+
+source( file.path ( source_directory_common, 'draw_triplet_motif_network_helper.R') ) 
+
+#######################################################################################################################
+# Read through the list of all triplet motifs 
+
+triplet_motifs_costanzo <- readRDS( file=file.path( list_of_triplets_directory, "triplet_motifs_costanzo_2016.Rdata") ) 
+
+triplet_motifs_costanzo <- as.data.frame ( triplet_motifs_costanzo )
+
+
+
+gene_names <- read.table ( file.path(data_directory, "gene_names_table.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
+						   na.strings="", quote="")
+
+
+## Results from Spatial Analysis of Functional Enrichment (SAFE tool)
+
+enriched_functions <- read.table ( file.path( results_directory, "SAFE/safe_exported_reports_20161123.txt-node_properties_annotation-highest.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
+								   na.strings="", quote="")
+
+#######################################################################################################################
+
+cw <- draw_triplet_motif_network  ( triplet_motifs_costanzo, 'All triplets network' ) 
+
+triplet_motif_network_display_style(cw) 
+
+cw <- add_node_attributes(cw, gene_names , "oln_id")
+
+cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")
+
+empty_label_table <- gene_names %>% dplyr::mutate( empty_label = "") %>% dplyr::select ( one_of( c( 'oln_id', 'empty_label')))
+
+cw <- add_node_attributes ( cw, empty_label_table, "oln_id")
+
+setDefaultNodeSize( cw, new.size=0.1 )
+
+list_of_nodes <- nodes(getGraph(cw))
+
+# setNodeLabelDirect (cw, list_of_nodes, rep('', length(list_of_nodes)))
+
+setNodeLabelRule(cw, 'empty_label')
+
+displayGraph(cw)
+
+current_example_dir <- file.path( results_directory, "SAFE")
+
[…]

### 2017-08-05 Source/Figures/reshape_triplet_motifs_helper.R

@@ -1,0 +1,481 @@
+### Script: reshapte_triplet_motifs_helper.R
+### Author: Ignatius Pang 
+### Date: 13-7-2016
+### Description: Helper functions for plotting results for poster presentation.
+##                 * Compare observed and random values using box plot.
+##				   * Unpivot the full results table from randomization analyses
+
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Poster'
+# setwd ( '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Poster/')
+
+#####################################################################
+
+## unpivot the columns motif_type, observed, and random
+unpivot_tables <- function(input_table, treatment_group)  { 
+	input_table_tidy <- input_table %>% 
+		dplyr::rename( observed=observed_counts, random=mean)  %>%
+		dplyr::select( one_of(c("motif_type", "observed", "random") )) %>%
+		tidyr::gather(  "obs_or_rand", "value", -motif_type )
+	
+	input_table_tidy <- cbind( input_table_tidy, group=
+							   	rep(treatment_group, length(input_table_tidy[,1])))
+	
+	return(input_table_tidy )
+}
+
+#####################################################################
+
+## Compare observed and random values, significant p-value = red, insignificant p-value = blue
+
+significance_to_colour <- function ( p_value, threshold) {
+	
+	
+	if (is.null(p_value)   ) {
+		
+		return("blue")
+	} 
+	
+	if (  is.na( p_value) | is.infinite(p_value) | is.nan(p_value) ) {
+		
+		return("blue")
+		
+	}
+
+	if ( p_value >= threshold ) {
+		
+		return("blue")
+		
+	} else if ( p_value < threshold ) {
+		
+		return("red")
+		
+	} 
+	
+	return("blue")
+	
+}
+
+
+## Compare observed and random values, significant p-value = red, insignificant p-value = blue
+boolean_to_colour <- function ( x) {
+	
+	
+	if (is.null(x)   ) {
+		
+		return("blue")
+	} 
+	
+	if (  is.na( x) | is.infinite(x) | is.nan(x) ) {
+		
+		return("blue")
+		
+	}
+	
+	if ( x == TRUE ) {
+		
+		return("red")
+		
+	}
+	
+	
+	
+	if ( x == FALSE ) {
+		
+		return("blue")
+		
+	}
+
+	
+	return("blue")
+	
+}
+
+
+# Function: print_box_plot_observed_vs_random
+# Description:
[…]

### 2017-08-05 Source/Figures/reshape_triplet_motifs_results.R

@@ -1,0 +1,342 @@
+### Script: reshapte_triplet_motifs_results.R
+### Author: Ignatius Pang 
+### Date: 13-7-2016
+### Description: Plotting results for poster presentation.
+##                 * Compare observed value and frequency distribution of random values using box plots.
+##				   * Compare observed value and the average values from randomization analyses using bar plots.  
+
+# cd '/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Poster'
+
+base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs"
+
+setwd ( '/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Poster/')
+
+library(dplyr)
+library(tidyr)
+# library(ggraptR)
+library(ggplot2)
+library(reshape2)
+
+#####################################################################								 
+
+source( file.path ( base_directory, 'Source/Poster/reshape_triplet_motifs_helper.R') )
+
+computational_results_directory <- file.path ( base_directory, "Results/Bootstrap_p_values") 
+figures_results_directory       <- file.path ( base_directory, "Results/Poster/Figures" ) 
+
+plot_background_colour <- "white"   # "#7E4E99" # 
+axis_text_colour <- "black"  # "#FFC000" # 
+
+
+### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
+### This setting is for the poster presentation.
+graphic_width <- 5
+graphic_height <- 3
+
+#####################################################################								 
+
+false_positive_rates <- 0.02
+
+all_15_types_of_triplet_motifs <- c("pp" 
+									,"tutu"
+									,"pku"
+									,"kuku"
+									,"ptd"
+									,"kdku"
+									,"ptu"
+									,"tdtd"
+									,"pkd"
+									,"tdtu"
+									,"kdkd"
+									,"tuku"
+									,"tdku"
+									,"tdkd"
+									,"tukd")
+
+################################################################################################
+##### Using boxplot to show the random values and using a point to show the observed results  ##
+################################################################################################
+
+### Motifs that are significant. Sorted in decending order of the number of observed motifs.
+
+negative_interactions_full <- read.table ( file= file.path( computational_results_directory, 
[…]

### 2017-08-05 Source/Negative_GI_Essential/collate_results_neg_gi_essential.R

@@ -1,0 +1,61 @@
+library(dplyr)
+library(tidyr)
+library(ggraptR)
+library(ggplot2)
+library(reshape2)
+
+#####################################################################								 
+
+### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
+### This setting is for the poster presentation.
+
+base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
+
+source_directory <- paste( base_directory, "Source/", sep="")
+source_directory_common <- paste( source_directory, "Common/",  sep="")
+source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
+source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
+
+results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Negative_GI_Essential/", sep="")
+final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+
+	if (! file.exists(final_results_directory)){
+		dir.create(final_results_directory)
+
+	}
+
+################################################################################################################################################
+# Counts of Triplet Motifs Costanzo et al. 2010 dataset
+
+triplet_motifs_full_results_file     <- "full_results_table_count_a_and_b.tab"
+count_triplet_motifs_randomized_file <- "randomized_results_table_count_a_and_b.tab" 
+
+triplet_motifs_file_pattern      	 <- "^randomized_results_table_count_a_and_b.tab"
+observed_file_pattern        		 <-  "Job_20/observed_a_and_b_essential_gene_counts.tab"
+final_results_directory_pattern  <- "Final_Results"
+
+number_of_randomized_samples         <- 2000
+p_values 							 <- 0.05
+
+collate_result_files_helper ( results_directory, triplet_motifs_full_results_file, count_triplet_motifs_randomized_file,
+							  triplet_motifs_file_pattern, observed_file_pattern, final_results_directory_pattern,
+							  number_of_randomized_samples, p_values)
+
+################################################################################################################################################
+
+triplet_motifs_full_results_file     <- "full_results_table_count_c.tab"
+count_triplet_motifs_randomized_file <- "randomized_results_table_count_c.tab" 
+
+triplet_motifs_file_pattern          <- "^randomized_results_table_count_c.tab"
+observed_file_pattern                <- "Job_20/observed_c_essential_gene_counts.tab"
+final_results_directory_pattern  <- "Final_Results"
+
+number_of_randomized_samples         <- 2000
+p_values 							 <- 0.05
+
[…]

### 2017-08-05 Source/Negative_GI_Essential/run_triplet_motifs_neg_essential_genes_on_katana_array.sh

@@ -1,0 +1,78 @@
+#!/bin/bash
+
+#PBS -N TriMoEssen[]
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=100gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+# Clive
+### PBS -l epilogue=/share/bioinfo/igy/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
+
+## Katana
+#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
+
+# Command for running array jobs 
+#PBS -t 1-20
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+PROJECT_DIRECTORY=Negative_GI_Essential
+MAIN_SCRIPT="count_triplet_motifs_negative_gi_essential_genes.R"
+HPC_CLUSTER="katana"
+NUM_RANDOM_TRIALS=100
+LOG_PREFIX="count_triplet_motifs_essential_genes"
+
+if [ $HPC_CLUSTER = 'clive' ] 
+then 
+	## Clive
+	module load openmpi/1.10.3
+	module load R/3.3.1-bioconductor-3.3
+elif [ $HPC_CLUSTER = 'katana' ]
+then 
+	## Katana
+	module load openmpi/1.8.3
+	module load R/3.2.2
+else
+	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
+fi
+
+DATE=$(date +"%Y%m%d")
+
+export PROJECT_DIRECTORY
+
+### Create relevant directories
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}
+fi
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID}
+fi
+
[…]

### 2017-08-05 Source/Negative_Genetic_Interactions/collate_randomization_results_neg_gi.R

@@ -1,0 +1,53 @@
+
+library(dplyr)
+library(tidyr)
+library(ggraptR)
+library(ggplot2)
+library(reshape2)
+
+#####################################################################								 
+
+
+## Load all the parameters 
+options <- commandArgs(trailingOnly = TRUE)
+source( "../Common/parameters_file.R")
+
+
+### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
+### This setting is for the poster presentation.
+false_positive_rates <- 0.02
+
+source_directory <- paste( base_directory, "Source/", sep="")
+source_directory_common <- paste( source_directory, "Common/",  sep="")
+source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
+source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
+
+results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Negative_Genetic_Interactions/", sep="")
+final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+
+################################################################################################################################################
+
+# Counts of Triplet Motifs Costanzo et al. 2010 dataset
+triplet_motifs_file_pattern      	 <- "^randomized_results_table*"
+triplet_motifs_full_results_file     <- "full_results_triplet_motifs_costanzo_2016_collated.tab"
+count_triplet_motifs_randomized_file <- "randomized_counts_triplet_motifs.tab" 
+observed_file_pattern 	 	 <- "Job_21/results_count_triplet_motifs_costanzo.tab"
+final_results_directory_pattern  <- "Final_Results"
+number_of_randomized_samples         <- 2000
+p_values 						   	 <- 0.05
+
+final_results_table_count_triplet_motifs <- collate_result_files_helper ( results_directory, 
+																		  triplet_motifs_full_results_file, count_triplet_motifs_randomized_file,
+							  triplet_motifs_file_pattern, observed_file_pattern, final_results_directory_pattern, 
+							  number_of_randomized_samples, p_values)
+
+################################################################################################################################################
+
+rows_to_include  <-  (final_results_table_count_triplet_motifs[, "observed_counts"] > sum ( final_results_table_count_triplet_motifs[, "observed_counts"] ) * false_positive_rates)  &
+					(final_results_table_count_triplet_motifs[, "enrichment_adj_p_values"]  < p_values)
+
[…]

### 2017-08-05 Source/Negative_Genetic_Interactions/epilogue_array_jobs_testing.sh

@@ -1,0 +1,10 @@
+#! /bin/bash
+
+echo "epilogue: copy from local scratch to working directory"
+echo "    ${TMPDIR}"
+echo "    ${PBS_O_WORKDIR}"
+echo
+
+
+
+rsync -a ${TMPDIR}/* 	$PBS_O_WORKDIR/../Results/${PROJECT_DIRECTORY}

### 2017-08-05 Source/Negative_Genetic_Interactions/run_triplet_motifs_array_on_katana_generic_version.sh

@@ -1,0 +1,83 @@
+#!/bin/bash
+
+#PBS -N TriMotif[]
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=100gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+## Clive
+#### PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue_array_jobs.sh
+
+## Katana
+#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue_array_jobs.sh
+
+# Command for running array jobs 
+#PBS -t 1-20
+
+PROJECT_DIRECTORY=Negative_Genetic_Interactions
+MAIN_SCRIPT=count_triplet_motifs_negative_interactions.R
+HPC_CLUSTER="clive"
+NUM_RANDOM_TRIALS=100
+LOG_PREFIX="count_triplet_motifs_neg_int"
+
+if [ $HPC_CLUSTER = 'clive' ] 
+then 
+	## Clive
+	module load openmpi/1.10.3
+	module load R/3.3.1-bioconductor-3.3
+elif [ $HPC_CLUSTER = 'katana' ]
+then 
+	## Katana
+	module load openmpi/1.8.3
+	module load R/3.2.2
+else
+	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
+fi
+
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+DATE=$(date +"%Y%m%d")
+
+
+export PROJECT_DIRECTORY
+
+### Create relevant directories
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}
+fi
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID}
+fi
+
[…]

### 2017-08-05 Source/Negative_Genetic_Interactions/transfer_files_to_various_clusters.sh

@@ -1,0 +1,41 @@
+
+## Transfer scripts on testing negative genetic interactions from Rm244 to clusters (array job )
+
+
+### Clive
+
+rsync -avh /media/z3371724/PostDoc/2016/Triplet_Motifs/Data/Triplet_Motifs_R_data/network_data_library.Rdata z3371724@clive:/share/bioinfo/igy/Triplet_Motifs/Data
+
+
+## Send the common scripts over to clive
+rsync -avh /media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/count_triplet_motifs_helper.R z3371724@clive:/share/bioinfo/igy/Triplet_Motifs/Source
+rsync -avh /media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R             z3371724@clive:/share/bioinfo/igy/Triplet_Motifs/Source
+
+
+rsync -avh /media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Negative_Genetic_Interactions/count_triplet_motifs_negative_interactions.R    z3371724@clive:/share/bioinfo/igy/Triplet_Motifs/Source/Negative_Genetic_Interactions/
+rsync -avh /media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Negative_Genetic_Interactions/run_triplet_motifs_array_on_clive.sh z3371724@clive:/share/bioinfo/igy/Triplet_Motifs/Source/Negative_Genetic_Interactions/
+rsync -avh /media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Negative_Genetic_Interactions/epilogue_array_jobs.sh z3371724@clive:/share/bioinfo/igy/Triplet_Motifs/Source/Negative_Genetic_Interactions/
+
+## Testing scripts
+rsync -avh /media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file_small_tests.R             z3371724@clive:/share/bioinfo/igy/Triplet_Motifs/Source/Negative_Genetic_Interactions/
+rsync -avh /media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Negative_Genetic_Interactions/run_triplet_motifs_array_on_clive_generic_version.sh z3371724@clive:/share/bioinfo/igy/Triplet_Motifs/Source/Negative_Genetic_Interactions/
[…]

### 2017-08-05 Source/Overexpressed_Toxic_Genes/collate_results_overexpression.R

@@ -1,0 +1,58 @@
+library(dplyr)
+library(tidyr)
+library(ggraptR)
+library(ggplot2)
+library(reshape2)
+
+#####################################################################								 
+
+### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
+### This setting is for the poster presentation.
+
+base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
+
+source_directory <- paste( base_directory, "Source/", sep="")
+source_directory_common <- paste( source_directory, "Common/",  sep="")
+source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
+source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
+
+results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Overexpressed_Toxic_Genes/", sep="")
+final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+
+	if (! file.exists(final_results_directory)){
+		dir.create(final_results_directory)
+
+	}
+
+
+################################################################################################################################################
+# Counts of Triplet Motifs Costanzo et al. 2010 dataset
+
+final_results_directory_pattern      <- "Final_Results"
+number_of_randomized_samples         <- 2000
+p_values 							 <- 0.05
+
+## A--B
+triplet_motifs_full_results_file     <- "full_results_table_overexpressed_toxic_gene_counts_a_and_b.tab"
+count_triplet_motifs_randomized_file <- "randomized_results_table_overexpressed_toxic_gene_counts_a_and_b.tab" 
+
+triplet_motifs_file_pattern      	 <- "^randomized_results_table_overexpressed_toxic_gene_counts_a_and_b.tab"
+observed_file_pattern        		 <-  "Job_20/observed_a_and_b_overexpressed_toxic_gene_counts.tab"
+
+collated_table <- collate_result_files_helper ( results_directory, triplet_motifs_full_results_file, count_triplet_motifs_randomized_file,
+							  triplet_motifs_file_pattern, observed_file_pattern, final_results_directory_pattern,
+							  number_of_randomized_samples, p_values)
+
+
+## C
+triplet_motifs_full_results_file     <- "full_results_table_overexpressed_toxic_gene_counts_c.tab"
+count_triplet_motifs_randomized_file <- "randomized_results_table_overexpressed_toxic_gene_counts_c.tab" 
+
[…]

### 2017-08-05 Source/Overexpressed_Toxic_Genes/count_triplet_motifs_overexpression.R

@@ -1,0 +1,160 @@
+### Script: count_triplet_motifs_overexpression.R
+### Author: Ignatius Pang 
+### Date: 27-5-2016
+### Description: Count the observed number of essential genes in triplet motifs. 
+### Randomize the respective networks and count the number of esential genes in triplet motifs. Keep the essential genes the same, only randomize the edges.
+### Repeat randomization 2000 times.
+### Obtain the bootstrap p-value
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# 
+
+#########################################################
+### Parameters 
+options <- commandArgs(trailingOnly = TRUE)
+
+### Source the parameters file here 
+
+if ( length(options) != 0 
+	 & ( options[1] == 'katana' | options[1] == 'clive')  ) {
+	source( "./parameters_file.R" )
+
+} else {
+	source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+}
+
+### Local Parameters
+if (is_run_locally) {
+	
+	results_directory <- paste (base_directory,"esults/Bootstrap_p_values_temp/Overexpressed_Toxic_Genes/", sep="")
+}
+
+
+observed_a_and_b_overexpressed_toxic_gene_counts <- "observed_a_and_b_overexpressed_toxic_gene_counts.tab"
+observed_c_overexpressed_toxic_gene_counts 	   <- "observed_c_overexpressed_toxic_gene_counts.tab"
+
+randomized_count_a_and_b_table_file 	<- "randomized_results_table_overexpressed_toxic_gene_counts_a_and_b.tab"
+randomized_count_c_table_file 		<- "randomized_results_table_overexpressed_toxic_gene_counts_c.tab"
+
+output_full_results_table_count_a_and_b	<- "full_results_table_overexpressed_toxic_gene_counts_a_and_b.tab"		  
+output_full_results_table_count_c  	<- "full_results_table_overexpressed_toxic_gene_counts_c.tab"
+
+## Tidy up overexpression table 
+overexpressed_toxic_genes <- as.data.frame( overexpressed_toxic_genes[, "oln_id"])
+colnames( overexpressed_toxic_genes) <- "oln_id"
+
+#########################################################
+
+#### Get the actual observed number of triplet motifs
+
[…]

### 2017-08-05 Source/Overexpressed_Toxic_Genes/run_triplet_motifs_overexpression_on_katana_array.sh

@@ -1,0 +1,81 @@
+#!/bin/bash
+
+#PBS -N TriMoOx[]
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=100gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+# Clive
+##### PBS -l epilogue=/share/bioinfo/igy/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
+
+## Katana
+#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
+
+# Command for running array jobs 
+#PBS -t 1-20
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+PROJECT_DIRECTORY=Overexpressed_Toxic_Genes
+MAIN_SCRIPT="count_triplet_motifs_overexpression.R"
+HPC_CLUSTER="katana"
+NUM_RANDOM_TRIALS=100
+LOG_PREFIX="count_triplet_motifs_overexpression"
+
+if [ $HPC_CLUSTER = 'clive' ] 
+then 
+	## Clive
+	module load openmpi/1.10.3
+	module load R/3.3.1-bioconductor-3.3
+elif [ $HPC_CLUSTER = 'katana' ]
+then 
+	## Katana
+	module load openmpi/1.8.3
+	module load R/3.2.2
+else
+	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
+fi
+
+DATE=$(date +"%Y%m%d")
+
+export PROJECT_DIRECTORY
+
+### Create relevant directories
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}
+fi
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID}
+fi
+
[…]

### 2017-08-05 Source/Paralogs/collate_results_paralogs.R

@@ -1,0 +1,46 @@
+library(dplyr)
+library(tidyr)
+# library(ggraptR)
+library(ggplot2)
+library(reshape2)
+
+#####################################################################								 
+
+### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
+### This setting is for the poster presentation.
+
+base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/"
+
+source_directory <- paste( base_directory, "Source/", sep="")
+source_directory_common <- paste( source_directory, "Common/",  sep="")
+source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
+source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
+
+# results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Paralogs/", sep="")
+results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Paralogs_Not_Randomize_GI/", sep="")
+
+final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+
+	if (! file.exists(final_results_directory)){
+		dir.create(final_results_directory)
+
+	}
+
+
+################################################################################################################################################
+# Counts of Triplet Motifs Costanzo et al. 2010 dataset
+
+triplet_motifs_full_results_file     <- "full_results_table_orthomcl_paralogs_in_tri_motifs.tab"
+count_triplet_motifs_randomized_file <- "randomized_counts_orthomcl_paralogs_in_tri_motifs.tab" 
+
+triplet_motifs_file_pattern      	 <- "^randomized_counts_orthomcl_paralogs_in_tri_motifs.tab"
+observed_file_pattern        		 <-  "Job_20/observed_counts_orthomcl_paralogs_in_tri_motifs.tab"
+final_results_directory_pattern      <- "Final_Results"
+number_of_randomized_samples         <- 2000
+p_values 							 <- 0.05
+
+collated_table <- collate_result_files_helper ( results_directory, triplet_motifs_full_results_file, count_triplet_motifs_randomized_file,
+							  triplet_motifs_file_pattern, observed_file_pattern, final_results_directory_pattern,
+							  number_of_randomized_samples, p_values)
+
+

### 2017-08-05 Source/Paralogs/count_triplet_motifs_paralogs.R

@@ -1,0 +1,235 @@
+### Script: count_triplet_motifs_paralogs.R
+### Author: Ignatius Pang 
+### Date: 27-5-2016
+### Description: For each type of triplet motif, count the number of motifs in which the edge with the negative genetic interaction 
+### consist of a pair of paralogous genes . 
+### Repeat the same calculation with randomizated 2000 networks and obtain the bootstrap p-value.
+### Randomization conserves the degree distribution of the network. 
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# 
+
+#########################################################
+### Parameters 
+options <- commandArgs(trailingOnly = TRUE)
+
+### Source the parameters file here 
+if ( length(options) != 0  )  { 
+	if ( options[1] == 'katana' | options[1] == 'clive')   {
+		source( "./parameters_file.R" )
+
+	} else {
+		source( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+	}	
+} else {
+	source( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+}	
+
+### Local Parameters
+if (is_run_locally) {
+
+	results_directory <- paste( base_directory, "Results/Bootstrap_p_values/Paralogs/", sep="")
+}
+
+observed_counts_orthomcl_paralogs_file	 <- "observed_counts_orthomcl_paralogs_in_tri_motifs.tab"
+observed_counts_sgd_paralogs_file	     <- "observed_counts_sgd_paralogs_in_tri_motifs.tab"
+
+randomized_counts_orthomcl_paralogs_file <- "randomized_counts_orthomcl_paralogs_in_tri_motifs.tab"
+randomized_counts_sgd_paralogs_file      <- "randomized_counts_sgd_paralogs_in_tri_motifs.tab"
+			  
+full_results_orthomcl_paralogs_file 	 <- "full_results_table_orthomcl_paralogs_in_tri_motifs.tab"		  
+full_results_sgd_paralogs_file  	     <- "full_results_table_sgd_paralogs_in_tri_motifs.tab"
+
+#########################################################
+#### Get the actual observed number of triplet motifs
+
+my_join_ac <- c( "query_oln_id_edited" = "oln_id_a")
[…]

### 2017-08-05 Source/Paralogs/run_triplet_motifs_with_paralogs_on_katana_array.sh

@@ -1,0 +1,81 @@
+#!/bin/bash
+
+#PBS -N TriMotPara[]
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=100gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+# Clive
+#### PBS -l epilogue=/share/bioinfo/igy/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
+
+## Katana
+#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
+
+# Command for running array jobs 
+#PBS -t 1-20
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+PROJECT_DIRECTORY=Paralogs
+MAIN_SCRIPT="count_triplet_motifs_paralogs.R"
+HPC_CLUSTER="katana"
+NUM_RANDOM_TRIALS=100
+LOG_PREFIX="count_triplet_motifs_paralogs"
+
+if [ $HPC_CLUSTER = 'clive' ] 
+then 
+	## Clive
+	module load openmpi/1.10.3
+	module load R/3.3.1-bioconductor-3.3
+elif [ $HPC_CLUSTER = 'katana' ]
+then 
+	## Katana
+	module load openmpi/1.8.3
+	module load R/3.2.2
+else
+	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
+fi
+
+DATE=$(date +"%Y%m%d")
+
+export PROJECT_DIRECTORY
+
+### Create relevant directories
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}
+fi
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID}
+fi
+
[…]

### 2017-08-05 Source/Protein_Complexes/collate_results_protein_complexes.R

@@ -1,0 +1,44 @@
+library(dplyr)
+library(tidyr)
+library(ggraptR)
+library(ggplot2)
+library(reshape2)
+
+#####################################################################								 
+
+### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
+### This setting is for the poster presentation.
+
+base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
+
+source_directory <- paste( base_directory, "Source/", sep="")
+source_directory_common <- paste( source_directory, "Common/",  sep="")
+source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
+source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
+
+results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Protein_Complexes/", sep="")
+final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+
+	if (! file.exists(final_results_directory)){
+		dir.create(final_results_directory)
+
+	}
+
+
+################################################################################################################################################
+# Counts of Triplet Motifs Costanzo et al. 2010 dataset
+
+triplet_motifs_full_results_file     <- "full_results_table_benschop_protein_complex_in_tri_motifs.tab"
+count_triplet_motifs_randomized_file <- "randomized_counts_benschop_protein_complex_in_tri_motifs.tab" 
+
+triplet_motifs_file_pattern      	 <- "^randomized_counts_benschop_protein_complex_in_tri_motifs.tab"
+observed_file_pattern        		 <-  "Job_20/observed_counts_benschop_protein_complex_in_tri_motifs.tab"
+final_results_directory_pattern      <- "Final_Results"
+number_of_randomized_samples         <- 2000
+p_values 							 <- 0.05
+
+collated_table <- collate_result_files_helper ( results_directory, triplet_motifs_full_results_file, count_triplet_motifs_randomized_file,
+							  triplet_motifs_file_pattern, observed_file_pattern, final_results_directory_pattern,
+							  number_of_randomized_samples, p_values)
+
+

### 2017-08-05 Source/Protein_Complexes/count_triplet_motifs_protein_complexes.R

@@ -1,0 +1,208 @@
+### Script: count_triplet_motifs_negative_gi_essential_genes.R
+### Author: Ignatius Pang 
+### Date: 27-5-2016
+### Description: Count the observed number of triplet motifs in which the protein products of all three genes are found in the same protein complex. 
+### Repeat the same calculation with randomizated 2000 networks and obtain the bootstrap p-value.
+### Randomization conserves the degree distribution of the network. 
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# 
+
+#########################################################
+### Parameters 
+options <- commandArgs(trailingOnly = TRUE)
+
+### Source the parameters file here 
+if ( length(options) != 0  )  { 
+	if ( options[1] == 'katana' | options[1] == 'clive')   {
+		source( "./parameters_file.R" )
+
+	} else {
+		source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+	}
+}
+
+### Local Parameters
+if (is_run_locally) {
+
+	results_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/Protein_Complexes/"
+}
+
+observed_counts_babu_protein_complex_file        <- "observed_counts_babu_protein_complex_in_tri_motifs.tab"
+observed_counts_benschop_protein_complex_file    <- "observed_counts_benschop_protein_complex_in_tri_motifs.tab"
+
+randomized_counts_babu_protein_complex_file 	 <- "randomized_counts_babu_protein_complex_in_tri_motifs.tab"
+randomized_counts_benschop_protein_complex_file  <- "randomized_counts_benschop_protein_complex_in_tri_motifs.tab"
+			  
+full_results_babu_protein_complex_file 		     <- "full_results_babu_protein_complex_in_tri_motifs.tab"
+full_results_benschop_protein_complex_file  	 <- "full_results_table_benschop_protein_complex_in_tri_motifs.tab"
+
+#########################################################
+
+#### Get the actual observed number of triplet motifs
+
+my_join_ac <- c( "query_oln_id_edited" = "oln_id_a")
+my_join_bc <- c( "array_oln_id_edited"= "oln_id_a", "oln_id_b" = "oln_id_b" )
+my_selected_columns <- c("query_oln_id_edited", "array_oln_id_edited", 
+						 "oln_id_b",  "interaction_type_abbrev.x",
[…]

### 2017-08-05 Source/Protein_Complexes/run_triplet_motifs_in_protein_complexes_on_katana.sh

@@ -1,0 +1,27 @@
+#!/bin/bash
+
+#PBS -N TriMoComplex
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=8gb
+#PBS -l walltime=11:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue.sh
+
+module load openmpi/1.8.3
+module load R/3.2.2
+
+DATE=$(date +"%Y%m%d")
+
+cd $PBS_O_WORKDIR
+
+rsync -a ${PBS_O_WORKDIR}/count_triplet_motifs_helper.R ${TMPDIR}
+rsync -a ${PBS_O_WORKDIR}/count_triplet_motifs_protein_complexes.R ${TMPDIR}
+rsync -a ${PBS_O_WORKDIR}/network_data_library.Rdata ${TMPDIR}
+
+cd $TMPDIR
+
+Rscript --vanilla  count_triplet_motifs_protein_complexes.R katana > count_triplet_motif_protein_complexes_$DATE.log
+
+

### 2017-08-05 Source/Random_Edges/collate_random_edges_results.R

@@ -1,0 +1,180 @@
+library(tidyr)
+library(dplyr)
+library(ggplot2)
+library(lazyeval)
+
+source('/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Random_Edges/collate_random_edges_results_helper.R')
+source('/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Poster/reshape_triplet_motifs_helper.R')
+
+### Directories
+results_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/Random_Edges/"
+
+final_results_directory <- paste ( results_directory, "Final_Results/", sep="")
+
+### Size of resulting plot 
+graphic_width  <- 10 
+graphic_height <- 10
+	
+### Parameter space
+PERCENTAGE_OF_ORIGINAL_NETWORK <- seq( 0.2, 1.3, 0.1 )
+INNER_LOOP <- seq(1, 20, 1)
+
+JOB_NUMBERS <- 0:239  ## Need to be upldated once the corrected results has been calculated by Katana
+adjust_job_number <- 1 ## Add this number to the job number to access the correct position in the  PARAMS array
+
+## Use purple background and create a subset of the triplet motifs for the poster
+print_poster_results_purple_background <- TRUE
+
+plot_background_colour <- "white"  
+axis_text_colour       <- "black" 
+
+if ( print_poster_results_purple_background== TRUE) {
+	plot_background_colour <-  "white" # "#7E4E99" 
+	axis_text_colour       <-  "black" # "#FFC000" 
+}
+
+##########################################################################################################
+
+PARAMS <- c()
+
+for( PERCENTAGE in PERCENTAGE_OF_ORIGINAL_NETWORK ) {
+	
+	for ( LOOP_COUNT in INNER_LOOP ) { 
+
+		PARAMS <- c( PARAMS, PERCENTAGE) 
+	}
+}
+
+
+# random_edges_after_randomization_counts_0.2_1_1_1_.tab
+# random_edges_before_randomization_counts_0.2_1_1_1_.tab
+
+prev_step_network_size <- 0 
+
+before_randomization_file_list <- c()
+after_randomization_file_list <- c() 
+
+for ( job_number in JOB_NUMBERS) {
+
+	proprotion_of_original_network_size <- PARAMS[job_number+adjust_job_number]
+
+	
+	before_randomization_file_list <- c(before_randomization_file_list, 
[…]

### 2017-08-05 Source/Random_Edges/collate_random_edges_results_helper.R

@@ -1,0 +1,240 @@
+library(tidyr)
+library(dplyr)
+library(ggplot2)
+library(lazyeval)
+
+
+#####################################################################################################################################
+
+collate_different_datasets <- function( results_directory, list_of_file_names, strsplit_pattern = '_', position_of_parameter = 6, expt_label) { 
+	collated_table <- NULL
+	
+	prev_parameter <- -1000 # Dummy value 
+	expt_number_counter <- 0 
+	
+	for ( i in 1:length ( list_of_file_names)) { 
+		
+		current_file_name <- list_of_file_names[i]
+		
+		file_name_splitted <- strsplit (current_file_name, strsplit_pattern )
+		
+		parameter_to_capture <- as.numeric( file_name_splitted[[1]][position_of_parameter] )
+		
+		if ( prev_parameter != parameter_to_capture ) {
+			
+			prev_parameter <- parameter_to_capture
+			expt_number_counter <- 0
+		}
+		
+		one_data_table <- read.table ( paste( results_directory, current_file_name, sep=""), header=TRUE)
+		
+		motif_types <- colnames( one_data_table)
+		
+		row_sums <- as.data.frame( rowSums( one_data_table, na.rm=TRUE) )
+		colnames(row_sums) <- 'total'
+		
+		## Continue with the experiment number if the network size parameter is the same, otherwise reset to zero
+		expt_number <- as.data.frame( (1+expt_number_counter):(length(one_data_table[,1] )+expt_number_counter) )
+		
+		expt_number_counter <- expt_number_counter + length ( one_data_table[,1])
+	
+		colnames( expt_number) <- 'expt_number'
+		
+		# print ( "hello")
+		# print( dim(row_sums))
+		# print (dim( expt_number))		
+		# print ( dim(one_data_table ))
+		
+		one_data_table <- cbind( one_data_table, total=row_sums, number=expt_number)
+		
+		columns_to_get <- which ( colnames(one_data_table ) %in%  c( motif_types, 'total'))
+		
+		one_data_table_gathered <- tidyr::gather ( one_data_table, 'motif_type', 'counts',
+												   columns_to_get)
+		
+		
+		parameter_column_data <- rep( parameter_to_capture, length ( one_data_table_gathered[,1]) ) 
+		expt_label_column_data <- rep( expt_label, length ( one_data_table_gathered[,1]) ) 
+		
+		one_data_table_gathered <- cbind( experiment= expt_label_column_data,
+										  parameter = parameter_column_data,
[…]

### 2017-08-05 Source/Random_Edges/count_triplet_motifs_random_edges.R

@@ -1,0 +1,265 @@
+### Script: count_triplet_motifs_random_edges.R
+### Author: Ignatius Pang 
+### Date: 20-5-2016
+### Description:Randomly add or remove edges to change the size of the network based on the original network size, count the number of motifs. Randomize the network and count the number triplet motifs. Repeat the above steps 2000 times.
+### Obtain the bootstrap p-value
+
+library(igraph)
+library(dplyr)
+library(lazyeval)
+library(parallel)
+
+sessionInfo()
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# Rscript --vanilla count_triplet_motifs_random_edges.R local 0.5 1 1 1  
+
+#########################################################
+### Parameters 
+options <- commandArgs(trailingOnly = TRUE)
+
+### Source the parameters file here 
+if ( length(options) != 0  )  { 
+	if ( options[1] == 'katana' | options[1] == 'clive')   {
+		source( "./parameters_file.R" )
+	} else {
+		print ('Load parameter file locally.')
+		source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+	}
+	
+} else {
+	print ('Load parameter file locally.')
+	source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+}
+
+source_directory_random_edges <- "./"
+
+if (is_run_locally) {
+	results_directory <- paste( base_directory, "Results/Bootstrap_p_values/Random_Edges/", sep="")
+	source_directory_random_edges <- paste( source_directory, "Random_Edges/", sep="")
+}
+
+source( paste (source_directory_random_edges, "random_edges_helper.R", sep="" ))
+
+### Local Parameters
+
+### Randomly add or remove edges to change the size of the network based on the original network size
+proportion_of_original_network_size_gi_network      <- 0.5 # Default no change at all
+proportion_of_original_network_size_kinase_network  <- 1
+proportion_of_original_network_size_ppi_network     <- 1 
+proportion_of_original_network_size_tf_network      <- 1
+
+
+if ( length(options) != 0 
+	 & ( options[1] == 'katana' | options[1] == 'clive') ) {
+	
+	if ( length( options ) != 7 ) {
+
+		 stop_program_notification_string <- paste('Not enough command line arguments.', 
[…]

### 2017-08-05 Source/Random_Edges/random_edges_helper.R

@@ -1,0 +1,151 @@
+#########################################################
+
+randomly_add_or_remove_edges_from_network <- function ( network_edge_list, proportion, column_a, column_b,   
+                                                        directed = FALSE, 
+                                                        simple_network = TRUE,
+                                                        maximum_num_of_tries = 10) {
+
+  network_edge_list <- clean_up_network (  network_edge_list, column_a, column_b, directed=directed) 
+
+  if ( proportion > 1) {
+    
+    network_edge_list <- randomly_add_edges_to_network(  network_edge_list,  proportion  - 1, column_a, column_b,   
+                                                         directed = directed, 
+                                                         simple_network = simple_network,
+                                                         maximum_num_of_tries = maximum_num_of_tries  ) 
+  } else if ( proportion < 1) {
+    
+    network_edge_list <- randomly_remove_edges_from_network   (  network_edge_list, 1- proportion  ) 
+  } 
+
+  return (network_edge_list ) 
+}
+
+
+
+######
+# Floor of proportion_to_remove * number of edges in the network is used to determine the number of edges to remove 
+randomly_remove_edges_from_network  <- function (  network_edge_list,  proportion_to_remove ) {
+  
+  
+  if ( proportion_to_remove >= 1) {
+    
+    stop ( "randomly_remove_edges_from_undirected_network: proportion to remove needs to be smaller than 1")
+    
+  }
+  
+  sampled_network <- sample_frac(network_edge_list, size=1-proportion_to_remove, replace = FALSE)
+  
+  return( sampled_network)  
+}
+
+
+randomly_add_edges_to_network <- function (  network_edge_list,  proportion_to_add, column_a, column_b,   
+                                                        directed = FALSE, 
+											 			simple_network = TRUE,
+                                                        maximum_num_of_tries = 10 ) {
+  
+  edge_list <- dplyr::select( network_edge_list, one_of ( c(column_a, column_b) ))
+  
[…]

### 2017-08-05 Source/Random_Edges/run_triplet_motifs_random_edges.sh

@@ -1,0 +1,68 @@
+#!/bin/bash
+
+#PBS -N TriMoRandEdge
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=16gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue_random_edges.sh
+
+# Command for running array jobs 
+#PBS -t 0-10
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+module load openmpi/1.8.3
+module load R/3.2.2
+
+DATE=$(date +"%Y%m%d")
+
+### Create relevant directories
+
+if [ ! -d $PBS_O_WORKDIR/../Results/Random_Edges ]; then
+  mkdir $PBS_O_WORKDIR/../Results/Random_Edges
+fi
+
+if [ ! -d $PBS_O_WORKDIR/../Log/Random_Edges ]; then
+  mkdir $PBS_O_WORKDIR/../Log/Random_Edges
+fi
+
+if [ ! -d $PBS_O_WORKDIR/Random_Edges ]; then
+  mkdir $PBS_O_WORKDIR/Random_Edges
+fi
+
+if [ ! -d $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID} ]; then
+  mkdir $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
+fi
+
+PARAMS=( 0.2 0.3 0.4 0.5 0.6 0.7 0.8 0.9 1.1 1.2 1.3 )
+
+network_size_proportion=${PARAMS[${PBS_ARRAYID}]}
+
+cd $PBS_O_WORKDIR/JDD
+
+rsync -a ${PBS_O_WORKDIR}/count_triplet_motifs_helper.R 	  $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
+rsync -a ${PBS_O_WORKDIR}/random_edges_helper.R 			  $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
+rsync -a ${PBS_O_WORKDIR}/count_triplet_motifs_random_edges.R $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
[…]

### 2017-08-05 Source/Random_Edges/run_triplet_motifs_random_edges_array_katana.sh

@@ -1,0 +1,106 @@
+#!/bin/bash
+
+#PBS -N TriMoRandEdge[]
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=100gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+## Clive
+#### PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue_array_jobs.sh
+
+## Katana
+#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue_array_jobs.sh
+
+# Command for running array jobs 
+#PBS -t 1-240
+
+
+PROJECT_DIRECTORY=Random_Edges
+MAIN_SCRIPT=count_triplet_motifs_random_edges.R
+HPC_CLUSTER="katana"
+NUM_RANDOM_TRIALS=100
+LOG_PREFIX="count_triplet_motifs_random_edges_gi"
+
+PERCENTAGE_OF_ORIGINAL_NETWORK=$( seq 0.2 0.1 1.3 )
+INNER_LOOP=$(seq 1 1 20)
+PARAMS=()
+
+for PERCENTAGE in $PERCENTAGE_OF_ORIGINAL_NETWORK
+do
+
+	for OUTPUT in $INNER_LOOP
+	do
+		echo $PERCENTAGE
+		PARAMS+=($PERCENTAGE)
+	done
+done
+
+# echo ${PARAMS[*]}
+#exit
+
+ARRAY_POSITION="$((PBS_ARRAYID - 1))"  
+
+network_size_proportion=${PARAMS[${ARRAY_POSITION}]}
+
+
+if [ $HPC_CLUSTER = 'clive' ] 
+then 
+	## Clive
+	module load openmpi/1.10.3
+	module load R/3.3.1-bioconductor-3.3
+elif [ $HPC_CLUSTER = 'katana' ]
+then 
+	## Katana
+	module load openmpi/1.8.3
+	module load R/3.2.2
+else
+	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
+fi
+
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+DATE=$(date +"%Y%m%d")
+
+
+export PROJECT_DIRECTORY
+
[…]

### 2017-08-05 Source/Random_Edges/run_triplet_motifs_random_edges_on_clive.sh

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+#PBS -N TriMoRandEdge
+#PBS -l nodes=1:ppn=24
+#PBS -l vmem=100gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+#PBS -l epilogue=/share/bioinfo/igy/Triplet_Motifs/Source/epilogue_random_edges.sh
+
+# Command for running array jobs 
+#PBS -t 0-10
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+#### To delete the array jobs
+# qdel -t 4-10 1182[]
+
+module load openmpi/1.10.3
+module load R/3.3.1-bioconductor-3.3
+
+DATE=$(date +"%Y%m%d")
+
+### Create relevant directories
+
+if [ ! -d $PBS_O_WORKDIR/../Results/Random_Edges ]; then
+  mkdir $PBS_O_WORKDIR/../Results/Random_Edges
+fi
+
+if [ ! -d $PBS_O_WORKDIR/../Log/Random_Edges ]; then
+  mkdir $PBS_O_WORKDIR/../Log/Random_Edges
+fi
+
+if [ ! -d $PBS_O_WORKDIR/Random_Edges ]; then
+  mkdir $PBS_O_WORKDIR/Random_Edges
+fi
+
+if [ ! -d $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID} ]; then
+  mkdir $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
+fi
+
+PARAMS=( 0.2 0.3 0.4 0.5 0.6 0.7 0.8 0.9 1.1 1.2 1.3 )
+
+network_size_proportion=${PARAMS[${PBS_ARRAYID}]}
+
+cd $PBS_O_WORKDIR/JDD
+
+rsync -a ${PBS_O_WORKDIR}/count_triplet_motifs_helper.R 	$PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
+rsync -a ${PBS_O_WORKDIR}/random_edges_helper.R 		$PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
[…]

### 2017-08-05 Source/Random_Edges/test_random_edges.R

@@ -1,0 +1,245 @@
+
+### Script: test_random_edges.R
+### Author: Ignatius Pang 
+### Date: 20-5-2016
+### Description: Test random additions or deletion of edges 
+
+library(igraph)
+library(dplyr)
+library(lazyeval)
+library(parallel)
+
+sessionInfo()
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# 
+
+#########################################################
+### Parameters 
+options <- commandArgs(trailingOnly = TRUE)
+
+is_rm244 <- TRUE
+
+if ( length(options) != 0 
+     & options[1] == 'katana') {
+  is_rm244 <- FALSE
+}
+
+print (is_rm244)
+
+random_number_seed <- 1985
+number_of_cores_to_use <- 16
+number_of_randomized_trials <- 2000
+num_iteration_rewire_network <- NULL # Number of times each network is rewired before counting the triplet motifs
+
+data_directory <- "./"
+source_directory <- "./"
+results_directory <- "./"
+source_directory_random_edges <- "./"
+
+before_transpose_triplet_motif_counts <- "results_count_triplet_motifs_before_transpose_costanzo.tab"
+output_observed_triplet_motif_counts <- "results_count_triplet_motifs_costanzo.tab" # "results_count_triplet_motifs_costanzo.tab"
+randomized_results_table_file <- "randomized_results_table.tab"
+output_enrichment_p_value <- "enrichment_p_value_fixed.tab"
+output_depletion_p_value <- "depletion_p_value_fixed.tab"
+output_full_results_table <- "full_results_table.tab"
+
+if (is_rm244) {
+  random_number_seed <- 1985
+  number_of_cores_to_use <- 4
+  number_of_randomized_trials <- 4
+  num_iteration_rewire_network <- 0 # Number of times each network is rewired before counting the triplet motifs
+  
+  #base_directory <- "C:/Users/home/Desktop/Triplet_Motifs/"
+   base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
+  
+  data_directory <- paste( base_directory, "Data/Triplet_Motifs_R_data/", sep="")
+  source_directory <- paste( base_directory, "Source/", sep="")
[…]

### 2017-08-05 Results/Bootstrap_p_values/Analyze_GI_edges/Job_40/compare_triplet_motif_gi_with_other_networks.R
Convert 'paste' to 'file.path'. Ensure parameters_file.R is used whenever possible.

@@ -1,335 +1,0 @@
-### Script: compare_triplet_motif_gi_with_other_networks.R
-### Author: Ignatius Pang 
-### Date: 22-8-2016
-### Description: Compare the genetic interaction edge in triplet motifs with other types of interactions. 
-
-#########################################################
-# Source location
-
-# psql sbi_triplet_motifs
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
-# 
-
-#########################################################
-### Parameters 
-### Global Parameters 
-
-options <- commandArgs(trailingOnly = TRUE)
-
-### Source the header file here 
-
-if ( length(options) != 0 
-	 & ( options[1] == 'katana' | options[1] == 'clive')  ) {
-	source( "./parameters_file.R" )
-
-} else {
-	source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
-}
-
-### Local Parameters
-observed_results_table_file   <- "observed_results_table_file.tab"
-randomized_results_table_file <- "randomized_results_table.tab"
-# output_enrichment_p_value     <- "enrichment_p_value_fixed.tab"
-# output_depletion_p_value      <- "depletion_p_value_fixed.tab"
-output_full_results_table     <- "full_results_table.tab"
-
-if (is_run_locally) {
-	
-	results_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/Analyze_GI_edges/"
-}
-
-#########################################################
-
-#### Get the actual observed number of triplet motifs
-
-
-#########################################################
-
-fix_edge_attribute_direction <- function (interaction_type_abbrev) {
-	
-	if ( is.na( interaction_type_abbrev ) ) {
-		return (NA)
-	} 	
-	
-	if (interaction_type_abbrev== "tu" ) {
-		return ('td')
-	} else if ( interaction_type_abbrev== "ku") {
-		return ('kd')
-	} else if ( interaction_type_abbrev== "td") {
-		return ('tu')
-	} else if ( interaction_type_abbrev== "kd") {
-		return ('ku')
-	} else if ( interaction_type_abbrev== "p") {
-		return ('p')
-	} 
-	else {
-		stop ('interaction type not supported')
-	}
-}
-
[…]

### 2017-08-05 Results/Bootstrap_p_values/Analyze_GI_edges/Job_40/count_triplet_motifs_helper.R

@@ -1,1520 +1,0 @@
-### Script: count_triplet_motifs_helper.R
-### Author: Ignatius Pang 
-### Date: 20-5-2016
-### Description: Count the observed number of triplet motifs. Randomize the respective networks and count the number triplet motifs, repeat randomization 1000 times.
-### Obtain the bootstrap p-value. This script contain the helper functions for the main script 'count_triplet_motifs_negative_interactions.R'.
-
-## Project space:
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
-# psql sbi_triplet_motifs 
-
-#########################################################
-## Insert directed network into both directions into the edge list table, so the direction that tables join together won't affect the analyses
-
-## Inputs:
-## input_table - must have 4 columns only, which are: gene_a, gene_b, interaction type, interaction type abbreviation
-## gene_a - column name for input table that cotains gene A of the interaction
-## gene_b - column name for input table that cotains gene B of the interaction
-## interaction_type_forward - information on the type of interaction for A  ---> B 
-## interaction_type_reverse - information on the type of interaction for B <---> A
-## interaction_abbrev_forward - abbereviated information on the type of interaction for A ---> B 
-## interaction_abberv_reverse - abbereviated information on the type of interaction for B ---> A 
-## col_a - column name for gene A in the output table
-## col_b - column name for gene B in the output table
-## col_type - column name for the interaction type in the output table
-## col_abbrev - column name for the interaction type abbreviation in the output table
-
-## Output table:
-## Output table has 4 columns, denoted by col_a, col_b, col_type and col_abbrev mentioned in the inputs description above.
-collate_interactions_from_both_direction <- function (input_table, gene_a, gene_b, 
-													  interaction_type_forward, interaction_type_reverse, 
-													  interaction_abbrev_forward, interaction_abberv_reverse,
-													  col_a, col_b, col_type, col_abbrev) {
-	num_rows <- length(input_table[,1])
-	
-	new_table <- as.data.frame( matrix(ncol=4, nrow=2*num_rows))
-	
[…]

### 2017-08-05 Source/Analyze_GI_edges/collate_results_analyze_gi_edges.R

@@ -9,21 +9,21 @@ library(reshape2)
 ### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
 ### This setting is for the poster presentation.
 
-base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
+## Set the parameters for this project
+options <- commandArgs(trailingOnly = TRUE)
+source( "./Common/parameters_file.R")
 
-source_directory <- paste( base_directory, "Source/", sep="")
-source_directory_common <- paste( source_directory, "Common/",  sep="")
-source_poster_directory <- paste( source_directory, "Poster/", sep="")
-source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
-source( paste(source_directory_common, "concatenate_result_files.R", sep="") )
-source( paste(source_poster_directory, "reshape_triplet_motifs_helper.R", sep="") )
+source_directory <- file.path( base_directory, "Source")
+source_directory_common <- file.path( source_directory, "Common")
+source_poster_directory <- file.path( source_directory, "Poster")
+source( file.path(source_directory_common, "count_triplet_motifs_helper.R") )
+source( file.path(source_directory_common, "concatenate_result_files.R") )
+source( file.path(source_poster_directory, "reshape_triplet_motifs_helper.R") )
 
-results_directory       <- paste( base_directory, "Results/Bootstrap_p_values/Analyze_GI_edges/", sep="")
-final_results_directory <- paste ( results_directory, "Final_Results/", sep="")
+results_directory       <- file.path( base_directory, "Results/Bootstrap_p_values/Analyze_GI_edges")
+final_results_directory <- file.path ( results_directory, "Final_Results")
 
-	if (! file.exists(final_results_directory)){
-		dir.create(final_results_directory)
-	}
+create_directory_if_not_exists(final_results_directory)
 
 ################################################################################################################################################
 ### Helper functions 
@@ -60,7 +60,7 @@ false_positive_rates 			     <- 0.02  # If the observed data is less than two pe
 number_to_use_for_bonferroni_adjustment <- 36
 
 ### Observed
-count_triplet_motifs_observed 		<- read.table ( paste( results_directory, observed_file_pattern, sep=""), 
+count_triplet_motifs_observed 		<- read.table ( file.path( results_directory, observed_file_pattern), 
 												header=TRUE )
 
 count_triplet_motifs_observed <- fix_table_column_names(count_triplet_motifs_observed) 
[…]

### 2017-08-05 Source/Cell_Cycle/collate_results_cell_cycle.R

@@ -9,20 +9,19 @@ library(reshape2)
 ### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
 ### This setting is for the poster presentation.
 
-base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
+options <- commandArgs(trailingOnly = TRUE)
 
-source_directory <- paste( base_directory, "Source/", sep="")
-source_directory_common <- paste( source_directory, "Common/",  sep="")
-source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
-source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
+source( "./Common/parameters_file.R")
 
-results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Cell_Cycle/", sep="")
-final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+source_directory <- file.path( base_directory, "Source")
+source_directory_common <- file.path( source_directory, "Common",  sep="")
+source( file.path(source_directory_common, "count_triplet_motifs_helper.R") )
+source(  file.path(source_directory_common, "concatenate_result_files.R") )
 
-	if (! file.exists(final_results_directory)){
-		dir.create(final_results_directory)
+results_directory                    <- file.path( base_directory, "Results/Bootstrap_p_values/Cell_Cycle")
+final_results_directory              <- file.path ( results_directory, "Final_Results")
 
-	}
+create_directory_if_not_exists(final_results_directory)
 
 ################################################################################################################################################
 # Counts of Triplet Motifs Costanzo et al. 2010 dataset

### 2017-08-05 Source/Cell_Cycle/count_triplet_motifs_periodic_genes.R

@@ -33,13 +33,14 @@ if ( length(options) != 0
 	source( "./parameters_file.R" )
 
 } else {
-	source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+	source( "./Common/parameters_file.R")
 }
 
 
 ### Local Parameters
 if (is_run_locally) {
-	results_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values_temp/Cell_Cycle/"
+	results_directory <- file.path( results_directory, "Bootstrap_p_values_temp/Cell_Cycle") 
+	create_directory_if_not_exists(results_directory)
 }
 
 # output_observed_triplet_motif_counts <- "results_count_triplet_motifs_costanzo.tab" # "results_count_triplet_motifs_costanzo.tab"

### 2017-08-05 Source/Common/save_R_datasets.R

@@ -9,15 +9,14 @@ library(lazyeval)
 # Description: Transfer data from the SQL database into text file so it can be uploaded into R for data analysis without database connection.
 
 
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/'
 # Rscript --vanilla save_R_datasets.R 
 
 #################################################################################################################
 
-# options <- commandArgs(trailingOnly = TRUE)
 
-data_directory <- "/home/ignatius/PostDoc/2017/Triplet_Motifs_Public/Data/Triplet_Motifs_R_data"
-source_directory <- "/home/ignatius/PostDoc/2017/Triplet_Motifs_Public/Source"
+options <- commandArgs(trailingOnly = TRUE)
+source( "./Common/parameters_file.R")
+
 
 source_directory_common  <- file.path( source_directory, "Common")
 

### 2017-08-05 Source/Negative_GI_Essential/collate_results_neg_gi_essential.R

@@ -9,20 +9,19 @@ library(reshape2)
 ### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
 ### This setting is for the poster presentation.
 
-base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
+options <- commandArgs(trailingOnly = TRUE)
+source( "./Common/parameters_file.R")
 
-source_directory <- paste( base_directory, "Source/", sep="")
-source_directory_common <- paste( source_directory, "Common/",  sep="")
-source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
-source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
 
-results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Negative_GI_Essential/", sep="")
-final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+source_directory <- file.path( base_directory, "Source/")
+source_directory_common <- file.path( source_directory, "Common/")
+source( file.path(source_directory_common, "count_triplet_motifs_helper.R") )
+source(  file.path(source_directory_common, "concatenate_result_files.R") )
 
-	if (! file.exists(final_results_directory)){
-		dir.create(final_results_directory)
+results_directory                    <- file.path( base_directory, "Results/Bootstrap_p_values/Negative_GI_Essential")
+final_results_directory              <- file.path ( results_directory, "Final_Results")
 
-	}
+create_directory_if_not_exists(final_results_directory)
 
 ################################################################################################################################################
 # Counts of Triplet Motifs Costanzo et al. 2010 dataset

### 2017-08-05 Source/Negative_GI_Essential/count_triplet_motifs_negative_gi_essential_genes.R

@@ -25,13 +25,14 @@ if ( length(options) != 0
 	source( "./parameters_file.R" )
 
 } else {
-	source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+	source( "./Common/parameters_file.R")
 }
 
 
 #### Local Parameters
 if (is_run_locally) {
-	results_directory <- paste ( base_directory, "Results/Bootstrap_p_values_temp/Negative_GI_Essential/",  sep="")
+	results_directory <- file.path ( results_directory, "Bootstrap_p_values_temp/Negative_GI_Essential")
+	create_directory_if_not_exists(results_directory)
 }
 
 observed_a_and_b_essential_gene_counts 	<- "observed_a_and_b_essential_gene_counts.tab"
@@ -79,10 +80,10 @@ results_count_c <- transpose_count_triplet_motifs_results(count_essential_genes_
 												"type_bc", "count_c")], 
 												"type_ac", "type_bc", "count_c", "motif_type") 
 
-write.table(results_count_a_and_b , file =  paste( results_directory, observed_a_and_b_essential_gene_counts, sep=""), 
+write.table(results_count_a_and_b , file =  file.path( results_directory, observed_a_and_b_essential_gene_counts), 
 			row.names = FALSE)
 
-write.table(results_count_c , file =  paste( results_directory, observed_c_essential_gene_counts, sep=""), 
+write.table(results_count_c , file =  file.path( results_directory, observed_c_essential_gene_counts), 
 			row.names = FALSE)
 
 
@@ -123,7 +124,7 @@ count_a_and_b_list <-  lapply ( list_of_randomized_triplet_motif_counts, functio
 													  
 randomized_count_a_and_b_table <- concat_motif_counts_list_into_table( count_a_and_b_list) 
 
-write.table ( randomized_count_a_and_b_table, file = paste( results_directory, randomized_count_a_and_b_table_file, sep=""), 
+write.table ( randomized_count_a_and_b_table, file = file.path( results_directory, randomized_count_a_and_b_table_file), 
 			  row.names = FALSE)
 
 			  
@@ -132,7 +133,7 @@ count_c_list <-   lapply ( list_of_randomized_triplet_motif_counts, function(x) 
 													  
 randomized_count_c_table <- concat_motif_counts_list_into_table( count_c_list) 
 			  
-write.table ( randomized_count_c_table, file = paste( results_directory, randomized_count_c_table_file, sep=""), 
[…]

### 2017-08-05 Source/Negative_Genetic_Interactions/count_triplet_motifs_negative_interactions.R

@@ -24,7 +24,7 @@ if ( length(options) != 0
 			source( "./parameters_file.R" )
 
 } else {
-	source( "../Common/parameters_file.R")
+	source( "./Common/parameters_file.R")
 }
 
 ### Local Parameters
@@ -37,7 +37,9 @@ output_full_results_table             <- "full_results_table.tab"
 
 if (is_run_locally) {
 
-	results_directory <- file.path( local_base_directory, "Results/Bootstrap_p_values_temp/Negative_Genetic_Interactions/")
+	results_directory <- file.path( results_directory, "Bootstrap_p_values_temp/Negative_Genetic_Interactions")
+	
+	create_directory_if_not_exists(results_directory)
 }
 
 

### 2017-08-05 Source/Overexpressed_Toxic_Genes/collate_results_overexpression.R

@@ -9,21 +9,18 @@ library(reshape2)
 ### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
 ### This setting is for the poster presentation.
 
-base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
+options <- commandArgs(trailingOnly = TRUE)
+source( "./Common/parameters_file.R")
 
-source_directory <- paste( base_directory, "Source/", sep="")
-source_directory_common <- paste( source_directory, "Common/",  sep="")
-source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
-source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
+source_directory <- file.path( base_directory, "Source")
+source_directory_common <- file.path( source_directory, "Common")
+source( file.path(source_directory_common, "count_triplet_motifs_helper.R") )
+source(  file.path(source_directory_common, "concatenate_result_files.R") )
 
-results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Overexpressed_Toxic_Genes/", sep="")
-final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+results_directory                    <- file.path( results_directory, "Bootstrap_p_values/Overexpressed_Toxic_Genes")
+final_results_directory              <- file.path ( results_directory, "Final_Results")
 
-	if (! file.exists(final_results_directory)){
-		dir.create(final_results_directory)
-
-	}
-
+create_directory_if_not_exists(final_results_directory)
 
 ################################################################################################################################################
 # Counts of Triplet Motifs Costanzo et al. 2010 dataset

### 2017-08-05 Source/Overexpressed_Toxic_Genes/count_triplet_motifs_overexpression.R

@@ -24,13 +24,13 @@ if ( length(options) != 0
 	source( "./parameters_file.R" )
 
 } else {
-	source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+	source( "./Common/parameters_file.R")
 }
 
 ### Local Parameters
 if (is_run_locally) {
 	
-	results_directory <- paste (base_directory,"esults/Bootstrap_p_values_temp/Overexpressed_Toxic_Genes/", sep="")
+	results_directory <- file.path (results_directory,"Bootstrap_p_values_temp/Overexpressed_Toxic_Genes")
 }
 
 
@@ -83,10 +83,10 @@ results_count_c <- transpose_count_triplet_motifs_results(count_overexpressed_to
 																							 "type_bc", "count_c")], 
 																"type_ac", "type_bc", "count_c", "motif_type") 
 
-write.table(results_count_a_and_b , file =  paste( results_directory, observed_a_and_b_overexpressed_toxic_gene_counts, sep=""), 
+write.table(results_count_a_and_b , file =  file.path( results_directory, observed_a_and_b_overexpressed_toxic_gene_counts), 
 			row.names = FALSE)
 
-write.table(results_count_c , file =  paste( results_directory, observed_c_overexpressed_toxic_gene_counts, sep=""), 
+write.table(results_count_c , file =  file.path( results_directory, observed_c_overexpressed_toxic_gene_counts), 
 			row.names = FALSE)
 
 
@@ -129,7 +129,7 @@ count_a_and_b_list <-  lapply ( list_of_randomized_triplet_motif_counts, functio
 													  
 randomized_count_a_and_b_table <- concat_motif_counts_list_into_table( count_a_and_b_list) 
 
-write.table ( randomized_count_a_and_b_table, file = paste( results_directory, randomized_count_a_and_b_table_file, sep=""), 
+write.table ( randomized_count_a_and_b_table, file = file.path( results_directory, randomized_count_a_and_b_table_file), 
 			  row.names = FALSE)
 
 			  
@@ -138,7 +138,7 @@ count_c_list <-   lapply ( list_of_randomized_triplet_motif_counts, function(x) 
 													  
 randomized_count_c_table <- concat_motif_counts_list_into_table( count_c_list) 
 			  
-write.table ( randomized_count_c_table, file = paste( results_directory, randomized_count_c_table_file, sep=""), 
[…]

### 2017-08-05 Source/Paralogs/collate_results_paralogs.R

@@ -9,23 +9,19 @@ library(reshape2)
 ### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
 ### This setting is for the poster presentation.
 
-base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/"
+options <- commandArgs(trailingOnly = TRUE)
+source( "./Common/parameters_file.R")
 
-source_directory <- paste( base_directory, "Source/", sep="")
-source_directory_common <- paste( source_directory, "Common/",  sep="")
-source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
-source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
+source_directory <- file.path( base_directory, "Source")
+source_directory_common <- file.path( source_directory, "Common")
+source( file.path(source_directory_common, "count_triplet_motifs_helper.R") )
+source(  file.path(source_directory_common, "concatenate_result_files.R") )
 
-# results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Paralogs/", sep="")
-results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Paralogs_Not_Randomize_GI/", sep="")
+results_directory                    <- file.path( results_directory, "Bootstrap_p_values/Paralogs_Not_Randomize_GI")
 
-final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+final_results_directory              <- file.path ( results_directory, "Final_Results")
 
-	if (! file.exists(final_results_directory)){
-		dir.create(final_results_directory)
-
-	}
-
+create_directory_if_not_exists(final_results_directory)
 
 ################################################################################################################################################
 # Counts of Triplet Motifs Costanzo et al. 2010 dataset

### 2017-08-05 Source/Paralogs/count_triplet_motifs_paralogs.R

@@ -23,16 +23,17 @@ if ( length(options) != 0  )  {
 		source( "./parameters_file.R" )
 
 	} else {
-		source( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+		source( "./Common/parameters_file.R")
 	}	
 } else {
-	source( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+	source( "./Common/parameters_file.R")
 }	
 
 ### Local Parameters
 if (is_run_locally) {
 
-	results_directory <- paste( base_directory, "Results/Bootstrap_p_values/Paralogs/", sep="")
+	results_directory <- file.path( results_directory, "Bootstrap_p_values/Paralogs")
+	create_directory_if_not_exists(results_directory)
 }
 
 observed_counts_orthomcl_paralogs_file	 <- "observed_counts_orthomcl_paralogs_in_tri_motifs.tab"
@@ -130,34 +131,25 @@ count_motifs_with_orthomcl_paralogs <- count_triplet_motifs_gi_against_edge_list
 count_motifs_with_orthomcl_paralogs <- transpose_count_triplet_motifs_results( count_motifs_with_orthomcl_paralogs, 
 																"type_ac", "type_bc", "count_edge_attribute", "motif_type") 	
 
-write.table( count_motifs_with_orthomcl_paralogs, file = paste( results_directory, observed_counts_orthomcl_paralogs_file, sep=""), 
+write.table( count_motifs_with_orthomcl_paralogs, file = file.path( results_directory, observed_counts_orthomcl_paralogs_file), 
 			 row.names = FALSE)
 
 
 ### Helper function to get statistics for paper.
 ## How many triplet motifs are associated with pairs of genes that are paralogs?
-# list_of_motifs_with_paralogs <- count_triplet_motifs_gi_against_edge_list_helper (triplet_motifs_costanzo, orthomcl_paralogs)
-# 	
+list_of_motifs_with_paralogs <- count_triplet_motifs_gi_against_edge_list_helper (triplet_motifs_costanzo, orthomcl_paralogs)
+list_of_motifs_with_paralogs
+
+
 # How many unique pairs of paralogs are associated with triplet motifs?
-# count_of_motifs_with_paralogs <- list_of_motifs_with_paralogs %>%
-# 								 dplyr::filter(edge_attribute == 1) %>%
-# 								 dplyr::select( one_of( c("oln_id_a", "oln_id_b") ) ) %>% 
[…]

### 2017-08-05 Source/Protein_Complexes/collate_results_protein_complexes.R

@@ -9,21 +9,18 @@ library(reshape2)
 ### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
 ### This setting is for the poster presentation.
 
-base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
+options <- commandArgs(trailingOnly = TRUE)
+source( "./Common/parameters_file.R")
 
-source_directory <- paste( base_directory, "Source/", sep="")
-source_directory_common <- paste( source_directory, "Common/",  sep="")
-source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
-source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
+source_directory <- file.path( base_directory, "Source")
+source_directory_common <- file.path( source_directory, "Common")
+source( file.path(source_directory_common, "count_triplet_motifs_helper.R") )
+source(  file.path(source_directory_common, "concatenate_result_files.R") )
 
-results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Protein_Complexes/", sep="")
-final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
+results_directory                    <- file.path( results_directory, "Bootstrap_p_values/Protein_Complexes")
+final_results_directory              <- file.path ( results_directory, "Final_Results")
 
-	if (! file.exists(final_results_directory)){
-		dir.create(final_results_directory)
-
-	}
-
+create_directory_if_not_exists(final_results_directory)
 
 ################################################################################################################################################
 # Counts of Triplet Motifs Costanzo et al. 2010 dataset

### 2017-08-05 Source/Protein_Complexes/count_triplet_motifs_protein_complexes.R

@@ -22,14 +22,15 @@ if ( length(options) != 0  )  {
 		source( "./parameters_file.R" )
 
 	} else {
-		source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+		source( "./Common/parameters_file.R")
 	}
 }
 
 ### Local Parameters
 if (is_run_locally) {
 
-	results_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/Protein_Complexes/"
+	results_directory <- file.path ( results_directory, "Bootstrap_p_values_temp/Protein_Complexes") 
+	create_directory_if_not_exists( results_directory)
 }
 
 observed_counts_babu_protein_complex_file        <- "observed_counts_babu_protein_complex_in_tri_motifs.tab"
@@ -62,49 +63,36 @@ my_column_names <- c( "oln_id_a",
 triplet_motifs_costanzo <- form_triplet_motifs(filtered_costanzo_stringent, interactions_combined, interactions_combined,
 											   my_join_ac, my_join_bc, my_selected_columns, my_column_names)
 
-
-##################################################################################################################################################
-#### Analysis on Babu membrane protein complexes dataset	
-# babu_motif_and_protein_complexes <- count_triplet_motifs_in_protein_complexes ( triplet_motifs_costanzo, babu_protein_complexes) 
-	
-
-# babu_protein_complex_count <- transpose_count_triplet_motifs_results(babu_motif_and_protein_complexes, 
-																# "type_ac", "type_bc", "total_count", "motif_type") 	
-
-# write.table(babu_protein_complex_count , file =  paste( results_directory, observed_counts_babu_protein_complex_file, sep=""), 
-			# row.names = FALSE)
-
-
 ##################################################################################################################################################
 ### Helper analysis to get statistics for use in paper 
-# benschop_motif_and_protein_complexes_temp <- count_triplet_motifs_in_protein_complexes_helper ( triplet_motifs_costanzo, benschop_protein_complexes)
-# 
-# benschop_motif_and_protein_complexes_temp <- as.data.frame( benschop_motif_and_protein_complexes_temp)
-# 
[…]

### 2017-08-05 Source/Random_Edges/collate_random_edges_results.R

@@ -3,13 +3,21 @@ library(dplyr)
 library(ggplot2)
 library(lazyeval)
 
-source('/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Random_Edges/collate_random_edges_results_helper.R')
-source('/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Poster/reshape_triplet_motifs_helper.R')
+
+options <- commandArgs(trailingOnly = TRUE)
+source( "./Common/parameters_file.R")
+
+
+source( file.path ( source_directory, 'Random_Edges/collate_random_edges_results_helper.R')) 
+source( file.path( source_directory, 'Figures/reshape_triplet_motifs_helper.R') )
 
 ### Directories
-results_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/Random_Edges/"
+results_directory <- file.path ( results_directory, "Bootstrap_p_values/Random_Edges" ) 
+final_results_directory <- file.path ( results_directory, "Final_Results")
 
-final_results_directory <- paste ( results_directory, "Final_Results/", sep="")
+create_directory_if_not_exists(results_directory)
+create_directory_if_not_exists(final_results_directory)
+
 
 ### Size of resulting plot 
 graphic_width  <- 10 
@@ -84,7 +92,7 @@ randomization_collated_counts <- rbind( before_randomization_collated_counts, af
 
 randomization_collated_counts[, 'motif_type'] <- convert_triplet_motifs_name_to_paper_style( randomization_collated_counts[, 'motif_type'])
 
-write.table ( randomization_collated_counts, file=paste ( final_results_directory, "randomization_collated_counts.txt", sep=""))
+write.table ( randomization_collated_counts, file=file.path ( final_results_directory, "randomization_collated_counts.txt"))
 
 
 #####################################################################################################################################
@@ -97,7 +105,7 @@ stat_test_result_random_edges <- random_edges_statstical_testing(randomization_c
 
 stat_test_result_random_edges[, 'motif_type'] <- convert_triplet_motifs_name_to_paper_style( stat_test_result_random_edges[, 'motif_type'])
 
-write.table ( stat_test_result_random_edges, file=paste ( final_results_directory, "stat_test_result_random_edges.txt", sep=""))
+write.table ( stat_test_result_random_edges, file=file.path ( final_results_directory, "stat_test_result_random_edges.txt"))
 
[…]

### 2017-08-05 Source/Random_Edges/count_triplet_motifs_random_edges.R

@@ -15,7 +15,6 @@ sessionInfo()
 # Source location
 
 # psql sbi_triplet_motifs
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
 # Rscript --vanilla count_triplet_motifs_random_edges.R local 0.5 1 1 1  
 
 #########################################################
@@ -28,22 +27,24 @@ if ( length(options) != 0  )  {
 		source( "./parameters_file.R" )
 	} else {
 		print ('Load parameter file locally.')
-		source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+		source( "./Common/parameters_file.R")
 	}
 	
 } else {
 	print ('Load parameter file locally.')
-	source( "/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Common/parameters_file.R")
+	source( "./Common/parameters_file.R")
 }
 
 source_directory_random_edges <- "./"
 
 if (is_run_locally) {
-	results_directory <- paste( base_directory, "Results/Bootstrap_p_values/Random_Edges/", sep="")
-	source_directory_random_edges <- paste( source_directory, "Random_Edges/", sep="")
+	results_directory <- file.path( results_directory, "Bootstrap_p_values_temp/Random_Edges")
+	source_directory_random_edges <- file.path( source_directory, "Random_Edges")
+	
+	create_directory_if_not_exists(results_directory)
 }
 
-source( paste (source_directory_random_edges, "random_edges_helper.R", sep="" ))
+source( file.path (source_directory_random_edges, "random_edges_helper.R" ))
 
 ### Local Parameters
 
@@ -245,14 +246,14 @@ if ( 'before_randomization' %in% names(list_of_randomized_triplet_motif_counts[[
 	
 	before_randomization_table <- concat_motif_counts_list_into_table( before_randomization_list)
 	
-	write.table ( before_randomization_table, file = paste( results_directory, before_randomization_counts_file, sep=""),
+	write.table ( before_randomization_table, file = file.path( results_directory, before_randomization_counts_file),
 				  row.names = FALSE)
 
 	after_randomization_list <-  lapply ( list_of_randomized_triplet_motif_counts, function(x) {return( x$after_randomization )} )
 	
 	after_randomization_table <- concat_motif_counts_list_into_table( after_randomization_list)
 	
-	write.table ( after_randomization_table, file = paste( results_directory, after_randomization_counts_file, sep=""),
[…]

### 2017-08-05 Source/Random_Edges/run_triplet_motifs_random_edges.sh

@@ -1,68 +1,0 @@
-#!/bin/bash
-
-#PBS -N TriMoRandEdge
-#PBS -l nodes=1:ppn=16
-#PBS -l vmem=16gb
-#PBS -l walltime=12:00:00
-#PBS -j oe
-#PBS -M i.pang@unsw.edu.au
-#PBS -m ae
-#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/epilogue_random_edges.sh
-
-# Command for running array jobs 
-#PBS -t 0-10
-
-### To check he status of array jobs, this is the command:
-# qstat  -t -n1 -u z3371724
-
-module load openmpi/1.8.3
-module load R/3.2.2
-
-DATE=$(date +"%Y%m%d")
-
-### Create relevant directories
-
-if [ ! -d $PBS_O_WORKDIR/../Results/Random_Edges ]; then
-  mkdir $PBS_O_WORKDIR/../Results/Random_Edges
-fi
-
-if [ ! -d $PBS_O_WORKDIR/../Log/Random_Edges ]; then
-  mkdir $PBS_O_WORKDIR/../Log/Random_Edges
-fi
-
-if [ ! -d $PBS_O_WORKDIR/Random_Edges ]; then
-  mkdir $PBS_O_WORKDIR/Random_Edges
-fi
-
-if [ ! -d $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID} ]; then
-  mkdir $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
-fi
-
-PARAMS=( 0.2 0.3 0.4 0.5 0.6 0.7 0.8 0.9 1.1 1.2 1.3 )
-
-network_size_proportion=${PARAMS[${PBS_ARRAYID}]}
-
-cd $PBS_O_WORKDIR/JDD
-
-rsync -a ${PBS_O_WORKDIR}/count_triplet_motifs_helper.R 	  $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
-rsync -a ${PBS_O_WORKDIR}/random_edges_helper.R 			  $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
-rsync -a ${PBS_O_WORKDIR}/count_triplet_motifs_random_edges.R $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
[…]

### 2017-08-05 Source/Random_Edges/run_triplet_motifs_random_edges_on_clive.sh

@@ -1,71 +1,0 @@
-#!/bin/bash
-
-#PBS -N TriMoRandEdge
-#PBS -l nodes=1:ppn=24
-#PBS -l vmem=100gb
-#PBS -l walltime=12:00:00
-#PBS -j oe
-#PBS -M i.pang@unsw.edu.au
-#PBS -m ae
-#PBS -l epilogue=/share/bioinfo/igy/Triplet_Motifs/Source/epilogue_random_edges.sh
-
-# Command for running array jobs 
-#PBS -t 0-10
-
-### To check he status of array jobs, this is the command:
-# qstat  -t -n1 -u z3371724
-
-#### To delete the array jobs
-# qdel -t 4-10 1182[]
-
-module load openmpi/1.10.3
-module load R/3.3.1-bioconductor-3.3
-
-DATE=$(date +"%Y%m%d")
-
-### Create relevant directories
-
-if [ ! -d $PBS_O_WORKDIR/../Results/Random_Edges ]; then
-  mkdir $PBS_O_WORKDIR/../Results/Random_Edges
-fi
-
-if [ ! -d $PBS_O_WORKDIR/../Log/Random_Edges ]; then
-  mkdir $PBS_O_WORKDIR/../Log/Random_Edges
-fi
-
-if [ ! -d $PBS_O_WORKDIR/Random_Edges ]; then
-  mkdir $PBS_O_WORKDIR/Random_Edges
-fi
-
-if [ ! -d $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID} ]; then
-  mkdir $PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
-fi
-
-PARAMS=( 0.2 0.3 0.4 0.5 0.6 0.7 0.8 0.9 1.1 1.2 1.3 )
-
-network_size_proportion=${PARAMS[${PBS_ARRAYID}]}
-
-cd $PBS_O_WORKDIR/JDD
-
-rsync -a ${PBS_O_WORKDIR}/count_triplet_motifs_helper.R 	$PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
-rsync -a ${PBS_O_WORKDIR}/random_edges_helper.R 		$PBS_O_WORKDIR/Random_Edges/Job_${PBS_ARRAYID}
[…]

### 2017-08-05 Source/Random_Edges/test_random_edges.R

@@ -1,245 +1,0 @@
-
-### Script: test_random_edges.R
-### Author: Ignatius Pang 
-### Date: 20-5-2016
-### Description: Test random additions or deletion of edges 
-
-library(igraph)
-library(dplyr)
-library(lazyeval)
-library(parallel)
-
-sessionInfo()
-
-#########################################################
-# Source location
-
-# psql sbi_triplet_motifs
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
-# 
-
-#########################################################
-### Parameters 
-options <- commandArgs(trailingOnly = TRUE)
-
-is_rm244 <- TRUE
-
-if ( length(options) != 0 
-     & options[1] == 'katana') {
-  is_rm244 <- FALSE
-}
-
-print (is_rm244)
-
-random_number_seed <- 1985
-number_of_cores_to_use <- 16
-number_of_randomized_trials <- 2000
-num_iteration_rewire_network <- NULL # Number of times each network is rewired before counting the triplet motifs
-
-data_directory <- "./"
-source_directory <- "./"
-results_directory <- "./"
-source_directory_random_edges <- "./"
-
-before_transpose_triplet_motif_counts <- "results_count_triplet_motifs_before_transpose_costanzo.tab"
-output_observed_triplet_motif_counts <- "results_count_triplet_motifs_costanzo.tab" # "results_count_triplet_motifs_costanzo.tab"
-randomized_results_table_file <- "randomized_results_table.tab"
-output_enrichment_p_value <- "enrichment_p_value_fixed.tab"
-output_depletion_p_value <- "depletion_p_value_fixed.tab"
-output_full_results_table <- "full_results_table.tab"
-
-if (is_rm244) {
-  random_number_seed <- 1985
-  number_of_cores_to_use <- 4
-  number_of_randomized_trials <- 4
-  num_iteration_rewire_network <- 0 # Number of times each network is rewired before counting the triplet motifs
-  
-  #base_directory <- "C:/Users/home/Desktop/Triplet_Motifs/"
-   base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
-  
-  data_directory <- paste( base_directory, "Data/Triplet_Motifs_R_data/", sep="")
-  source_directory <- paste( base_directory, "Source/", sep="")
[…]

### 2017-09-17 Source/Figures/paper_figures.Rmd
Sync development code with public release repository

---
title: "paper_figures.Rmd"
author: "Ignatius Pang"
date: "31 August 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("..")) 
```

## Description 
Create the figures for the manuscript. Does not include the network diagrams, these are in a separate script.

## Import library
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape2)
library(svglite)
```

## Global parameters

```{r}

# figure_file_suffix <- ".tiff"
# figure_file_suffix <- ".svg"
figure_file_suffix <- ".pdf"
options <- commandArgs(trailingOnly = TRUE)

source( file.path( local_base_directory, "./Common/parameters_file.R") ) 
source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))
source( file.path ( local_base_directory, './Figures/paper_figures_helper.R') )

computational_results_directory <- file.path ( local_base_directory, "Results/Bootstrap_p_values") 
figures_results_directory       <- file.path ( local_base_directory, "Results/Figures/Graphs" )

plot_background_colour <- "white"   # "#7E4E99" # 
axis_text_colour <- "black"  # "#FFC000" #

### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
### This setting is for the poster presentation.
graphic_width <- 5
graphic_height <- 3

# False positive rate for filtering triplet motifs with low counts
false_positive_rates <- 0.02

# List of 15 types of triplet motifs
all_15_types_of_triplet_motifs <- c("pp" 
									,"tutu"
									,"pku"
									,"kuku"
									,"ptd"
									,"kdku"
									,"ptu"
									,"tdtd"
									,"pkd"
									,"tdtu"
									,"kdkd"
									,"tuku"
									,"tdku"
									,"tdkd"
									,"tukd")

# Parameter for Figure 5.
max_num_overlapping_triplets_to_show <- 35

```

## Figure 1a. 
Please refer to the script 'print_triplet_network.R'. This requires Cytoscape to be opened. 
The figure was manually selected from this network. Please note it takes a long computational time to draw this in Cytoscape.

## Figure 1b.
Please refer to the script 'print_triplet_network.R'. This requires Cytoscape to be opened. 
Please note it takes a long computational time to draw this in Cytoscape.

## Figure 1c.
Please refer to the script 'print_triplet_network.R'. This requires Cytoscape to be opened. 
After the network was draw, the Spatial Analysis of Functional Enrichment (SAFE) tool was used to draw this figure.

Anastasia Baryshnikova (2016) Systematic Functional Annotation and Visualization of Biological Networks. 
Cell Systems , Volume 2 , Issue 6 , 412 - 421.

The Gene Ontology Annotation file used is in the following file path: 'Results/SAFE/go_bp_140819.txt'.

## Find over-represented motifs 
Sort triplet motifs by count and get those that are significantly over-represented. 
```{r}
### Motifs that are significant. Sorted in decending order of the number of observed motifs.

negative_interactions_full <- read.table ( file= file.path( computational_results_directory, 
										   "Negative_Genetic_Interactions/Final_Results/full_results_triplet_motifs_costanzo_2016_collated.tab") )

rows_to_include  <-  (negative_interactions_full[, "observed_counts"] > sum ( negative_interactions_full[, "observed_counts"] ) * false_positive_rates)  &
					 (negative_interactions_full[, "enrichment_adj_p_values"]  < 0.05)

rows_to_include <- ifelse ( is.na(rows_to_include), FALSE, rows_to_include)

significant_types_of_motifs <- dplyr::arrange ( negative_interactions_full[rows_to_include, ], desc( observed_counts ) ) %>%
							   dplyr::select ( one_of ( c( "motif_type"))) %>% 
							   as.data.frame() %>%  
							   t() %>% 
							   as.vector()

## Convert motif names to paper format
significant_types_of_motifs <- convert_triplet_motifs_name_to_paper_style( significant_types_of_motifs )

significant_types_of_motifs <- significant_types_of_motifs[ c("pp", "tutu",  "tdp", "pku", "kuku", "pkd" )]

```

## Figure 2a.
This figure was hand drawn.

## Figure 2b. Six over-represented triplet motifs
```{r}

### Print the analysis of negative genetic interactions 
negative_interactions_full     <- read.table ( file= file.path( computational_results_directory, 
											   "Negative_Genetic_Interactions/Final_Results/full_results_triplet_motifs_costanzo_2016_collated.tab") )

negative_interactions_full     <- dplyr::arrange ( negative_interactions_full, desc( observed_counts ) )

negative_interactions_random   <- read.table ( file=  file.path( computational_results_directory, 
																 "Negative_Genetic_Interactions/Final_Results/randomized_counts_triplet_motifs.tab"  ))

negative_interactions_observed <- read.table ( file= file.path( computational_results_directory, 
																"Negative_Genetic_Interactions/Job_21/results_count_triplet_motifs_costanzo.tab"), 
								               header=TRUE )

print_box_plot_observed_vs_random(negative_interactions_observed, negative_interactions_random, negative_interactions_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

ggsave(file.path(figures_results_directory, paste( "significant_triplet_motifs_negative_gi", figure_file_suffix, sep="") ), 
	   plot=last_plot(), width=graphic_width, 
	   height=graphic_height )

```

## Figure 2c. Paralogs are enriched among the negative genetic interactions of triplet motifs.
```{r}
orthomcl_paralogs_full   <- read.table ( file.path( computational_results_directory,
													  "Paralogs/Final_Results/full_results_table_orthomcl_paralogs_in_tri_motifs.tab"), header =TRUE)

orthomcl_paralogs_random   <- read.table ( file.path( computational_results_directory,
												   "Paralogs/Final_Results/randomized_counts_orthomcl_paralogs_in_tri_motifs.tab"), header =TRUE)
orthomcl_paralogs_observed <- read.table ( file.path( computational_results_directory,
												   "Paralogs/Job_1/observed_counts_orthomcl_paralogs_in_tri_motifs.tab"), header =TRUE)

print_box_plot_observed_vs_random(orthomcl_paralogs_observed, orthomcl_paralogs_random, orthomcl_paralogs_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

ggsave(file.path(figures_results_directory, paste("orthomcl_paralogs", figure_file_suffix, sep="")), plot=last_plot(), width=graphic_width, height=graphic_height )

```

## Figure 3. Random removal or addition of negative genetic interactions highlights the robust over-representation of the six triplet motifs.  
```{r}

## Randomly add or remove edges

# Need to run collate_random_edges_results.R first

### Directories
final_results_directory <- file.path( computational_results_directory, "Random_Edges/Final_Results")

stat_test_result_random_edges <- read.table ( file=file.path( final_results_directory, "stat_test_result_random_edges.txt" ))

randomization_collated_counts <- read.table (  file=file.path ( final_results_directory, "randomization_collated_counts.txt"))

# The motif types sorted by largest to lowest count
# motif_types_sorted_by_counts_desc <- dplyr::filter ( randomization_collated_counts, parameter==1 & experiment=='Before' & motif_type != 'total' ) %>%
# 	dplyr::select( one_of(c('experiment', 'motif_type', 'counts'))) %>%
# 	dplyr::arrange(desc(counts)) %>%
# 	dplyr::distinct() %>%
# 	dplyr::select (one_of(c('motif_type'))) %>%
# 	as.data.frame() %>%
# 	t() %>%
# 	as.vector()

# The motif types are set according to this list 
motif_types_sorted_by_counts_desc <- c( "PP", "TUTU", "TDP", "PKU",  "KUKU",  "PKD",  
										"PTU", "KDKU", "TDTD", "KDKD", "TDTU", "TUKD", "TDKD", "TDKU", "TUKU" )

### Get statistical significance of results
background_shading_table <- dplyr::select(stat_test_result_random_edges, one_of(c('parameter', 'motif_type', 'is_significant')))
background_shading_table$experiment <-1
background_shading_table$counts <-1
background_shading_table[, 'is_significant'] <- as.factor(background_shading_table[, 'is_significant'] )

## Change the order in which the motif types are ordered when they appear as rows in the facet grid
background_shading_table[, 'motif_type'] <- factor (  background_shading_table[, 'motif_type'], levels = motif_types_sorted_by_counts_desc ) 
randomization_collated_counts[, 'motif_type'] <- factor ( randomization_collated_counts[,'motif_type'], levels = motif_types_sorted_by_counts_desc ) 
randomization_collated_counts[, 'experiment'] <- factor ( randomization_collated_counts[,'experiment'], levels = c( 'Before', 'After') )

# removal or addition of nodes to network
randomization_collated_counts %>%
	dplyr::filter (  motif_type != 'total' ) %>%
	ggplot (  aes( experiment, counts) ) +
	geom_boxplot()  +
	geom_rect(data = background_shading_table ,aes(  fill=is_significant ),
			  xmin = -Inf,xmax = Inf,
			  ymin = -Inf,ymax = Inf,alpha = 0.3) +
	scale_fill_manual( values=c('blue', 'red')) +
	facet_grid(   motif_type ~ parameter , scales="free") + 
	labs( title = "Removal or Addition of Edges to Network") +
	xlab( "Before or After Network Randomization") +
	ylab ('Counts') +
	theme( plot.background = element_rect(fill = "white", color="white"), 
		   axis.text = element_text(colour = "black"),
		   axis.title = element_text(colour = "black"),
		   strip.text.y = element_text(face = "italic"),
		   plot.title = element_text(hjust = 0.5, size = rel(1), colour = "black"),
		   legend.position="none")

ggsave(file.path(figures_results_directory, paste("randomization_collated_results", figure_file_suffix, sep="")), 
	   plot=last_plot(), width=10, height=10 )

ggsave(file.path(figures_results_directory, paste("randomization_collated_results_15x15", figure_file_suffix, sep="")), plot=last_plot(), width=15, height=15 )

```

## Figure 4a.
This figure was hand drawn.

## Figure 4b. Overlap of negative genetic interactions in triplet motifs with other types of interactions. 
```{r}

final_results_directory <- file.path( computational_results_directory, "Analyze_GI_edges/Final_Results")

triplet_motifs_full_results_file     <- "full_results_table_analyze_gi_edge_in_tri_motifs.tab"
count_triplet_motifs_randomized_file <- "randomized_results_table.tab"

joined_table_summarized_filtered <- read.table (  file=file.path( final_results_directory, triplet_motifs_full_results_file), header = TRUE  )

analyze_gi_edges_counts_gathered <- read.table ( file=file.path( final_results_directory, count_triplet_motifs_randomized_file), header = TRUE )

motif_type_levels_order <- c( 'PP', 'TUTU', 'TDP', 'PKU', 'KUKU', 'PKD')

edge_type_levels_order  <- c( 'None', 'P', 'K1', 'K2', 'T1', 'T2')

joined_table_summarized_filtered[, "motif_type"] <- factor ( joined_table_summarized_filtered[,"motif_type"], levels=motif_type_levels_order)
analyze_gi_edges_counts_gathered[, "motif_type"] <- factor ( analyze_gi_edges_counts_gathered[,"motif_type"], levels=motif_type_levels_order)

joined_table_summarized_filtered[, "edge_type"] <- factor ( joined_table_summarized_filtered[,"edge_type"], levels=edge_type_levels_order)
analyze_gi_edges_counts_gathered[, "edge_type"] <- factor ( analyze_gi_edges_counts_gathered[,"edge_type"], levels=edge_type_levels_order)

ggplot_analyze_gi_edges <- ggplot(analyze_gi_edges_counts_gathered, aes(edge_type, counts)) +
	geom_boxplot() +
	## Add the observed values as additional points
	geom_point( data=joined_table_summarized_filtered, aes(x=edge_type, y=observed_counts, color=color ),
				 size=4 , alpha=0.5) 	+
	scale_color_identity()

### With wrapping
ggplot_analyze_gi_edges + 
	## Add faceting
	facet_wrap ( ~ motif_type , scales="free") +
	xlab( "Types of Motifs") 	+ 
	ylab( "Counts") + 
	theme( axis.text.x=element_text(face="italic") ,  strip.text.x=element_text(face="italic"), 
		   text = element_text(size=20)
		   )

ggsave(file.path(figures_results_directory, paste( "analyze_gi_edges_wrap", figure_file_suffix, sep="")), 
	   plot=last_plot(), width=10.3, height=7.5 ) # , width=10, height=7
```

## Figure 5a. Genetic interactions shared by two or more overlapping triplets highlight functional interaction modules .  
```{r}

randomized_table <- read.table(  file.path( computational_results_directory, "Repeated_GI_in_Motifs_Freq_Dist/Final_Results/overlapping_triplets_randomized_frequency_distribution.txt"), 
								 header=TRUE)

statistical_analysis <- read.table(  file.path( computational_results_directory, "Repeated_GI_in_Motifs_Freq_Dist/Final_Results/overlapping_triplets_frequency_distribution.txt"),
									 header = TRUE)

## Draw counts distribution table 
randomized_table %>%
	dplyr::filter( counts <= max_num_overlapping_triplets_to_show ) %>%
	dplyr::mutate( total_count = total_count + 1) %>%
	dplyr::filter( motif_type != 'Others') %>%
	ggplot( aes( counts, total_count, group=counts ) ) + 
	geom_boxplot(color="grey40") +
	scale_y_log10() + 
	xlab(label="Num. Overlapping Triplets") +
	ylab(label="Num. Genetic Interactions") +
	geom_point( data=statistical_analysis, aes( color=is_significant_color), color=statistical_analysis$is_significant_color, 
				alpha=0.6, size=2) +
	coord_cartesian(xlim=c(0, max_num_overlapping_triplets_to_show)) + 
	guides(color=FALSE) +
	facet_grid ( motif_type ~., scales="free" )

ggsave(file.path(figures_results_directory, paste("repeated_gi_num_motifs_per_gi", figure_file_suffix, sep="") ), 
	   plot=last_plot(), width=5, height=6) # , height=graphic_height

```

## Figure 5c, d, e. 
Please refer to the file 'print_triplet_network_specific_network.Rmd'

## Figure 6. Triplet motifs that have a significant over-representation of:

## Figure 6a. Triplet motifs that have a significant over-representation of a pair of essential proteins involved in negative genetic interactions.
```{r}
essential_ab_full <- read.table ( file.path( computational_results_directory,
											 "Negative_GI_Essential/Final_Results/full_results_table_count_a_and_b.tab"), header =TRUE)

essential_ab_random   <- read.table ( file.path( computational_results_directory,
												 "Negative_GI_Essential/Final_Results/randomized_results_table_count_a_and_b.tab"), header =TRUE)

essential_ab_observed <- read.table ( file.path( computational_results_directory,
												 "Negative_GI_Essential/Job_20/observed_a_and_b_essential_gene_counts.tab"), header =TRUE)

print_box_plot_observed_vs_random(essential_ab_observed, essential_ab_random, essential_ab_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

ggsave(file.path(figures_results_directory, paste("essential_gene_ab", figure_file_suffix, sep="")), plot=last_plot(), width=graphic_width, height=graphic_height )

```

## Figure 6b. Triplet motifs that have a significant over-representation of an essential third protein not part of the negative genetic interaction in the triplet motif.
```{r}

essential_c_full  <- read.table ( file.path( computational_results_directory,
												"Negative_GI_Essential/Final_Results/full_results_table_count_c.tab"), header =TRUE)

essential_c_random   <- read.table ( file.path( computational_results_directory,
											  "Negative_GI_Essential/Final_Results/randomized_results_table_count_c.tab"), header =TRUE)

essential_c_observed <- read.table ( file.path( computational_results_directory,
											  "Negative_GI_Essential/Job_20/observed_c_essential_gene_counts.tab"), header =TRUE)

print_box_plot_observed_vs_random(essential_c_observed, essential_c_random, essential_c_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

ggsave(file.path(figures_results_directory, paste("essential_gene_c", figure_file_suffix, sep="")), plot=last_plot(), width=graphic_width, height=graphic_height )

```

## Figure 6c. Triplet motifs that have a significant over-representation of a pair of cell cycle-regulated genes involve in negative genetic interactions
```{r}

periodic_ab_full <- read.table ( file.path( computational_results_directory,
											"Cell_Cycle/Final_Results/full_results_periodic_gene_counts_a_and_b.tab"), header =TRUE)

periodic_ab_random   <- read.table ( file.path( computational_results_directory,
												"Cell_Cycle/Final_Results/randomized_results_periodic_gene_counts_a_and_b.tab"), header =TRUE)
periodic_ab_observed <- read.table ( file.path( computational_results_directory,
												"Cell_Cycle/Job_1/observed_a_and_b_periodic_gene_counts.tab"), header =TRUE)

print_box_plot_observed_vs_random(periodic_ab_observed, periodic_ab_random, periodic_ab_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

ggsave(file.path(figures_results_directory, paste("periodic_ab", figure_file_suffix, sep="")), plot=last_plot(), width=graphic_width, height=graphic_height )

```

## Figure 6d. Triplet motifs that have a significant over-representation of a cell cycle-regulated protein not part of the negative genetic interaction in the triplet motif
```{r}

periodic_c_full <- read.table ( file.path( computational_results_directory,
											"Cell_Cycle/Final_Results/full_results_periodic_gene_counts_c.tab"), header =TRUE)

periodic_c_random   <- read.table ( file.path( computational_results_directory,
												"Cell_Cycle/Final_Results/randomized_results_periodic_gene_counts_c.tab"), header =TRUE)
periodic_c_observed <- read.table ( file.path( computational_results_directory,
												"Cell_Cycle/Job_1/observed_c_periodic_gene_counts.tab"), header =TRUE)

print_box_plot_observed_vs_random(periodic_c_observed, periodic_c_random, periodic_c_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

ggsave(file.path(figures_results_directory, paste("periodic_c", figure_file_suffix, sep="")), plot=last_plot(), width=graphic_width, height=graphic_height )

```

## Figure 6e. Triplet motifs that have a significant over-representation of a pair of proteins that are toxic upon overexpression and involved in negative genetic interaction.
```{r}

overexpression_ab_full <- read.table ( file.path( computational_results_directory,
									  "Overexpressed_Toxic_Genes/Final_Results/full_results_table_overexpressed_toxic_gene_counts_a_and_b.tab"), header =TRUE)

overexpression_ab_random   <- read.table ( file.path( computational_results_directory,
										  "Overexpressed_Toxic_Genes/Final_Results/randomized_results_table_overexpressed_toxic_gene_counts_a_and_b.tab"), header =TRUE)

overexpression_ab_observed <- read.table ( file.path( computational_results_directory,
												"Overexpressed_Toxic_Genes/Job_1/observed_a_and_b_overexpressed_toxic_gene_counts.tab"), header =TRUE)

print_box_plot_observed_vs_random(overexpression_ab_observed, overexpression_ab_random, overexpression_ab_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
								  axis_text_colour=axis_text_colour)

ggsave(file.path(figures_results_directory, paste("overexpression_ab", figure_file_suffix, sep="")), plot=last_plot(), width=graphic_width, height=graphic_height )

```

## Figure 6f. Triplet motifs that have a significant over-representation of a protein that is toxic upon overexpression and not part of the negative genetic interaction in the triplet motif. 
```{r}

overexpression_c_full <- read.table ( file.path( computational_results_directory,
										   "Overexpressed_Toxic_Genes/Final_Results/full_results_table_overexpressed_toxic_gene_counts_c.tab"), 
									       header =TRUE)

overexpression_c_random   <- read.table ( file.path( computational_results_directory,
										  "Overexpressed_Toxic_Genes/Final_Results/randomized_results_table_overexpressed_toxic_gene_counts_c.tab"),
										  header =TRUE)

overexpression_c_observed <- read.table ( file.path( computational_results_directory,
											   "Overexpressed_Toxic_Genes/Job_1/observed_c_overexpressed_toxic_gene_counts.tab"), header =TRUE)

print_box_plot_observed_vs_random(overexpression_c_observed, overexpression_c_random, overexpression_c_full, significant_types_of_motifs,
								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour )

ggsave(file.path(figures_results_directory, paste("overexpression_c", figure_file_suffix, sep="")), plot=last_plot(), width=graphic_width, height=graphic_height )

```

## Figure 7.
Please refer to the file 'print_triplet_network_specific_network.Rmd'

### 2017-09-17 Source/Figures/print_triplet_network_specific_network.Rmd
Sync development code with public release repository

@@
 
-Description: I want to visualize the network, which consists of all the triplet motifs. Only edges in triplet motifs are shown.
+## Description
+I want to visualize the network and draw network figures for the manuscript.
 
+```{r setup, include=FALSE}
+knitr::opts_knit$set(root.dir = normalizePath("..")) 
+```
+
+## Load libraires
 ```{r}
 library(RCy3)
+library(plyr)
 library(dplyr)
-library(RODBC)
 library(sqldf)
+
+sessionInfo()
 ```
 
-Read helper functions 
+## Read helper functions 
 ```{r}
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Poster/'
+# cd '/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Poster/'
 
@@
 options <- commandArgs(trailingOnly = TRUE)
-source( "./Common/parameters_file.R")
+# setwd( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source")
 
-setwd ( file.path( base_directory, 'Source/Figures') )
+source( file.path( getwd(), "Common/parameters_file.R") )
 
 source( file.path ( source_directory_common, 'draw_triplet_motif_network_helper.R') ) 
+source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))
 
+supplementary_data_directory <- file.path(results_directory, "Supplementary_Files" ) 
+create_directory_if_not_exists(supplementary_data_directory)
+
+list_of_triplets_directory <- '/home/ignatius/PostDoc/2016/Triplet_Motifs/Data/Triplet_Motifs_R_data'
 ```
 
-Read data tables 
+## Read data tables 
 ```{r}
+results_directory <- file.path(   local_base_directory, "Results" ) 
+networks_directory <- file.path ( results_directory, "Figures/Networks")
+
 triplet_motifs_costanzo_2016 <- read.table ( file.path( list_of_triplets_directory, "triplet_motifs_costanzo_2016.txt"), 
@@
 
+if ( ! ( "oln_id_a" %in% colnames( triplet_motifs_costanzo_2016) ) ) {
 	triplet_motifs_costanzo_2016 <- triplet_motifs_costanzo_2016 %>%
-								dplyr::rename( oln_id_a = node_a, oln_id_b = node_b, oln_id_c = node_c)
+								dplyr::rename(  oln_id_a = node_a , oln_id_b =  node_b ,  oln_id_c = node_c  )
+}
 
@@
 gene_names <- read.table ( file.path(data_directory, "gene_names_table.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
-						    na.strings="", quote="")
+						    na.strings="", quote="\"")
 
@@
 
-enriched_functions <- read.table ( file.path( results_directory, "SAFE/safe_exported_reports_20161123.txt-node_properties_annotation-highest.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
-						    na.strings="", quote="")
+enriched_functions <- read.table ( file= file.path( results_directory, "SAFE/20161123/Triplet_Motifs/safe_exported_reports_20161123.txt-node_properties_annotation-highest.txt"), 
+								   header=TRUE, stringsAsFactors = TRUE, 
+						    na.strings="", quote="", sep="\t")
 
@@
 
-Build phenotype master table 
+## Build phenotype master table 
 ```{r}
@@
 essential_periodic_expression_toxic_overexpression <- essential_periodic_expression_toxic_overexpression %>%
- 														group_by ( oln_id) %>%
- 														summarise( overexpression_toxic = sum( overexpression_toxic), 
+ 														dplyr::group_by ( oln_id) %>%
+ 														dplyr::summarise( overexpression_toxic = sum( overexpression_toxic), 
  																   essential = sum( essential), 
@@
 
+write.table ( essential_periodic_expression_toxic_overexpression, 
+			  file.path(supplementary_data_directory, "essential_periodic_expression_toxic_overexpression.txt"),
+			  sep="\t", 
+			  quote=FALSE,
+			  row.names = FALSE  )
+
 ```
 
-Get densely annotated triplets 
+## Get densely annotated triplets 
 ```{r}
@@
 
+write.table ( densely_annotated_triplet_motif, file.path(supplementary_data_directory, "densely_annotated_triplet_motif.txt"),
+			  sep="\t", 
+			  quote=FALSE,
+			  row.names = FALSE  )
+
 ```
 
-Network of tightly regulated proteins (involved in spindle pole formation)
+## Figure 5c. A genetic interaction overlapping with multiple triplets. Focus on protein complexes. 
+```{r}
+
+list_of_gi <- count_repeated_gi_in_triplet_motifs_look_at_gi( triplet_motifs_costanzo_2016 ) %>%
+			  dplyr::filter( motif_type != "others") %>%
+			  dplyr::filter (motif_type == 'protein_complexes') %>%
+			  dplyr::filter ( counts == '4') %>%
+			  # TIM complex YHR083W, YGR082W	  
+			  dplyr::filter ( (oln_id_a == 'YHR083W' & oln_id_b == 'YGR082W') |
+			  				  (oln_id_a == 'YGR082W' & oln_id_b == 'YHR083W')  )
+
+selected_regulatory_triplets <- triplet_motifs_costanzo_2016 %>%
+	dplyr::right_join ( list_of_gi) %>%
+	dplyr::filter(	type_ac == 'p'  & type_bc == 'p' )  %>%
+	dplyr::select ( one_of( c( "oln_id_a", "oln_id_b", "oln_id_c", "type_ac", "type_bc", "genetic_interaction_score" ))) %>%
+	as.data.frame()
+
+cw <- draw_triplet_motif_network  ( selected_regulatory_triplets, 'Tightly regulated proteins' )
+
+cw <- add_node_attributes(cw, gene_names , "oln_id")
+
+cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")
+
+displayGraph(cw)
+
+triplet_motif_network_display_style(cw)
+
+redraw (cw)
+
+current_example_dir <- file.path( networks_directory, "Repeated_GI_Example")
+
+create_directory_if_not_exists( current_example_dir)
+
+## saveNetwork command currently not working for unknown reasons
+Sys.sleep(5)
+saveImage ( cw, file.name= file.path( current_example_dir, "repeated_gi_example_protein_complexes"), image.type='pdf')
+
+```
+
+## Figure 5d. A genetic interaction overlapping with multiple triplets. Focus on regulatory triplets. 
+```{r}
+
+regulatory_triplets_overlapping_gi  <- function( num_triplets_overlapping) {
+	list_of_gi <- count_repeated_gi_in_triplet_motifs_look_at_gi( triplet_motifs_costanzo_2016 ) %>%
+			  dplyr::filter( motif_type != "others") %>%
+			  dplyr::filter (motif_type == 'regulatory_triplets') %>%
+			  dplyr::filter ( counts == '4') %>%
+			  dplyr::filter ( (oln_id_a == 'YPL018W' & oln_id_b == 'YPL253C') | 
+			  				  (oln_id_a == 'YPL253C' & oln_id_b == 'YPL018W')  	)
+
+selected_regulatory_triplets <- triplet_motifs_costanzo_2016 %>%
+	dplyr::right_join ( list_of_gi) %>%
+	dplyr::filter(	( type_ac == 'tu'  & type_bc == 'tu') |
+				   	( type_ac == 'td' & type_bc == 'p') |
+				   	( type_ac == 'p' & type_bc == 'td') 
+				    )  %>%
+	dplyr::select ( one_of( c( "oln_id_a", "oln_id_b", "oln_id_c", "type_ac", "type_bc", "genetic_interaction_score" ))) %>%
+	as.data.frame()
+
+cw <- draw_triplet_motif_network  ( selected_regulatory_triplets, 'Tightly regulated proteins' )
+
+cw <- add_node_attributes(cw, gene_names , "oln_id")
+
+cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")
+
+displayGraph(cw)
+
+triplet_motif_network_display_style(cw)
+
+redraw (cw)
+
+current_example_dir <- file.path( networks_directory, "Repeated_GI_Example")
+
+create_directory_if_not_exists( current_example_dir)
+
+## saveNetwork command currently not working for unknown reasons
+Sys.sleep(5)
+saveImage ( cw, file.name= file.path( current_example_dir, 
+									  paste("regulatory_", num_triplets_overlapping, "_triplets_overlapping_gi", sep="") ), 
+									  image.type='pdf' )
+
+}
+
+# walk( 2:18, regulatory_triplets_overlapping_gi)
+
+walk( 4, regulatory_triplets_overlapping_gi)
+
+```
+
+## Figure 5e. A genetic interaction overlapping with multiple triplets. Focus on signaling triplets. 
+```{r}
+signaling_triplets_overlapping_gi  <- function( num_triplets_overlapping) {
+
+list_of_gi <- count_repeated_gi_in_triplet_motifs_look_at_gi( triplet_motifs_costanzo_2016 ) %>%
+			  dplyr::filter( motif_type != "others") %>%
+			  dplyr::filter (motif_type == 'signaling_triplets') %>%
+			  dplyr::filter ( counts == '5') %>%
+			  dplyr::filter ( (oln_id_a == 'YGR188C' & oln_id_b == 'YDL028C') | 
+			  				  (oln_id_a == 'YDL028C' & oln_id_b == 'YGR188C')  	)
+
+selected_regulatory_triplets <- triplet_motifs_costanzo_2016 %>%
+	dplyr::right_join ( list_of_gi) %>%
+	dplyr::filter(	( type_ac == 'ku'  & type_bc == 'ku') |
+				   	( type_ac == 'kd' & type_bc == 'p') |
+				   	( type_ac == 'p' & type_bc == 'kd') |
+				   	( type_ac == 'ku' & type_bc == 'p') |
+				   	( type_ac == 'p' & type_bc == 'ku') 
+				    )  %>%
+	dplyr::select ( one_of( c( "oln_id_a", "oln_id_b", "oln_id_c", "type_ac", "type_bc", "genetic_interaction_score" ))) %>%
+	as.data.frame()
+
+cw <- draw_triplet_motif_network  ( selected_regulatory_triplets, 'Tightly regulated proteins' )
+
+cw <- add_node_attributes(cw, gene_names , "oln_id")
+
+cw <- add_node_attributes ( cw, enriched_functions, "Node.label.ORF")
+
+displayGraph(cw)
+
+triplet_motif_network_display_style(cw)
+
+redraw (cw)
+
+current_example_dir <- file.path( networks_directory, "Repeated_GI_Example")
+
+create_directory_if_not_exists( current_example_dir)
+
+## saveNetwork command currently not working for unknown reasons
+Sys.sleep(5)
+saveImage ( cw, file.name= file.path( current_example_dir, 
+									  paste( "signaling_", num_triplets_overlapping, "_triplets_overlapping_gi", sep="") ), 
+			image.type='pdf')
+
+}
+
+#walk( 2:16, signaling_triplets_overlapping_gi)
+
+walk( 5, signaling_triplets_overlapping_gi)
+
+```
+
+## Figure 7. Triplet motifs consisting of proteins that are essential, toxic upon protein overexpression and those periodically expressed in the cell cycle.
+
+## Figure 7a. Venn Diagram
+
+```{r}
+
+results_phenotypic_annotation_enriched_motif <- sqldf( "select distinct oln_id_a, oln_id_b, oln_id_c
+	, case when essential_a = 1 and essential_b = 1 and essential_c = 1 then 1 else 0 end as essential_abc
+	, case when periodically_expressed_a = 1 and periodically_expressed_b = 1 and periodically_expressed_c = 1 then 1 else 0 end as periodically_expressed_abc
+	, case when overexpression_toxic_a = 1 and overexpression_toxic_b = 1 and overexpression_toxic_c = 1 then 1 else 0 end as overexpression_toxic_abc
+from densely_annotated_triplet_motif
+
+where ( ( type_ac = 'p' and type_bc = 'p' )
+	or  ( type_ac = 'tu' and type_bc = 'tu' ) 
+	or  ( type_ac = 'ku' and type_bc = 'ku' ) 
+	or  ( type_ac = 'p'  and type_bc = 'ku' ) 
+	or  ( type_ac = 'p'  and type_bc = 'td' ) 
+	or  ( type_ac = 'p'  and type_bc = 'kd' ) 
+	or  ( type_ac = 'ku' and type_bc = 'p'  ) 
+	or  ( type_ac = 'td' and type_bc = 'p'  ) 
+	or  ( type_ac = 'kd' and type_bc = 'p'  )
+      )  ;" )
+
+counts_for_venn_diagram <- sqldf( "select essential_abc, periodically_expressed_abc, overexpression_toxic_abc, count(*) as counts
+from results_phenotypic_annotation_enriched_motif
+group by essential_abc, periodically_expressed_abc, overexpression_toxic_abc; "  )
+
+print ( counts_for_venn_diagram)
+
+```
+
+## Figure 7b. Network of tightly regulated proteins (involved in spindle pole formation)
 ```{r}
@@
 
-current_example_dir <- file.path( results_directory, "Achilles_heel/Spindle-pole body example")
+current_example_dir <- file.path( networks_directory, "Achilles_heel/Spindle-pole body example")
 
@@
 
-All three proteins in the motif needs to be essential and periodically expressed 
+## Figure 7c. Triplets in which all proteins are essential and their corresponding genes are expressed periodically in the cell cycle. 
 ```{r}
@@
 
-current_example_dir <- file.path( results_directory, "Achilles_heel/Essential and periodically expressed")
+current_example_dir <- file.path( networks_directory, "Achilles_heel/Essential and periodically expressed")
 
@@
 
-Essential and toxic upon overexpression
+## Figure 7d. Triplets where all proteins are essential and toxic upon overexpression. 
 ```{r}
@@
 
-current_example_dir <- file.path( results_directory, "Achilles_heel/Essential and toxic upon overexpression")
+current_example_dir <- file.path( networks_directory, "Achilles_heel/Essential and toxic upon overexpression")
 
@@
 
-Periodically expressed and toxic upon overexpression
+## Figure 7e. All three genes in the triplet motif are cell cycle-regulated and the corresponding protein product is toxic upon overexpression. 
 ```{r}
@@
 
-current_example_dir <- file.path( results_directory, "Achilles_heel/Periodically expressed and toxic upon overexpression")
+current_example_dir <- file.path( networks_directory, "Achilles_heel/Periodically expressed and toxic upon overexpression")
 

### 2017-09-17 Source/Supplementary_Files/supplementary_files.Rmd
Sync development code with public release repository

---
title: "Supplementary Files"
Date: 30-8-2017
output:
  html_document: default
  html_notebook: default
Author: Ignatius Pang
---

## Description

I want to create the supplementary tables for this manuscript.

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("..")) 
```

```{r}
library(RCy3)
library(plyr)
library(dplyr)
library(RODBC)
library(sqldf)
library(knitr) # required for the 'kable' function for printing pretty table in html

sessionInfo()
```

## Read helper functions 
```{r}

source_directory_common <- '/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Common/'
## Load the root base directory for the entire project
options <- commandArgs(trailingOnly = TRUE)
source( file.path( source_directory_common, "parameters_file.R") )

source( file.path ( source_directory_common, 'draw_triplet_motif_network_helper.R') ) 
source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))

supplementary_data_directory <- file.path(results_directory, "Supplementary_Files" ) 
create_directory_if_not_exists(supplementary_data_directory)

```

## Global parameters
```{r}

## All interactions in the kinase substrate network must be greater than this score
sharifpoor_kinase_substrate_network_threshold <- 2.5

## Thresholds for the Costanzo genetic interaction network
## Stringent negative genetic interactions must have score less than this threshold
costanzo_stringent_negative_gi_score_threshold    <- -0.12

## Stringent negative genetic interactions must have p-value less than this threshold
costanzo_stringent_negative_gi_p_value_threshold  <-  0.05

## Stringent negative genetic interactions must have absolute value of stanard deviation (std_dev) less than this threshold
costanzo_stringent_negative_gi_std_dev_threshold <- 0.08
```

## Read data tables 
```{r}
results_directory <- file.path(   local_base_directory, "Results" )

triplet_motifs_costanzo_2016 <- read.table ( file.path( data_directory, "triplet_motifs_costanzo_2016.txt"), 
											 header =TRUE , stringsAsFactors = FALSE)

if ( ! ( "oln_id_a" %in% colnames( triplet_motifs_costanzo_2016) ) ) {
	triplet_motifs_costanzo_2016 <- triplet_motifs_costanzo_2016 %>%
								dplyr::rename(  oln_id_a = node_a , oln_id_b =  node_b ,  oln_id_c = node_c  )
}

toxic_upon_overexpression <- read.table ( file.path( data_directory, "overexpressed_toxic_genes.txt"), header=TRUE , stringsAsFactors = FALSE)

essential_genes <- read.table ( file.path( data_directory, "essential_genes.txt"), header=TRUE, stringsAsFactors = FALSE)

cell_cycle_peak_times_of_orfs <- read.table ( file.path( data_directory, "periodically_expressed_genes.txt"), header=TRUE, stringsAsFactors = FALSE)

gene_names <- read.table ( file.path(data_directory, "gene_names_table.txt"), sep="\t", header=TRUE, stringsAsFactors = FALSE, 
						    na.strings="", quote="\"")

## Results from Spatial Analysis of Functional Enrichment (SAFE tool)

enriched_functions <- read.table ( file= file.path( results_directory, "SAFE/20161123/Triplet_Motifs/safe_exported_reports_20161123.txt-node_properties_annotation-highest.txt"), 
								   header=TRUE, stringsAsFactors = TRUE, 
						    na.strings="", quote="", sep="\t")

```

## Negative Genetic interactions 
```{r}

constanzo_stringet_2016_negative_genetic_interactions <- sqldf( paste(  "select distinct query_oln_id_edited as query_oln_id
														, gene_names_a.gene_name as query_gene_name
														, gene_names_a.description as query_gene_description
														, array_oln_id_edited as array_oln_id
														, gene_names_b.gene_name as array_gene_name
														, gene_names_b.description as array_gene_description
														, genetic_interaction_score
													 from filtered_costanzo_stringent_2016 gi
                                                          left join gene_names as gene_names_a
																on gi.query_oln_id_edited = gene_names_a.oln_id
                                                          left join gene_names as gene_names_b
																on gi.array_oln_id_edited = gene_names_b.oln_id
													 where genetic_interaction_score < ", costanzo_stringent_negative_gi_score_threshold, 
															" and p_value < ", costanzo_stringent_negative_gi_p_value_threshold, 
															" and abs(std_dev) < ", costanzo_stringent_negative_gi_std_dev_threshold , ";" ) )

write.table ( constanzo_stringet_2016_negative_genetic_interactions, 
			  file.path(supplementary_data_directory, "constanzo_stringet_2016_negative_genetic_interactions.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head( constanzo_stringet_2016_negative_genetic_interactions))
dim( constanzo_stringet_2016_negative_genetic_interactions)
```

## Protein interaction networks
```{r}

raw_sbi_interactome_joined <- sqldf(  " select gene_names_a.gene_name as gene_name_a
,oln_id_a
,gene_names_a.description as gene_description_a

,gene_names_b.gene_name as gene_name_b
,oln_id_b
,gene_names_b.description as gene_description_b

,pubmed_id
,expt_system
,source_table
,ppi.description
,author
			from raw_sbi_interactome ppi
					left join gene_names as gene_names_a
																on ppi.oln_id_a = gene_names_a.oln_id
                                                          left join gene_names as gene_names_b
																on ppi.oln_id_b = gene_names_b.oln_id;")

write.table ( raw_sbi_interactome_joined, 
			  file.path(supplementary_data_directory, "protein-protein_interactions.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head(raw_sbi_interactome_joined ))
dim( raw_sbi_interactome_joined)

```

## Kinase-substrate network
```{r}

kinase_network_filtered <- dplyr::filter( kinase_network, score > sharifpoor_kinase_substrate_network_threshold) %>%
							dplyr::select(-interaction_id) %>%
							dplyr::select(one_of ( c("kinase_gene_name", "kinase_oln_id", "target_gene_name", "target_oln_id", "score" )))

kinase_network_filtered <- sqldf( " select gene_names_a.gene_name as kinase_gene_name
									, kinase_oln_id         
									, gene_names_a.description as kinase_gene_description

									, gene_names_b.gene_name as target_gene_name
									, target_oln_id
									, gene_names_b.description as target_gene_description

									, score            
										from kinase_network_filtered kinase_substrate
										left join gene_names as gene_names_a 
														on kinase_substrate.kinase_oln_id = gene_names_a.oln_id
                                        left join gene_names as gene_names_b
														on kinase_substrate.target_oln_id = gene_names_b.oln_id;")

write.table ( kinase_network_filtered, file.path(supplementary_data_directory, "kinase-substrate_interactions.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head(kinase_network_filtered))
dim(kinase_network_filtered)

```

## Transcriptional regulatory network
```{r}

tf_network_filtered <- dplyr::filter( tf_network, gene_expression_evidence + binding_evidence >= 2 | combinatorial_evidence >= 1 )

tf_network_filtered <- sqldf( " select gene_names_a.gene_name as regulator_gene_name
								, regulator_oln_id         
								, gene_names_a.description as regulator_gene_description

								, gene_names_b.gene_name as target_gene_name
								, target_oln_id
								, gene_names_b.description as target_gene_description

								, gene_expression_evidence 
								, binding_evidence         
								, combinatorial_evidence   
								, regulation_direction    
								, pubmed_id              
									from tf_network_filtered tf
									left join gene_names as gene_names_a 
												on tf.regulator_oln_id = gene_names_a.oln_id
                                    left join gene_names as gene_names_b
												on tf.target_oln_id = gene_names_b.oln_id;")

write.table ( tf_network_filtered, file.path(supplementary_data_directory, "transcription_factor-target_gene_interactions.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head( tf_network_filtered))
dim( tf_network_filtered)

```

## Build phenotype master table 
```{r}

toxic_upon_overexpression <- toxic_upon_overexpression %>%
								dplyr::select ( one_of ( c( "oln_id"))) %>%
								dplyr::mutate ( overexpression_toxic = 1)

essential_genes <- essential_genes %>%
						dplyr::mutate ( essential = 1)

cell_cycle_peak_times_of_orfs <- cell_cycle_peak_times_of_orfs %>%
									dplyr::mutate ( periodically_expressed = 1)

essential_periodic_expression_toxic_overexpression <- toxic_upon_overexpression %>%
														full_join ( essential_genes ) %>% 
														full_join (  cell_cycle_peak_times_of_orfs )

essential_periodic_expression_toxic_overexpression [is.na( essential_periodic_expression_toxic_overexpression  ) ] <- 0

essential_periodic_expression_toxic_overexpression <- essential_periodic_expression_toxic_overexpression %>%
 														dplyr::group_by ( oln_id) %>%
 														dplyr::summarise( overexpression_toxic = sum( overexpression_toxic), 
 																   essential = sum( essential), 
 																   periodically_expressed = sum( periodically_expressed))

essential_periodic_expression_toxic_overexpression <- full_join ( essential_periodic_expression_toxic_overexpression, gene_names ) %>%
													  dplyr::mutate ( overexpression_toxic = ifelse(is.na(overexpression_toxic), 0, overexpression_toxic),
													  				  essential = ifelse(is.na(essential), 0, essential),
													  				  periodically_expressed = ifelse(is.na(periodically_expressed), 
													  				  								  0, periodically_expressed)
													  				)

write.table ( essential_periodic_expression_toxic_overexpression, 
			  file.path(supplementary_data_directory, "phenotype_table.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head( essential_periodic_expression_toxic_overexpression))
dim( essential_periodic_expression_toxic_overexpression)

```

## Paralogs and Ohnologs
```{r}

orthomcl_paralogs <- clean_graph_table  (orthomcl_paralogs,  "oln_id_a", "oln_id_b", directed=FALSE ) %>%
					 dplyr::mutate( type="paralog")

sgd_ohnologs 	  <- clean_graph_table  (sgd_paralogs,  "oln_id_a", "oln_id_b", directed=FALSE ) %>% # This table actually contain ohnologs
					 dplyr::mutate( type="ohnolog")

all_paralogs_and_ohnologs <- dplyr::union ( orthomcl_paralogs, sgd_ohnologs) %>%
							 dplyr::arrange( type) %>%
							 dplyr::group_by( oln_id_a, oln_id_b) %>%
							 dplyr::summarise( type=paste( type, collapse=", ")) %>%
							 dplyr::arrange(oln_id_a, oln_id_b)

all_paralogs_and_ohnologs <- sqldf( " select gene_names_a.gene_name as gene_name_a
									, oln_id_a         
									, gene_names_a.description as gene_description_a

									, gene_names_b.gene_name as gene_name_b
									, oln_id_b
									, gene_names_b.description as gene_description_b

									, type            
										from all_paralogs_and_ohnologs 
										left join gene_names as gene_names_a 
														on all_paralogs_and_ohnologs.oln_id_a = gene_names_a.oln_id
                                        left join gene_names as gene_names_b
														on all_paralogs_and_ohnologs.oln_id_b = gene_names_b.oln_id;")

# all_paralogs_and_ohnologs %>%
# 	dplyr::filter( grepl(",", type) )

write.table ( all_paralogs_and_ohnologs, file.path(supplementary_data_directory, "all_paralogs_and_ohnologs.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head(all_paralogs_and_ohnologs))
dim(all_paralogs_and_ohnologs)

```

## All interactions combined together  (part 1)
```{r}

# Cleaning transcription factor-target gene interactions
tf_network_collated <- tibble::as_tibble(tf_network) %>%
						clean_graph_table ( "regulator_oln_id", "target_oln_id", directed=TRUE) %>%
						collate_interactions_from_both_direction( "regulator_oln_id", "target_oln_id", 
																	   "transcription factor-target down", "transcription factor-target up",
																	   "td", "tu", 
																	   "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev")

# Cleaning kinase-substrate interactions
kinase_network_subset <- subset(kinase_network, score > sharifpoor_kinase_substrate_network_threshold)

kinase_network_collated <- 	tibble::as_tibble(kinase_network_subset) %>%
     clean_graph_table ( "kinase_oln_id", "target_oln_id", directed=TRUE) %>%
	collate_interactions_from_both_direction( "kinase_oln_id", "target_oln_id", 
													 "kinase-substrate down", "kinase-substrate up",
													 "kd", "ku", 
													 "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev")

# Cleaning SBI interactome
sbi_interactome <-  dplyr::select ( raw_sbi_interactome, one_of(c("oln_id_a", "oln_id_b")) ) %>% 
					dplyr::distinct()

sbi_interactome_collated <-  tibble::as_tibble(sbi_interactome) %>%
								clean_graph_table ( "oln_id_a", "oln_id_b", directed=FALSE) %>%
								collate_interactions_from_both_direction(  "oln_id_a", "oln_id_b", 
																			 "protein-protein", "protein-protein",
																			 "p", "p", 
																			 "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev")

# Cleaning the negative genetic interactions network

costanzo_2016_stringent_gi_collated <-  filtered_costanzo_stringent_2016 %>% 
	dplyr:: filter ( genetic_interaction_score < costanzo_stringent_negative_gi_score_threshold & 
					 	p_value < costanzo_stringent_negative_gi_p_value_threshold & 
					 	abs ( std_dev ) < costanzo_stringent_negative_gi_std_dev_threshold) %>%
	tibble::as_tibble() %>%
	clean_graph_table ( "query_oln_id_edited", "array_oln_id_edited", directed=FALSE) %>%
	collate_interactions_from_both_direction(  "query_oln_id_edited", "array_oln_id_edited",
											   "negative genetic interaction", "negative genetic interaction",
											   "ng", "ng",
											   "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev")

# All interactions combined together
interactions_combined <- dplyr::bind_rows(tf_network_collated, kinase_network_collated, sbi_interactome_collated, costanzo_2016_stringent_gi_collated)

interactions_combined <- sqldf( " select gene_names_a.gene_name as gene_name_a
									, oln_id_a
									, gene_names_a.description as gene_description_a

									, gene_names_b.gene_name as gene_name_b
									, oln_id_b
									, gene_names_b.description as gene_description_b

									, interaction_type
									, interaction_type_abbrev
								  from interactions_combined 
										left join gene_names as gene_names_a 
														on interactions_combined.oln_id_a = gene_names_a.oln_id
                                        left join gene_names as gene_names_b
														on interactions_combined.oln_id_b = gene_names_b.oln_id;")

kable(head(interactions_combined))
dim(interactions_combined)

```

## Get densely annotated triplets 
```{r}

densely_annotated_triplet_motif <- sqldf( "select data_a.gene_name as gene_name_a
, motifs.oln_id_a
, data_a.description as gene_description_a

, data_b.gene_name as gene_name_b
, motifs.oln_id_b
, data_b.description as gene_description_b

, data_c.gene_name as gene_name_c
, motifs.oln_id_c
, data_c.description as gene_description_c

, upper(motifs.type_ac) as type_of_interaction_a_to_c
, upper(motifs.type_bc) as type_of_interaction_b_to_c
, case when type_ac > type_bc then upper( type_ac || type_bc ) else upper( type_bc || type_ac ) end as type_of_motif
, case when data_a.essential = 1 and data_b.essential = 1 and data_c.essential = 1 then 1 else 0 end as all_proteins_essential
, case when data_a.periodically_expressed = 1 and data_b.periodically_expressed = 1 and data_c.periodically_expressed = 1 then 1 else 0 end as all_proteins_periodically_expressed
, case when data_a.overexpression_toxic = 1 and data_b.overexpression_toxic = 1 and data_c.overexpression_toxic = 1 then 1 else 0 end as all_proteins_toxic_upon_protein_expression

, data_a.essential as is_protein_a_essential
, data_a.periodically_expressed as is_protein_a_periodically_expressed
, data_a.overexpression_toxic as is_protein_a_toxic_upon_overexpression

, data_b.essential as is_protein_b_essential
, data_b.periodically_expressed as is_protein_b_periodically_expressed
, data_b.overexpression_toxic as is_protein_b_toxic_upon_overexpression

, data_c.essential as is_protein_c_essential
, data_c.periodically_expressed as is_protein_c_periodically_expressed
, data_c.overexpression_toxic as is_protein_c_toxic_upon_overexpression

from triplet_motifs_costanzo_2016  motifs
		left outer join essential_periodic_expression_toxic_overexpression data_a
			on data_a.oln_id = oln_id_a
		left outer join essential_periodic_expression_toxic_overexpression data_b
			on data_b.oln_id = oln_id_b
		left outer join essential_periodic_expression_toxic_overexpression data_c
			on data_c.oln_id = oln_id_c;
", stringsAsFactors=FALSE)

write.table ( densely_annotated_triplet_motif, file.path(supplementary_data_directory, "list_of_triplet_motifs.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head( densely_annotated_triplet_motif))
dim (densely_annotated_triplet_motif )
```

## Interactions that are from triplet motifs only
```{r}

gene_a <- as.character( as.vector(c( t(triplet_motifs_costanzo_2016[,1]) ,
									 t(triplet_motifs_costanzo_2016[,1])    , 
									 t(triplet_motifs_costanzo_2016[,2]) ) ))

gene_b <- as.character( as.vector(c( t(triplet_motifs_costanzo_2016[,2]) ,
									 t(triplet_motifs_costanzo_2016[,3])    , 
									 t(triplet_motifs_costanzo_2016[,3]) ) ))

edge_type_attributes <- as.character( as.vector( c( 
		rep( "ng", length(triplet_motifs_costanzo_2016[,1] )),
		t(triplet_motifs_costanzo_2016[, c("type_ac")]),
		t(triplet_motifs_costanzo_2016[, c("type_bc")])
	)  ) )

interactions_from_triplet_motifs <- data.frame( oln_id_a = gene_a, oln_id_b = gene_b, type_of_interaction = edge_type_attributes  )

interactions_from_triplet_motifs <- sqldf( " select gene_names_a.gene_name as gene_name_a
									, oln_id_a         
									, gene_names_a.description as gene_description_a

									, gene_names_b.gene_name as gene_name_b
									, oln_id_b
									, gene_names_b.description as gene_description_b

									, type_of_interaction            
										from interactions_from_triplet_motifs interactions 
										left join gene_names as gene_names_a 
														on interactions.oln_id_a = gene_names_a.oln_id
                                        left join gene_names as gene_names_b
														on interactions.oln_id_b = gene_names_b.oln_id;")

interactions_from_triplet_motifs <- interactions_from_triplet_motifs %>% dplyr::distinct()

write.table ( interactions_from_triplet_motifs, 
			  file.path(supplementary_data_directory, "interactions_from_triplet_motifs_only.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )

kable(head( interactions_from_triplet_motifs))
dim( interactions_from_triplet_motifs)

```

## All interactions combined together  (part 2)
```{r}

interactions_from_triplet_motifs <- dplyr::mutate(interactions_from_triplet_motifs, is_part_of_a_triplet=1) %>%
									dplyr::rename( interaction_type_abbrev =type_of_interaction )

interactions_combined <- dplyr::left_join (interactions_combined, interactions_from_triplet_motifs,
										   by = c("gene_name_a", "oln_id_a", "gene_description_a", 
										   	      "gene_name_b", "oln_id_b", "gene_description_b", "interaction_type_abbrev"))

interactions_combined <- dplyr::mutate( interactions_combined, is_part_of_a_triplet = ifelse( is.na(is_part_of_a_triplet), 0,1 ) )

write.table ( interactions_combined, file.path(supplementary_data_directory, "all_interactions.tab"),
			  sep="\t", 
			  quote=FALSE,
			  row.names = FALSE  )	
```

### 2017-09-17 Source/Analyze_GI_edges/compare_triplet_motif_gi_with_other_networks.R

@@ -151,30 +151,31 @@ count_triplet_motifs_compare_with_other_networks_second_step <- function (negati
 
 count_triplet_motifs_compare_with_other_networks <- function (triplet_motifs, type_ac, type_bc, interaction_type_abbrev, my_counts, total_count ) {
 	
-	a_ge_b <- filter_( triplet_motifs, paste(type_ac, ">=", type_bc) ) %>%
-		group_by_( .dots=lapply ( c(type_ac, type_bc, interaction_type_abbrev), as.name)  ) %>%
-		summarise_( .dots= list(counts=interp( ~sum(x), x=as.name(my_counts))) )
+	a_ge_b <- dplyr::filter_( triplet_motifs, paste(type_ac, ">=", type_bc) ) %>%
+			  dplyr::group_by_( .dots=lapply ( c(type_ac, type_bc, interaction_type_abbrev), as.name)  ) %>%
+			  dplyr::summarise_( .dots= list(counts=interp( ~sum(x), x=as.name(my_counts))) )
 	
 	columns_to_select <- c(type_ac, type_bc, interaction_type_abbrev, "counts")
 	
-	b_gt_a <- filter_( triplet_motifs, paste(type_bc, ">", type_ac) ) %>%
-		group_by_( .dots=lapply ( c(type_ac, type_bc, interaction_type_abbrev), as.name) ) %>%
-		summarise_( .dots= list(counts=interp( ~sum(x), x=as.name(my_counts))) ) %>%
-		dplyr::rename_( .dots=setNames(list(type_ac, type_bc, interaction_type_abbrev), c(type_bc, type_ac, interaction_type_abbrev) ) ) %>%
-		select( one_of( columns_to_select ))
+	b_gt_a <- dplyr::filter_( triplet_motifs, paste(type_bc, ">", type_ac) ) %>%
+			  dplyr::group_by_( .dots=lapply ( c(type_ac, type_bc, interaction_type_abbrev), as.name) ) %>%
+			  dplyr::summarise_( .dots= list(counts=interp( ~sum(x), x=as.name(my_counts))) ) %>%
+			  dplyr::rename_( .dots=setNames(list(type_ac, type_bc, interaction_type_abbrev), 
+			  							   c(type_bc, type_ac, interaction_type_abbrev) ) ) %>%
[…]

### 2017-09-17 Source/Common/count_triplet_motifs_helper.R

@@ -5,60 +5,14 @@
 ### Obtain the bootstrap p-value. This script contain the helper functions for the main script 'count_triplet_motifs_negative_interactions.R'.
 
 ## Project space:
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# cd '/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/'
 # psql sbi_triplet_motifs 
-
-#########################################################
-## Insert directed network into both directions into the edge list table, so the direction that tables join together won't affect the analyses
-
-## Inputs:
-## input_table - must have 4 columns only, which are: gene_a, gene_b, interaction type, interaction type abbreviation
-## gene_a - column name for input table that cotains gene A of the interaction
-## gene_b - column name for input table that cotains gene B of the interaction
-## interaction_type_forward - information on the type of interaction for A  ---> B 
-## interaction_type_reverse - information on the type of interaction for B <---> A
-## interaction_abbrev_forward - abbereviated information on the type of interaction for A ---> B 
-## interaction_abberv_reverse - abbereviated information on the type of interaction for B ---> A 
-## col_a - column name for gene A in the output table
-## col_b - column name for gene B in the output table
-## col_type - column name for the interaction type in the output table
-## col_abbrev - column name for the interaction type abbreviation in the output table
-
-## Output table:
-## Output table has 4 columns, denoted by col_a, col_b, col_type and col_abbrev mentioned in the inputs description above.
-collate_interactions_from_both_direction <- function (input_table, gene_a, gene_b, 
-													  interaction_type_forward, interaction_type_reverse, 
-													  interaction_abbrev_forward, interaction_abberv_reverse,
-													  col_a, col_b, col_type, col_abbrev) {
-	num_rows <- length(input_table[,1])
-	
-	new_table <- as.data.frame( matrix(ncol=4, nrow=2*num_rows))
-	
[…]

### 2017-09-17 Source/Figures/reshape_triplet_motifs_helper.R

@@ -1,481 +1,0 @@
-### Script: reshapte_triplet_motifs_helper.R
-### Author: Ignatius Pang 
-### Date: 13-7-2016
-### Description: Helper functions for plotting results for poster presentation.
-##                 * Compare observed and random values using box plot.
-##				   * Unpivot the full results table from randomization analyses
-
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Poster'
-# setwd ( '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/Poster/')
-
-#####################################################################
-
-## unpivot the columns motif_type, observed, and random
-unpivot_tables <- function(input_table, treatment_group)  { 
-	input_table_tidy <- input_table %>% 
-		dplyr::rename( observed=observed_counts, random=mean)  %>%
-		dplyr::select( one_of(c("motif_type", "observed", "random") )) %>%
-		tidyr::gather(  "obs_or_rand", "value", -motif_type )
-	
-	input_table_tidy <- cbind( input_table_tidy, group=
-							   	rep(treatment_group, length(input_table_tidy[,1])))
-	
-	return(input_table_tidy )
-}
-
-#####################################################################
-
-## Compare observed and random values, significant p-value = red, insignificant p-value = blue
-
-significance_to_colour <- function ( p_value, threshold) {
-	
-	
-	if (is.null(p_value)   ) {
-		
-		return("blue")
-	} 
-	
-	if (  is.na( p_value) | is.infinite(p_value) | is.nan(p_value) ) {
-		
-		return("blue")
-		
-	}
-
-	if ( p_value >= threshold ) {
-		
-		return("blue")
-		
-	} else if ( p_value < threshold ) {
-		
-		return("red")
-		
-	} 
-	
-	return("blue")
-	
-}
-
-
-## Compare observed and random values, significant p-value = red, insignificant p-value = blue
-boolean_to_colour <- function ( x) {
-	
-	
-	if (is.null(x)   ) {
-		
-		return("blue")
-	} 
-	
-	if (  is.na( x) | is.infinite(x) | is.nan(x) ) {
-		
-		return("blue")
-		
-	}
-	
-	if ( x == TRUE ) {
-		
-		return("red")
-		
-	}
-	
-	
-	
-	if ( x == FALSE ) {
-		
-		return("blue")
-		
-	}
-
-	
-	return("blue")
-	
-}
-
-
-# Function: print_box_plot_observed_vs_random
-# Description:
[…]

### 2017-09-17 Source/Figures/reshape_triplet_motifs_results.R

@@ -1,343 +1,0 @@
-### Script: reshapte_triplet_motifs_results.R
-### Author: Ignatius Pang 
-### Date: 13-7-2016
-### Description: Plotting results for poster presentation.
-##                 * Compare observed value and frequency distribution of random values using box plots.
-##				   * Compare observed value and the average values from randomization analyses using bar plots.  
-
-# cd '/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Figures'
-
-base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs"
-
-setwd ( '/home/ignatius/PostDoc/2016/Triplet_Motifs/Source/Figures/')
-
-library(dplyr)
-library(tidyr)
-# library(ggraptR)
-library(ggplot2)
-library(reshape2)
-
-#####################################################################								 
-
-source( file.path ( base_directory, 'Source/Figures/reshape_triplet_motifs_helper.R') )
-
-computational_results_directory <- file.path ( base_directory, "Results/Bootstrap_p_values") 
-figures_results_directory       <- file.path ( base_directory, "Results/Poster/Figures" ) 
-
-plot_background_colour <- "white"   # "#7E4E99" # 
-axis_text_colour <- "black"  # "#FFC000" # 
-
-
-### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
-### This setting is for the poster presentation.
-graphic_width <- 5
-graphic_height <- 3
-
-#####################################################################								 
-
-false_positive_rates <- 0.02
-
-all_15_types_of_triplet_motifs <- c("pp" 
-									,"tutu"
-									,"pku"
-									,"kuku"
-									,"ptd"
-									,"kdku"
-									,"ptu"
-									,"tdtd"
-									,"pkd"
-									,"tdtu"
-									,"kdkd"
-									,"tuku"
-									,"tdku"
-									,"tdkd"
-									,"tukd")
-
-################################################################################################
-##### Using boxplot to show the random values and using a point to show the observed results  ##
-################################################################################################
-
-### Motifs that are significant. Sorted in decending order of the number of observed motifs.
-
-negative_interactions_full <- read.table ( file= file.path( computational_results_directory, 
[…]

### 2017-09-17 Source/Negative_GI_Essential/collate_results_neg_gi_essential.R

@@ -1,6 +1,5 @@
 library(dplyr)
 library(tidyr)
-library(ggraptR)
 library(ggplot2)
 library(reshape2)
 

### 2017-09-17 Source/Negative_Genetic_Interactions/collate_randomization_results_neg_gi.R

@@ -1,7 +1,6 @@
 
 library(dplyr)
 library(tidyr)
-library(ggraptR)
 library(ggplot2)
 library(reshape2)
 

### 2017-09-17 Source/Overexpressed_Toxic_Genes/collate_results_overexpression.R

@@ -12,8 +12,6 @@ library(reshape2)
 options <- commandArgs(trailingOnly = TRUE)
 source( "./Common/parameters_file.R")
 
-source_directory <- file.path( base_directory, "Source")
-source_directory_common <- file.path( source_directory, "Common")
 source( file.path(source_directory_common, "count_triplet_motifs_helper.R") )
 source(  file.path(source_directory_common, "concatenate_result_files.R") )
 

### 2017-09-17 Source/Paralogs/count_triplet_motifs_paralogs.R

@@ -113,7 +113,7 @@ gi_and_paralog_table_b <- inner_join ( orthomcl_paralogs_table, filtered_costanz
 																		  "oln_id_a" = "array_oln_id_edited" ))  %>%
 	dplyr::select(one_of (c('oln_id_a', 'oln_id_b')) ) 
 
-result_table <- union ( gi_and_paralog_table_a, gi_and_paralog_table_b)
+result_table <- dplyr::union ( gi_and_paralog_table_a, gi_and_paralog_table_b)
 
 ##### 
 

### 2017-09-17 Source/Random_Edges/collate_random_edges_results.R

@@ -8,8 +8,11 @@ options <- commandArgs(trailingOnly = TRUE)
 source( "./Common/parameters_file.R")
 
 
+# figure_file_suffix <- ".tiff"
+figure_file_suffix <- ".pdf"
+
 source( file.path ( source_directory, 'Random_Edges/collate_random_edges_results_helper.R')) 
-source( file.path( source_directory, 'Figures/reshape_triplet_motifs_helper.R') )
+source( file.path( source_directory, 'Figures/paper_figures_helper.R') )
 
 ### Directories
 results_directory <- file.path ( results_directory, "Bootstrap_p_values/Random_Edges" ) 
@@ -31,7 +34,7 @@ JOB_NUMBERS <- 0:239  ## Need to be upldated once the corrected results has been
 adjust_job_number <- 1 ## Add this number to the job number to access the correct position in the  PARAMS array
 
 ## Use purple background and create a subset of the triplet motifs for the poster
-print_poster_results_purple_background <- TRUE
+print_poster_results_purple_background <- FALSE
 
 plot_background_colour <- "white"  
 axis_text_colour       <- "black" 
@@ -52,7 +55,6 @@ for( PERCENTAGE in PERCENTAGE_OF_ORIGINAL_NETWORK ) {
 		PARAMS <- c( PARAMS, PERCENTAGE) 
 	}
 }
-
 
 # random_edges_after_randomization_counts_0.2_1_1_1_.tab
 # random_edges_before_randomization_counts_0.2_1_1_1_.tab
@@ -92,7 +94,6 @@ randomization_collated_counts <- rbind( before_randomization_collated_counts, af
 
 randomization_collated_counts[, 'motif_type'] <- convert_triplet_motifs_name_to_paper_style( randomization_collated_counts[, 'motif_type'])
 
-write.table ( randomization_collated_counts, file=file.path ( final_results_directory, "randomization_collated_counts.txt"))
 
 
 #####################################################################################################################################
@@ -114,15 +115,14 @@ write.table ( stat_test_result_random_edges, file=file.path ( final_results_dire
 #####################################################################################################################################
 
 # The motif types sorted by largest to lowest count
-motif_types_sorted_by_counts_desc <- filter ( randomization_collated_counts, parameter==1 & experiment=='Before' & motif_type != 'total' ) %>%
-									select( one_of(c('experiment', 'motif_type', 'counts'))) %>% 
-									arrange(desc(counts)) %>%
[…]

### 2017-09-17 Source/Random_Edges/count_triplet_motifs_random_edges.R

@@ -138,19 +138,19 @@ run_add_or_remove_edges_once <- function(iteration_holder, filtered_costanzo_str
 ### Createa a table that include all kinase-substrate, protein-protein and transcription factor-gene interactions
 ### Do not contain genetic interactions
 
-tf_network_collated <- collate_interactions_from_both_direction_tbl_df(tbl_df(tf_network), "regulator_oln_id", "target_oln_id",
+tf_network_collated <- collate_interactions_from_both_direction(tibble::as_tibble(tf_network), "regulator_oln_id", "target_oln_id",
                                                                        "transcription factor-target down", "transcription factor-target up",
                                                                        "td", "tu",
                                                                        "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev")
 
 
-kinase_network_collated <- 	tbl_df(kinase_network_subset) %>%
-  collate_interactions_from_both_direction_tbl_df( "kinase_oln_id", "target_oln_id",
+kinase_network_collated <- tibble::as_tibble(kinase_network_subset) %>%
+						   collate_interactions_from_both_direction( "kinase_oln_id", "target_oln_id",
                                                    "kinase-substrate down", "kinase-substrate up",
                                                    "kd", "ku",
                                                    "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev")
 
-sbi_interactome_collated <- collate_interactions_from_both_direction_tbl_df( tbl_df(sbi_interactome), "oln_id_a", "oln_id_b",
+sbi_interactome_collated <- collate_interactions_from_both_direction( tibble::as_tibble(sbi_interactome), "oln_id_a", "oln_id_b",
                                                                              "protein-protein", "protein-protein",
                                                                              "p", "p",
                                                                              "oln_id_a", "oln_id_b", "interaction_type", "interaction_type_abbrev")

### 2017-09-17 Source/Repeated_GI_in_Motifs/collate_results_repeated_gi_in_motifs.R

@@ -1,90 +1,0 @@
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(reshape2)
-
-#####################################################################								 
-
-### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
-### This setting is for the poster presentation.
-
-base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/"
-figures_results_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Poster/Figures"
-	
-source_directory <- paste( base_directory, "Source/", sep="")
-source_directory_common <- paste( source_directory, "Common/",  sep="")
-source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
-source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
-
-results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Repeated_GI_in_Motifs/", sep="")
-final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
-
-	if (! file.exists(final_results_directory)){
-		dir.create(final_results_directory)
-
-	}
-
-################################################################################################################################################
-# Counts of Triplet Motifs Costanzo et al. 2010 dataset
-
-triplet_motifs_full_results_file     <- "full_results_counts_unique_gi_pairs_in_motifs.tab"
-count_triplet_motifs_randomized_file <- "randomized_counts_unique_gi_pairs_in_motifs.tab" 
-
-triplet_motifs_file_pattern      	 <- "^randomized_counts_unique_gi_pairs_in_motifs.tab"
-observed_file_pattern        		 <- "Job_20/observed_counts_unique_gi_pairs_in_motifs.tab"
-final_results_directory_pattern      <- "Final_Results"
-number_of_randomized_samples         <- 2000
-p_values 							 <- 0.05
-
-collated_table <- collate_result_files_helper ( results_directory, triplet_motifs_full_results_file, count_triplet_motifs_randomized_file,
-							  triplet_motifs_file_pattern, observed_file_pattern, final_results_directory_pattern,
-							  number_of_randomized_samples, p_values)
-
-
-
-################################################################################################
-
[…]

### 2017-09-17 Source/Repeated_GI_in_Motifs/collate_results_repeated_gi_in_motifs_freq_dist.R

@@ -2,28 +2,45 @@ library(dplyr)
 library(tidyr)
 library(ggplot2)
 library(reshape2)
+library(purrr)
 
 #####################################################################								 
 
 ### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
 ### This setting is for the poster presentation.
 
-base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/"
-figures_results_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Poster/Figures"
-graphic_width <- 5
-graphic_height <- 3
 
-source_directory <- paste( base_directory, "Source/", sep="")
-source_directory_common <- paste( source_directory, "Common/",  sep="")
-source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
-source( paste(source_directory_common, "concatenate_result_files.R", sep="") )
+source( "./Common/parameters_file.R")
 
-results_directory       <- paste( base_directory, "Results/Bootstrap_p_values/Repeated_GI_in_Motifs_Freq_Dist/", sep="")
-final_results_directory <- paste ( results_directory, "Final_Results/", sep="")
+source( file.path(source_directory_common, "count_triplet_motifs_helper.R" ) )
+source( file.path(source_directory_common, "concatenate_result_files.R") )
+source( file.path(source_directory, 'Figures/paper_figures_helper.R') )
+
+results_directory       <- file.path( base_directory, "Results/Bootstrap_p_values/Repeated_GI_in_Motifs_Freq_Dist" )
+final_results_directory <- file.path ( results_directory, "Final_Results" )
 
 if (! file.exists(final_results_directory)){
-		dir.create(final_results_directory)
+	  dir.create(final_results_directory)
 }
+
+################################################################################################################################################
+
+
+convert_panel_group_name <- function( input) {
+	
+	if( input =="protein_complexes" | input ==  "Protein Complexes") {
+		return ( "Protein Complexes")
+	} else if ( input ==  "regulatory_triplets" | input==  "Regulatory Triplets" ){
+		return( "Regulatory Triplets")
+	} else if ( input == "signaling_triplets" | input == "Signaling Triplets" ) {
+		return ( "Signaling Triplets")
[…]

### 2017-09-17 Source/Repeated_GI_in_Motifs/count_repeated_gi_in_motifs.R

@@ -1,168 +1,0 @@
-### Script: count_triplet_motifs_repeated_gi_edges.R
-### Author: Ignatius Pang 
-### Date: 27-5-2016
-### Description: For each type of triplet motif, count the number of motifs in which multiple triplet motifs of the same type share the same genetic interaction.  
-### Repeat the same calculation with randomizated 2000 networks and obtain the bootstrap p-value.
-### Network randomization preserves the degree distribution of the network. 
-
-#########################################################
-# Source location
-
-# psql sbi_triplet_motifs
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
-# 
-
-#########################################################
-### Parameters 
-options <- commandArgs(trailingOnly = TRUE)
-
-
-### Source the parameters file here 
-if ( length(options) != 0  )  { 
-	if ( options[1] == 'katana' | options[1] == 'clive')   {
-		source( "./parameters_file.R" )
-
-	} else {
-		source( "./Source/Common/parameters_file.R")
-	}
-} else {
-	source( "./Source/Common/parameters_file.R")
-}
-
-### Local Parameters
-if (is_run_locally) {
-	results_directory <- "./Results/Bootstrap_p_values_temp/Repeated_GI_in_Motifs/"
-	create_directory_if_not_exists(results_directory)
-}
-
-observed_counts_unique_gi_pairs_in_motifs_file     <- "observed_counts_unique_gi_pairs_in_motifs.tab"
-
-randomized_counts_unique_gi_pairs_in_motifs_file   <- "randomized_counts_unique_gi_pairs_in_motifs.tab"
-			  
-full_results_counts_unique_gi_pairs_in_motifs_file <- "full_results_counts_unique_gi_pairs_in_motifs.tab"		
-
-#########################################################
-
-#### Get the actual observed number of triplet motifs
-
-my_join_ac <- c( "query_oln_id_edited" = "oln_id_a")
-my_join_bc <- c( "array_oln_id_edited"= "oln_id_a", "oln_id_b" = "oln_id_b" )
-my_selected_columns <- c("query_oln_id_edited", "array_oln_id_edited", 
-						 "oln_id_b",  "interaction_type_abbrev.x",
-						 "interaction_type_abbrev.y", "genetic_interaction_score", "p_value", "std_dev")
-my_column_names <- c( "oln_id_a", 
-					  "oln_id_b",
-					  "oln_id_c",
-					  "type_ac",
[…]

### 2017-09-17 Source/Repeated_GI_in_Motifs/count_repeated_gi_in_motifs_detailed.R

@@ -1,134 +1,0 @@
-### Script: count_triplet_motifs_repeated_gi_edges.R
-### Author: Ignatius Pang 
-### Date: 27-5-2016
-### Description: For each type of triplet motif, count the number of motifs in which multiple triplet motifs of the same type share the same genetic interaction.  
-### Repeat the same calculation with randomizated 2000 networks and obtain the bootstrap p-value.
-### Network randomization preserves the degree distribution of the network. 
-
-#########################################################
-# Source location
-
-# psql sbi_triplet_motifs
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
-# 
-
-#########################################################
-### Parameters 
-options <- commandArgs(trailingOnly = TRUE)
-
-
-### Source the parameters file here 
-if ( length(options) != 0  )  { 
-	if ( options[1] == 'katana' | options[1] == 'clive')   {
-		source( "./parameters_file.R" )
-
-	} else {
-		source( "./Source/Common/parameters_file.R")
-	}
-}
-
-### Local Parameters
-if (is_run_locally) {
-	results_directory <- "./Results/Bootstrap_p_values_temp/Repeated_GI_in_Motifs_Detailed/"
-	create_directory_if_not_exists(results_directory)
-}
-
-observed_counts_unique_gi_pairs_in_motifs_file     <- "observed_counts_unique_gi_pairs_in_motifs.tab"
-
-randomized_counts_unique_gi_pairs_in_motifs_file   <- "randomized_counts_unique_gi_pairs_in_motifs.tab"
-			  
-full_results_counts_unique_gi_pairs_in_motifs_file <- "full_results_counts_unique_gi_pairs_in_motifs.tab"		
-
-#########################################################
-
-#### Get the actual observed number of triplet motifs
-
-my_join_ac <- c( "query_oln_id_edited" = "oln_id_a")
-my_join_bc <- c( "array_oln_id_edited"= "oln_id_a", "oln_id_b" = "oln_id_b" )
-my_selected_columns <- c("query_oln_id_edited", "array_oln_id_edited", 
-						 "oln_id_b",  "interaction_type_abbrev.x",
-						 "interaction_type_abbrev.y", "genetic_interaction_score", "p_value", "std_dev")
-my_column_names <- c( "oln_id_a", 
-					  "oln_id_b",
-					  "oln_id_c",
-					  "type_ac",
-					  "type_bc",
-					  "genetic_interaction_score",
[…]

### 2017-09-17 Source/Repeated_GI_in_Motifs/count_repeated_gi_in_motifs_freq_distribution.R

@@ -22,10 +22,10 @@ if ( length(options) != 0  )  {
 	if ( options[1] == 'katana' | options[1] == 'clive')   {
 		source( "./parameters_file.R" )
 	} else {
-		source( "./Source/Common/parameters_file.R")
+		source( "./Common/parameters_file.R")
 	}
 } else {
-	source( "./Source/Common/parameters_file.R")
+	source( "./Common/parameters_file.R")
 }
 
 ### Local Parameters
@@ -69,6 +69,33 @@ triplet_motifs_costanzo <- form_triplet_motifs(filtered_costanzo_stringent, inte
 # observed_counts_unique_gi_pairs_in_motifs <- count_repeated_gi_in_triplet_motifs( triplet_motifs_costanzo)
 
 observed_counts_unique_gi_pairs_in_motifs <- count_repeated_gi_in_triplet_motifs_distribution( triplet_motifs_costanzo)
+
+list_of_gi <- count_repeated_gi_in_triplet_motifs_look_at_gi( triplet_motifs_costanzo ) %>%
+			  dplyr::filter( motif_type != "others") %>%
+            #  dplyr::filter( oln_id_a == "YDR507C" & oln_id_b == "YCR002C" )
+			  dplyr::filter (motif_type == 'regulatory_triplets') %>%
+			  dplyr::filter ( counts == '5')
+
+# 
+# triplet_motifs_costanzo %>%
+# 	dplyr::filter( oln_id_a == "YDR507C"  & oln_id_b == "YCR002C"  & 
+# 				   	!( type_ac == 'p' & type_bc == 'p') & 
+# 				   	!( type_ac == 'kd' & type_bc == 'ku') ) %>%
+# 	dplyr::select( one_of ( c("oln_id_a", "oln_id_b", "oln_id_c"))) %>%
+# 	dplyr::distinct()
+
+
+
+triplet_motifs_costanzo %>%
+	dplyr::right_join ( list_of_gi) %>%
+	dplyr::filter(	( type_ac == 'tu'  & type_bc == 'tu') |
+				   	( type_ac == 'td' & type_bc == 'p') |
+				   	( type_ac == 'p' & type_bc == 'td') 
+				    )  %>%
+	as.data.frame()
+	# dplyr::select( one_of ( c("oln_id_a", "oln_id_b", "oln_id_c"))) %>%
+	# dplyr::distinct()
+
 
[…]

### 2017-09-17 Source/Repeated_GI_in_Motifs/run_repeated_gi_edges_detailed_on_katana_array.sh

@@ -1,78 +1,0 @@
-#!/bin/bash
-
-#PBS -N TMRepGIDetail[]
-#PBS -l nodes=1:ppn=16
-#PBS -l vmem=100gb
-#PBS -l walltime=12:00:00
-#PBS -j oe
-#PBS -M i.pang@unsw.edu.au
-#PBS -m ae
-# Clive
-#### PBS -l epilogue=/share/bioinfo/igy/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
-
-## Katana
-#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
-
-# Command for running array jobs 
-#PBS -t 1-40
-
-### To check he status of array jobs, this is the command:
-# qstat  -t -n1 -u z3371724
-
-PROJECT_DIRECTORY=Repeated_GI_in_Motifs_Detailed
-MAIN_SCRIPT="count_repeated_gi_in_motifs_detailed.R"
-LOG_PREFIX="count_repeated_gi_in_motifs_detailed"
-HPC_CLUSTER="katana"
-NUM_RANDOM_TRIALS=50
-
-if [ $HPC_CLUSTER = 'clive' ] 
-then 
-	## Clive
-	module load openmpi/1.10.3
-	module load R/3.3.1-bioconductor-3.3
-elif [ $HPC_CLUSTER = 'katana' ]
-then 
-	## Katana
-	module load openmpi/1.8.3
-	module load R/3.2.2
-else
-	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
-fi
-
-DATE=$(date +"%Y%m%d")
-
-export PROJECT_DIRECTORY
-
-### Create relevant directories
-
-if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY} ]; then
-  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}
-fi
-
-if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID} ]; then
-  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID}
-fi
-
[…]

### 2017-09-17 Source/Repeated_GI_in_Motifs/run_repeated_gi_edges_on_katana_array.sh

@@ -1,78 +1,0 @@
-#!/bin/bash
-
-#PBS -N TriMoRepGI[]
-#PBS -l nodes=1:ppn=16
-#PBS -l vmem=100gb
-#PBS -l walltime=12:00:00
-#PBS -j oe
-#PBS -M i.pang@unsw.edu.au
-#PBS -m ae
-# Clive
-#### PBS -l epilogue=/share/bioinfo/igy/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
-
-## Katana
-#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
-
-# Command for running array jobs 
-#PBS -t 1-40
-
-### To check he status of array jobs, this is the command:
-# qstat  -t -n1 -u z3371724
-
-PROJECT_DIRECTORY=Repeated_GI_in_Motifs
-MAIN_SCRIPT="count_repeated_gi_in_motifs.R"
-LOG_PREFIX="count_repeated_gi_in_motifs"
-HPC_CLUSTER="katana"
-NUM_RANDOM_TRIALS=50
-
-if [ $HPC_CLUSTER = 'clive' ] 
-then 
-	## Clive
-	module load openmpi/1.10.3
-	module load R/3.3.1-bioconductor-3.3
-elif [ $HPC_CLUSTER = 'katana' ]
-then 
-	## Katana
-	module load openmpi/1.8.3
-	module load R/3.2.2
-else
-	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
-fi
-
-DATE=$(date +"%Y%m%d")
-
-export PROJECT_DIRECTORY
-
-### Create relevant directories
-
-if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY} ]; then
-  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}
-fi
-
-if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID} ]; then
-  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID}
-fi
-
[…]

### 2017-09-17 Source/Unique_GI_in_Motifs/collate_results_unique_gi_in_motifs.R

@@ -1,43 +1,0 @@
-library(dplyr)
-library(tidyr)
-library(ggraptR)
-library(ggplot2)
-library(reshape2)
-
-#####################################################################								 
-
-### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
-### This setting is for the poster presentation.
-
-base_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/"
-
-source_directory <- paste( base_directory, "Source/", sep="")
-source_directory_common <- paste( source_directory, "Common/",  sep="")
-source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )
-source(  paste(source_directory_common, "concatenate_result_files.R", sep="") )
-
-results_directory                    <- paste( base_directory, "Results/Bootstrap_p_values/Unique_GI_in_Motifs/", sep="")
-final_results_directory              <- paste ( results_directory, "Final_Results/", sep="")
-
-	if (! file.exists(final_results_directory)){
-		dir.create(final_results_directory)
-
-	}
-
-################################################################################################################################################
-# Counts of Triplet Motifs Costanzo et al. 2010 dataset
-
-triplet_motifs_full_results_file     <- "full_results_counts_unique_gi_pairs_in_motifs.tab"
-count_triplet_motifs_randomized_file <- "randomized_counts_unique_gi_pairs_in_motifs.tab" 
-
-triplet_motifs_file_pattern      	 <- "^randomized_counts_unique_gi_pairs_in_motifs.tab"
-observed_file_pattern        		 <-  "Job_20/observed_counts_unique_gi_pairs_in_motifs.tab"
-final_results_directory_pattern      <- "Final_Results"
-number_of_randomized_samples         <- 2000
-p_values 							 <- 0.05
-
-collated_table <- collate_result_files_helper ( results_directory, triplet_motifs_full_results_file, count_triplet_motifs_randomized_file,
-							  triplet_motifs_file_pattern, observed_file_pattern, final_results_directory_pattern,
-							  number_of_randomized_samples, p_values)
-
-

### 2017-09-17 Source/Unique_GI_in_Motifs/count_triplet_motifs_unique_gi_edges.R

@@ -1,128 +1,0 @@
-### Script: count_triplet_motifs_repeated_gi_edges.R
-### Author: Ignatius Pang 
-### Date: 27-5-2016
-### Description: For each type of triplet motif, count the number of motifs in which multiple triplet motifs of the same type share the same genetic interaction.  
-### Repeat the same calculation with randomizated 2000 networks and obtain the bootstrap p-value.
-### Network randomization preserves the degree distribution of the network. 
-
-#########################################################
-# Source location
-
-# psql sbi_triplet_motifs
-# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
-# 
-
-#########################################################
-### Parameters 
-options <- commandArgs(trailingOnly = TRUE)
-
-
-### Source the parameters file here 
-if ( length(options) != 0  )  { 
-	if ( options[1] == 'katana' | options[1] == 'clive')   {
-		source( "./parameters_file.R" )
-
-	} else {
-		source( "./Source/Common/parameters_file.R")
-	}
-}
-
-### Local Parameters
-if (is_run_locally) {
-
-	results_directory <- "./Results/Bootstrap_p_values_temp/Unique_GI_in_Motifs/"
-	create_directory_if_not_exists(results_directory)
-}
-
-observed_counts_unique_gi_pairs_in_motifs_file <- "observed_counts_unique_gi_pairs_in_motifs.tab"
-
-randomized_counts_unique_gi_pairs_in_motifs_file <- "randomized_counts_unique_gi_pairs_in_motifs.tab"
-			  
-full_results_counts_unique_gi_pairs_in_motifs_file 	 <- "full_results_counts_unique_gi_pairs_in_motifs.tab"		
-
-#########################################################
-
-#### Get the actual observed number of triplet motifs
-
-my_join_ac <- c( "query_oln_id_edited" = "oln_id_a")
-my_join_bc <- c( "array_oln_id_edited"= "oln_id_a", "oln_id_b" = "oln_id_b" )
-my_selected_columns <- c("query_oln_id_edited", "array_oln_id_edited", 
-						 "oln_id_b",  "interaction_type_abbrev.x",
-						 "interaction_type_abbrev.y", "genetic_interaction_score", "p_value", "std_dev")
-my_column_names <- c( "oln_id_a", 
-					  "oln_id_b",
-					  "oln_id_c",
-					  "type_ac",
-					  "type_bc",
-					  "genetic_interaction_score",
[…]

### 2017-09-17 Source/Unique_GI_in_Motifs/run_unique_gi_edges_on_katana_array.sh

@@ -1,78 +1,0 @@
-#!/bin/bash
-
-#PBS -N TriMoRepGI[]
-#PBS -l nodes=1:ppn=16
-#PBS -l vmem=100gb
-#PBS -l walltime=12:00:00
-#PBS -j oe
-#PBS -M i.pang@unsw.edu.au
-#PBS -m ae
-# Clive
-#### PBS -l epilogue=/share/bioinfo/igy/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
-
-## Katana
-#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
-
-# Command for running array jobs 
-#PBS -t 1-40
-
-### To check he status of array jobs, this is the command:
-# qstat  -t -n1 -u z3371724
-
-PROJECT_DIRECTORY=Unique_GI_in_Motifs
-MAIN_SCRIPT="count_triplet_motifs_repeated_gi_edges.R"
-HPC_CLUSTER="katana"
-NUM_RANDOM_TRIALS=50
-LOG_PREFIX="count_triplet_motifs_repeated_gi_edges"
-
-if [ $HPC_CLUSTER = 'clive' ] 
-then 
-	## Clive
-	module load openmpi/1.10.3
-	module load R/3.3.1-bioconductor-3.3
-elif [ $HPC_CLUSTER = 'katana' ]
-then 
-	## Katana
-	module load openmpi/1.8.3
-	module load R/3.2.2
-else
-	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
-fi
-
-DATE=$(date +"%Y%m%d")
-
-export PROJECT_DIRECTORY
-
-### Create relevant directories
-
-if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY} ]; then
-  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}
-fi
-
-if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID} ]; then
-  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID}
-fi
-
[…]

### 2017-12-19 Source/Figures/paper_figures.Rmd
Update codes after submission of paper revision

@@
 ```{r}
+
+# install.packages( 'ggpubr')
 library(dplyr)
@@
 library(svglite)
+library(ggpubr)
 ```
@@
 
+# 
 # figure_file_suffix <- ".tiff"
@@
 
+local_base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source"
 source( file.path( local_base_directory, "./Common/parameters_file.R") ) 
 source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))
-source( file.path ( local_base_directory, './Figures/paper_figures_helper.R') )
+source( file.path ( source_directory, './Figures/paper_figures_helper.R') )
 
@@
 
+## Find over-represented motifs 
+Sort triplet motifs by count and get those that are significantly over-represented. 
+```{r}
+### Motifs that are significant. Sorted in decending order of the number of observed motifs.
+
+negative_interactions_full <- read.table ( file= file.path( computational_results_directory, 
+										   "Negative_Genetic_Interactions/Final_Results/full_results_triplet_motifs_costanzo_2016_collated.tab") )
+
+rows_to_include  <-  (negative_interactions_full[, "observed_counts"] > 
+					  	sum ( negative_interactions_full[, "observed_counts"] ) * false_positive_rates)  &
+					 (negative_interactions_full[, "enrichment_adj_p_values"]  < 0.05)
+
+rows_to_include <- ifelse ( is.na(rows_to_include), FALSE, rows_to_include)
+
+significant_types_of_motifs <- dplyr::arrange ( negative_interactions_full[rows_to_include, ], desc( observed_counts ) ) %>%
+							   dplyr::select ( one_of ( c( "motif_type"))) %>% 
+							   as.data.frame() %>%  
+							   t() %>% 
+							   as.vector()
+
+## Convert motif names to paper format
+significant_types_of_motifs <- convert_triplet_motifs_name_to_paper_style( significant_types_of_motifs )
+
+significant_types_of_motifs <- significant_types_of_motifs[ c("pp", "tutu",  "tdp", "pku", "kuku", "pkd" )]
+
+```
+
+## Analyze how filtering the negative genetic interaction by the stringency in fitness score affects the six types of triplet motifs. 
+```{r}
+
+full_results_file_list   <- Sys.glob ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent*/Final_Results/full*")
+random_results_file_list <- Sys.glob ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent*/Final_Results/random*")
+
+list_of_percentiles <- as.numeric( gsub( ".*More_stringent_network_(\\d+).*", "\\1", full_results_file_list) )
+
+observed_results_file_list <- map_chr( list_of_percentiles,
+	 function(x) { 
+	 		paste( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent_network_", x,"/Job_", 
+	 		   		(x / 5*20),"/results_count_triplet_motifs_costanzo.tab", sep="") 
+	 	 })
+
+input_list <- list( full_results_file_list, 
+			 random_results_file_list, 
+			 observed_results_file_list)
+
+## Test length of inpu
+map ( input_list, length)
+
+results_list <- combine_graphs_using_faceting ( input_list, list_of_percentiles, sort_facet_decreasing=TRUE)
+
+is_significant_tidy <- results_list$is_significant
+observed_data_tidy <- results_list$observed_data
+random_data_tidy <- results_list$random_data
+
+ significance_color <- sapply ( is_significant_tidy[,"is_significant"], function(x) {  return(boolean_to_colour(x)) } )
+
+ background_colour <- "white"
+
+	return_plot <- ggplot(random_data_tidy, aes(facet_type, value)) + 
+			geom_boxplot() + 
+			geom_point( data=observed_data_tidy, aes(x=facet_type, y=value  )   ## Add the observed values as additional points
+						, color=significance_color, size=2 , alpha=0.5) 	+ # , size=4 , alpha=0.5
+			xlab( "Percentage of Negative Genetic Interactions") 	+ 
+			ylab( "Counts")  + 
+			facet_grid( key ~., scales="free") +
+			theme( plot.background = element_rect(fill = background_colour, color=background_colour), 
+				   axis.text = element_text(colour = axis_text_colour),
+				   axis.title = element_text(colour = axis_text_colour),
+				   strip.text.y=element_text(face="italic"))
+
+	ggsave(file.path(figures_results_directory, paste( "more_stringent_network_all", figure_file_suffix, sep="") ), 
+	   plot=return_plot, width=graphic_width, 
+	   height=graphic_height*2 )
+
+```
+
 ## Figure 1a. 
@@
 
-## Find over-represented motifs 
-Sort triplet motifs by count and get those that are significantly over-represented. 
-```{r}
-### Motifs that are significant. Sorted in decending order of the number of observed motifs.
-
-negative_interactions_full <- read.table ( file= file.path( computational_results_directory, 
-										   "Negative_Genetic_Interactions/Final_Results/full_results_triplet_motifs_costanzo_2016_collated.tab") )
-
-rows_to_include  <-  (negative_interactions_full[, "observed_counts"] > sum ( negative_interactions_full[, "observed_counts"] ) * false_positive_rates)  &
-					 (negative_interactions_full[, "enrichment_adj_p_values"]  < 0.05)
-
-rows_to_include <- ifelse ( is.na(rows_to_include), FALSE, rows_to_include)
-
-significant_types_of_motifs <- dplyr::arrange ( negative_interactions_full[rows_to_include, ], desc( observed_counts ) ) %>%
-							   dplyr::select ( one_of ( c( "motif_type"))) %>% 
-							   as.data.frame() %>%  
-							   t() %>% 
-							   as.vector()
-
-## Convert motif names to paper format
-significant_types_of_motifs <- convert_triplet_motifs_name_to_paper_style( significant_types_of_motifs )
-
-significant_types_of_motifs <- significant_types_of_motifs[ c("pp", "tutu",  "tdp", "pku", "kuku", "pkd" )]
-
-```
-
 ## Figure 2a.
@@
 ```{r}
-
 ### Print the analysis of negative genetic interactions 
@@
 
+## The maximum number of overlapping triplets for each gi to show (e.g. highest nubmer of overlaps)
+statistical_analysis <- dplyr::filter( statistical_analysis, counts <= max_num_overlapping_triplets_to_show)
+
 ## Draw counts distribution table 
@@
 Please refer to the file 'print_triplet_network_specific_network.Rmd'
+
+## Supplementary Figure 1. Frequency of triplet motifs where all three proteins in the triplet share the same GO slim term.
+```{r}
+
+full_results_file_list <- Sys.glob ( paste ( computational_results_directory, 
+										 "/GO_Terms_*/Final_Results/full_results_table_*_in_tri_motifs.tab", sep="")  )
+
+random_results_file_list <- Sys.glob ( paste( computational_results_directory, 
+																 "/GO_Terms_*/Final_Results/randomized_counts_*_in_tri_motifs.tab", sep=""  ) )
+
+observed_results_file_list <- Sys.glob ( paste( computational_results_directory, 
+																"/GO_Terms_*/Job_20/observed_counts_go_terms*_in_tri_motifs.tab", sep="" ))
+
+list_of_go_types <- factor( c("Biological\nProcess", "Cellular\nComponent", "Molecular\nFunction") )
+
+input_list <- list( full_results_file_list, 
+			 random_results_file_list, 
+			 observed_results_file_list)
+
+## Test number of input files in each element of the 'input_list' object, 
+## They should all have the same length
+map ( input_list, length)
+
+output_file_name <- file.path(figures_results_directory, paste( "significant_gene_ontology_all", figure_file_suffix, sep="") )
+
+result_list <- combine_graphs_using_faceting ( input_list, list_of_go_types, sort_facet_decreasing=FALSE)
+
+motif_type_significance_box_plot_vertical_stack_faceting( result_list$observed_data, 
+														  result_list$random_data, 
+														  result_list$is_significant, 
+														  output_file_name, graphic_width, graphic_height*2)
+
+```
+
+## Supplementary Figure 2. Frequency of triplet motifs where all three proteins in the triplet share the same phenotype annotation. 
+```{r}
+
+### Print the analysis of negative genetic interactions 
+negative_interactions_full     <- read.table ( file= file.path( computational_results_directory, 
+											   "Phenotype/Final_Results/full_results_table_phenotypes_in_tri_motifs.tab") )
+
+negative_interactions_full     <- dplyr::arrange ( negative_interactions_full, desc( observed_counts ) )
+
+negative_interactions_random   <- read.table ( file=  file.path( computational_results_directory, 
+																 "Phenotype/Final_Results/randomized_counts_phenotypes_in_tri_motifs.tab"  ))
+
+negative_interactions_observed <- read.table ( file= file.path( computational_results_directory, 
+																"Phenotype/Job_20/observed_counts_phenotypes_in_tri_motifs.tab"), 
+								               header=TRUE )
+
+print_box_plot_observed_vs_random(negative_interactions_observed, negative_interactions_random, negative_interactions_full, significant_types_of_motifs,
+								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
+								  axis_text_colour=axis_text_colour)
+
+ggsave(file.path(figures_results_directory, paste( "significant_Phenotype", figure_file_suffix, sep="") ), 
+	   plot=last_plot(), width=graphic_width, 
+	   height=graphic_height )
+
+```

### 2017-12-19 Source/Phenotype/clean_phenotype_data.Rmd
Update codes after submission of paper revision

---
title: "Clean SGD's phenotype data"
output: html_notebook
---

```{r}
library(dplyr)
library(data.table)

```

## Commmand to transfer phenotye data from UNSW to home
```{r}
# rsync -avh  babs:/home/ignatius/PostDoc/2016/Triplet_Motifs/Data/SGD/Phenotype_20171201         /home/ignatius/PostDoc/2016/Triplet_Motifs/Data/SGD

```

```{r}

# remove viable
# remove inviable
# strain_background match S288C only
# reference not 16455487

# mutant_type + phenotype + chemical

phenotype_data <- read.table ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Data/SGD/Phenotype_20171201/phenotype_data.tab", 
			 sep="\t", header=FALSE, stringsAsFactors = FALSE, quote = "", comment.char="")

colnames(phenotype_data ) <- c( "oln_id",	"feature_type",	"gene_name",	"sgd_id",	
	"reference",	"experiment_type",	"mutant_type",	"allele",	"strain_background",	"phenotype"	,
	"chemical",	"condition",	"details",	"reporter" )

## Only get the chemical-genetics data 
filtered_phenotype_data_temp <- phenotype_data %>%
						dplyr::filter( !( phenotype %in% c( 'viable', 'inviable' ) ) ) %>%
						dplyr::filter(  strain_background  %in% c( "S288C", "S288C (BY4742)", 
																   "S288C (BY4743)", "S288C (BY4741)") ) %>% 
						dplyr::filter( grepl( "PMID: 16455487\\|", reference ) == FALSE ) %>% # Sopko overexpression dataset is excluded here
						dplyr::filter( grepl( ": normal", phenotype ) == FALSE ) %>%  ## avoid any normal phenotype
						dplyr::filter ( grepl( "resistance to chemicals", phenotype ) == TRUE |
											grepl( "thermotolerance", phenotype) == TRUE |
											grepl( "resistance", phenotype) == TRUE |
											grepl( "morphology", phenotype) == TRUE) %>%
 						dplyr::mutate ( phenotype_label = paste ("(", mutant_type, ", ",
																	 phenotype, ", ", chemical, ")", sep=""  ))

head( filtered_phenotype_data_temp)

filtered_phenotype_data_temp %>% 
	dplyr::select (one_of(c('oln_id'))) %>% 
	dplyr::distinct() %>% 
	dplyr::count()

```

### Filters that are no longer needed
```{r}
							# dplyr::filter( !(grepl( "competitive fitness: decreased", phenotype ) == TRUE &  chemical==" ")  ) %>%
							# dplyr::filter( !(grepl( "competitive fitness: increaseed", phenotype ) == TRUE &  chemical==" ")  ) %>%
							# dplyr::filter( !(grepl( "haploinsufficient", phenotype ) == TRUE &  chemical==" " )  ) %>%
							# dplyr::filter( !(grepl( "haploproficient", phenotype ) == TRUE  &  chemical==" " ) ) %>%
							# dplyr::filter( !(grepl( "viability: decreased", phenotype ) == TRUE  &  chemical==" " ) ) %>%
							# dplyr::filter( !(grepl( "growth", phenotype ) == TRUE  &  chemical==" " ) ) %>%
							# dplyr::filter( !(grepl( "replicative lifespan: decreased", phenotype ) == TRUE  &  chemical==" " ) ) %>%
```

## lookup table of phenotype to id
```{r}

phenotype_list <-  as.factor( filtered_phenotype_data_temp[, "phenotype_label"])

phenotype_to_id_lookup_table <- data.frame(  id = as.numeric(phenotype_list), 
							 phenotype_label=phenotype_list )

write.table ( phenotype_to_id_lookup_table,
			  file.path("/home/ignatius/PostDoc/2016/Triplet_Motifs/Data/SGD/Phenotype_20171201/phenotype_to_id_lookup_table.tab"),
			  row.names = FALSE, sep="\t", quote=FALSE)

```

## a phenotype must be associated with at least 3 genes for it to be included in triplet analysis
```{r}

filtered_phenotype_data_num_class <- filtered_phenotype_data_temp

filtered_phenotype_data_num_class[, "phenotype_label"] <- as.numeric( as.factor(filtered_phenotype_data_num_class[, "phenotype_label"])  )

to_include_phenotype <- table ( as.numeric( filtered_phenotype_data_num_class[, "phenotype_label"] )  ) > 2 
to_include_phenotype_table <- data.frame( to_include = to_include_phenotype)
rownames( to_include_phenotype_table) <- as.integer(names( to_include_phenotype))
to_include_phenotype_table <- tibble::rownames_to_column(to_include_phenotype_table)
to_include_phenotype_table[,"rowname"] <- as.integer( to_include_phenotype_table[,"rowname"] )

filtered_phenotype_data_num_class <-  filtered_phenotype_data_num_class %>%
	dplyr::left_join(to_include_phenotype_table, by=c( "phenotype_label" = "rowname")) %>%
	dplyr::filter( to_include == TRUE) %>%
	dplyr::select( -to_include)

dim(filtered_phenotype_data_num_class)

write.table ( filtered_phenotype_data_num_class,
			  file.path("/home/ignatius/PostDoc/2016/Triplet_Motifs/Data/SGD/Phenotype_20171201/filtered_phenotype_data_num_class.tab"),
			  row.names = FALSE, sep="\t", quote=FALSE)
```

```{r}
filtered_phenotype_data <- filtered_phenotype_data_num_class %>%
							dplyr::select ( one_of( c("oln_id", "phenotype_label"))) %>%
							dplyr::distinct()

filtered_phenotype_list_table <- filtered_phenotype_data %>%
								 dplyr::group_by( oln_id) %>%
								 dplyr::summarise( phenotype_label_list=list(phenotype_label)  ) %>%
								 as.data.frame()

filtered_phenotype_data_detailed_list <- filtered_phenotype_data_temp %>%
										 dplyr::select ( one_of( c("oln_id", "phenotype_label"))) %>%
										 dplyr::distinct() %>%
								 		 dplyr::group_by( oln_id) %>%
								 		 dplyr::summarise( phenotype_label_list=list(phenotype_label)  ) %>%
								 		 as.data.frame()

```

```{r}
# 
# pairs_of_genes_with_same_phenotype <- filtered_phenotype_data %>%
# 										dplyr::inner_join( filtered_phenotype_data, by=c("phenotype_label"= "phenotype_label")) %>%
# 										dplyr::filter( oln_id.x > oln_id.y) 
# 
# dim( pairs_of_genes_with_same_phenotype)
# 
# 
# temp_phenotype <- dplyr::rename(filtered_phenotype_data, "oln_id.z" = "oln_id" )
# 
# triplets_of_genes_with_same_phenotype	<- pairs_of_genes_with_same_phenotype	%>%
# 										dplyr::inner_join( temp_phenotype, 
# 														   by=c("phenotype_label"= "phenotype_label")) %>%
# 										dplyr::filter( oln_id.x != oln_id.z & oln_id.y != oln_id.z )
# 
# 
# dim( triplets_of_genes_with_same_phenotype)

```

## Convert into a matrix of phenotypes
```{r}

# filtered_phenotype_data_for_matrix <- filtered_phenotype_data_temp %>%
# 							dplyr::select ( one_of( c("oln_id", "phenotype_label"))) %>%
# 							dplyr::distinct() %>%
# 							dplyr::mutate( phenotype_label = as.integer(as.factor(phenotype_label))) %>%
# 							dplyr::mutate( has_phenotype = 1)
# 
# 
# head( filtered_phenotype_data_for_matrix)

#phenotype_data_matrix <- tidyr::spread( filtered_phenotype_data_for_matrix, key =phenotype_label, value=has_phenotype, fill=0)

#head(phenotype_data_matrix[1:10,])

# gene_pair_phenotype_distance_matirx <- dist( phenotype_data_matrix)

```

### 2017-12-19 Source/Supplementary_Files/supplementary_files.Rmd
Update codes after submission of paper revision

@@
 						    na.strings="", quote="", sep="\t")
+
+## Table list all triplets where the genetic interactions overlap with other types of interactions 
+triplets_gi_overlapping_other_edges <- read.table( file.path(supplementary_data_directory, "triplets_with_overlapping_edges.tab"), 
+										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )
+
+## List of GO terms shared by all three proteins in the triplet 
+## The tables need t be pre-computed by the script: "GO_terms/count_go_terms.R"
+shared_go_terms_BP_per_triplet <- read.table( file.path(supplementary_data_directory, "shared_go_terms_BP_per_triplet.tab"), 
+										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )
+shared_go_terms_CC_per_triplet <- read.table( file.path(supplementary_data_directory, "shared_go_terms_CC_per_triplet.tab"), 
+										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )
+shared_go_terms_MF_per_triplet <- read.table( file.path(supplementary_data_directory, "shared_go_terms_MF_per_triplet.tab"), 
+										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )
+
+## List of phenotypes shared by all three proteins in the triplet 
+## Phenotype data obtained from SGD.
+## This table needs to be pre-computed by the script 'Phenotype/count_triplets_with_same_phenotype.R'
+triplet_shared_phenotype <- read.table( file.path(supplementary_data_directory, "motif_and_phenotypes_detail.txt"), 
+										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )
 
@@
 
+## Calculate the number of other triplets sharing this negative genetic interactions
+num_of_overlapping_triplets_table <-  densely_annotated_triplet_motif %>%
+								dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b", "oln_id_c", 
+															"type_of_interaction_a_to_c", "type_of_interaction_b_to_c" ))) %>%
+								dplyr::group_by( oln_id_a, oln_id_b) %>%
+								# Remember that we need to minus one here to exclude itself from the count
+								dplyr::summarise( num_of_other_triplets_sharing_this_genetic_interaction = n() - 1) %>% 
+								dplyr::ungroup()
+
+densely_annotated_triplet_motif <- sqldf( " select x.*
+											, coalesce( overlap.P, 0) as P
+											, coalesce( overlap.K1, 0) as K1
+											, coalesce( overlap.K2, 0) as K2
+											, coalesce( overlap.T1, 0) as T1	
+											, coalesce( overlap.T2, 0) as T2
+											, coalesce( repeated_gi.num_of_other_triplets_sharing_this_genetic_interaction, 0) 
+                                   					as num_of_other_triplets_sharing_this_genetic_interaction
+											, coalesce(w_bp.go_BP_count, 0 ) as num_go_BP_shared
+											, w_bp.go_BP_intersect_abc
+											, coalesce(w_cc.go_CC_count, 0 ) as num_go_CC_shared
+											, w_cc.go_CC_intersect_abc
+											, coalesce(w_mf.go_MF_count, 0 ) as num_go_MF_shared
+											, w_mf.go_MF_intersect_abc
+											, coalesce(y.num_phenotype_shared, 0) num_phenotype_shared
+											, y.phenotype_intersect_abc
+										    from densely_annotated_triplet_motif x
+												 left join triplets_gi_overlapping_other_edges overlap 
+												   on  x.oln_id_a = overlap.oln_id_a
+														and x.oln_id_b = overlap.oln_id_b
+														and x.oln_id_c = overlap.oln_id_c 
+														and x.type_of_interaction_a_to_c = upper(overlap.type_ac)
+														and x.type_of_interaction_b_to_c = upper(overlap.type_bc)
+												 left join num_of_overlapping_triplets_table repeated_gi
+													on x.oln_id_a = repeated_gi.oln_id_a
+														and x.oln_id_b = repeated_gi.oln_id_b
+												 left join shared_go_terms_BP_per_triplet  w_bp
+										  			on  x.oln_id_a = w_bp.oln_id_a
+														and x.oln_id_b = w_bp.oln_id_b
+														and x.oln_id_c = w_bp.oln_id_c 
+														and x.type_of_interaction_a_to_c = upper(w_bp.type_ac)
+														and x.type_of_interaction_b_to_c = upper(w_bp.type_bc)
+												 left join shared_go_terms_CC_per_triplet  w_cc
+										  			on  x.oln_id_a = w_cc.oln_id_a
+														and x.oln_id_b = w_cc.oln_id_b
+														and x.oln_id_c = w_cc.oln_id_c 
+														and x.type_of_interaction_a_to_c = upper(w_cc.type_ac)
+														and x.type_of_interaction_b_to_c = upper(w_cc.type_bc)
+												 left join shared_go_terms_MF_per_triplet  w_mf
+										  			on  x.oln_id_a = w_mf.oln_id_a
+														and x.oln_id_b = w_mf.oln_id_b
+														and x.oln_id_c = w_mf.oln_id_c 
+														and x.type_of_interaction_a_to_c = upper(w_mf.type_ac)
+														and x.type_of_interaction_b_to_c = upper(w_mf.type_bc)
+										  		 left join triplet_shared_phenotype y
+										  			on  x.oln_id_a = y.oln_id_a
+														and x.oln_id_b = y.oln_id_b
+														and x.oln_id_c = y.oln_id_c 
+														and x.type_of_interaction_a_to_c = upper(y.type_ac)
+														and x.type_of_interaction_b_to_c = upper(y.type_bc)
+														 ")
+
 write.table ( densely_annotated_triplet_motif, file.path(supplementary_data_directory, "list_of_triplet_motifs.tab"),
@@
 
-## Interactions that are from triplet motifs only
+## Interactions that are part of triplets, excluding those that are not part of triplets
 ```{r}

### 2017-12-19 Source/Analyze_GI_edges/compare_triplet_motif_gi_with_other_networks.R

@@ -26,6 +26,11 @@ observed_results_table_file   <- "observed_results_table_file.tab"
 randomized_results_table_file <- "randomized_results_table.tab"
 output_full_results_table     <- "full_results_table.tab"
 
+
+supplementary_data_directory <- file.path(results_directory, "Supplementary_Files" ) 
+create_directory_if_not_exists(supplementary_data_directory)
+
+
 if (is_run_locally) {
 	
 	results_directory <- file.path( results_directory, "Bootstrap_p_values_temp/Analyze_GI_edges" ) 
@@ -185,6 +190,71 @@ count_triplet_motifs_compare_with_other_networks <- function (triplet_motifs, ty
 	return( triplet_motif_counts)
 }
 
+
+## Function to get table for supplementary data in the 
+count_triplet_motifs_compare_with_other_networks_for_supplementary <- function (negative_genetic_interaction, interactions_combined, 
+																				oln_id_a, oln_id_b, type_ac, type_bc, interaction_type_abbrev, my_counts, total_count ) {
+	
+	colnames( negative_genetic_interaction)[colnames( negative_genetic_interaction) == "oln_id_a"] <-  "query_oln_id_edited"
+	colnames( negative_genetic_interaction)[colnames( negative_genetic_interaction) == "oln_id_b"] <-  "array_oln_id_edited"
+	
+	my_join_ac <- c( "query_oln_id_edited" = "oln_id_a")
+	my_join_bc <- c( "array_oln_id_edited"= "oln_id_a", "oln_id_b" = "oln_id_b" )
+	my_selected_columns <- c("query_oln_id_edited", "array_oln_id_edited", 
+							 "oln_id_b",  "interaction_type_abbrev.x",
+							 "interaction_type_abbrev.y", "genetic_interaction_score")
+	my_column_names <- c( "oln_id_a", 
+						  "oln_id_b",
+						  "oln_id_c",
+						  "type_ac",
+						  "type_bc",
+						  "genetic_interaction_score" )      
+	
+	triplet_motifs <- form_triplet_motifs(negative_genetic_interaction, interactions_combined, interactions_combined,
+										  my_join_ac, my_join_bc, my_selected_columns, my_column_names)
+	
+	table_join_by_names <- c( oln_id_a, oln_id_b)
+	names( table_join_by_names ) <- c( oln_id_a, oln_id_b)
+	
+	compare_gi_with_other_networks <- dplyr::left_join(triplet_motifs, interactions_combined,
+													   by=table_join_by_names) 
+	
[…]

### 2017-12-19 Source/Common/concatenate_result_files.R

@@ -208,8 +208,8 @@ collate_result_files_helper <- function ( raw_results_directory, triplet_motifs_
 	final_results_table_count_triplet_motifs <- get_full_results_table(count_triplet_motifs_observed, count_triplet_motifs_randomized, 
 																	   p.value=p_values) 
 
-	write.table ( count_triplet_motifs_randomized, file=file.path( final_results_directory, count_triplet_motifs_randomized_file ))
-	write.table (final_results_table_count_triplet_motifs, file=file.path( final_results_directory, triplet_motifs_full_results_file ) )
+	write.table ( count_triplet_motifs_randomized, file=file.path( raw_results_directory, final_results_directory_pattern, count_triplet_motifs_randomized_file ))
+	write.table (final_results_table_count_triplet_motifs, file=file.path( raw_results_directory, final_results_directory_pattern, triplet_motifs_full_results_file ) )
 	
 	return( final_results_table_count_triplet_motifs)
 }

### 2017-12-19 Source/Common/count_triplet_motifs_helper.R

@@ -1153,6 +1153,172 @@ count_triplet_motifs_in_protein_complexes <- function ( triplet_motifs_list, pro
 	return ( motif_and_protein_complexes)
 }
 
+#########################################################
+
+
+count_triplet_motifs_go_terms_helper <- function ( triplet_motifs_list, go_terms_table) {
+	
+	motif_and_go_terms <- dplyr::left_join( triplet_motifs_list, go_terms_table, by=c("oln_id_a" = "oln_id") ) %>%
+		dplyr::rename( go_term_a = go_term) %>%
+		dplyr::left_join( go_terms_table, by=c("oln_id_b" = "oln_id") ) %>%
+		dplyr::rename( go_term_b = go_term) %>%
+		dplyr::left_join( go_terms_table, by=c("oln_id_c" = "oln_id") ) %>%
+		dplyr::rename( go_term_c = go_term) %>%
+		dplyr::filter( go_term_a == go_term_b & go_term_b == go_term_c) 
+	
+	return ( motif_and_go_terms)
+}
+
+## Function: count_triplet_motifs_go_terms
+## Count the number of triplet motif in which the protein products of all three genes have the same GO terms
+## Input:
+## triplet_motifs_list: A table containing the global list of triplet motifs
+##	This input table must contain the following columns, 
+#   oln_id_a - The Ordered Locus Name of Gene A
+#   oln_id_b - The Ordered Locus Name of Gene B
+#   oln_id_c - The Ordered Locus Name of Gene C
+#   type_ac - The type of interactions between gene A and gene C, one of p, ku, kd, tu, td
+#   type_bc - The type of interactions between gene B and gene C, one of p, ku, kd, tu, td  
+## go_terms_table: A table containing the list of GO terms for each protein.
+##	This input table must contain the following columns, 
+#   go_term - The GO term of the protein
+#   oln_id - The Ordered Locus Name corresponding to the protein 
+count_triplet_motifs_go_terms <- function ( triplet_motifs_list, go_terms_table) {
+	
+	motif_and_go_terms <- count_triplet_motifs_go_terms_helper ( triplet_motifs_list, go_terms_table) 
+	
+	## This following two lines ensure that we don't double count protien complexes. 
+	## Sometimes, all three proteins can be found in more than one complexes.
+	motif_and_go_terms <- motif_and_go_terms %>% 
[…]

### 2017-12-19 Source/Common/epilogue_array_jobs.sh

@@ -5,3 +5,4 @@ echo "    ${TMPDIR}"
 echo "    ${PBS_O_WORKDIR}"
 echo
 
+rsync -a ${TMPDIR}/*.log ${PBS_O_WORKDIR}/

### 2017-12-19 Source/Common/parameters_file.R

@@ -38,7 +38,8 @@ array_job_id 			     <- NULL
 random_number_seed 		     <- 1985
 number_of_cores_to_use 		 <- 24
 number_of_randomized_trials  <- 100
-num_iteration_rewire_network <- NULL # Number of times each network is rewired before counting the triplet motifs
+num_iteration_rewire_network <- NULL # Number of times each network is rewired before counting the triplet motifs.
+									 # If null, this is equal to the number of edges in the network. 
 use_costanzo_2010_dataset 	 <- FALSE
 
 
@@ -51,8 +52,8 @@ results_directory 		<- "./"
 source_directory_common <- "./"
 
 if ( length(options) != 0 &
-	! (  options[1] == 'katana' | options[1] == 'clive' | options[1] == 'local'  )  ) {
-		stop ( 'First command line parameter must either by katana, clive, or local') 
+	 ! (  options[1] == 'katana' | options[1] == 'clive' | options[1] == 'local'  )  ) {
+	stop ( 'First command line parameter must either by katana, clive, or local') 
 }
 
 if ( length(options) != 0 
@@ -101,7 +102,7 @@ if (is_run_locally == TRUE) {
 	number_of_cores_to_use <- 4
 	number_of_randomized_trials <- 4
 	num_iteration_rewire_network <- 0.001 # Number of times each network is rewired before counting the triplet motifs
-
+	
 	data_directory <- paste( local_base_directory, "Data/Triplet_Motifs_R_data/", sep="")
 	source_directory <- paste( local_base_directory, "Source/", sep="")
 	results_directory <- paste( local_base_directory, "Results/", sep="")

### 2017-12-19 Source/Figures/paper_figures_helper.R

@@ -90,7 +90,7 @@ boolean_to_colour <- function ( x) {
 }
 
 
-# Function: print_box_plot_observed_vs_random
+# Function: print_box_plot_observed_vs_random_helper
 # Description:
 # 	Compare observed and random values using box plot.
 # 	Significant observed data is shown as a red dot, Insignificant observed data is shown as a blue dot.
@@ -109,8 +109,11 @@ boolean_to_colour <- function ( x) {
 #   false_positive_counts_threshold: if the observed count is lower than a proportion of the total observed counts, then it is considered a false positive
 #   p_value_threshold: p-value below which the item is considered to be statistically significant
 #   p_value_column: which column from the p_values_data column to obtain the p-value, default value = "enrichment_adj_p_values"
-
-print_box_plot_observed_vs_random <- function (observed_data, random_data, p_values_data, motifs_to_include = NULL, ordering=NULL, plot_type="boxplot", 
+## Return:
+# The tidied up observed_data
+# The tidied up random_data
+# A list called is_significant, showing which motif is significant
+print_box_plot_observed_vs_random_helper <- function (observed_data, random_data, p_values_data, motifs_to_include = NULL, ordering=NULL, plot_type="boxplot", 
 											   background_colour="white", axis_text_colour="black", false_positive_counts_threshold = 0.02, p_value_threshold=0.05,
 											   p_value_column="enrichment_adj_p_values") {
 	
@@ -139,7 +142,7 @@ print_box_plot_observed_vs_random <- function (observed_data, random_data, p_val
 		colnames(observed_data ) <- c(current_observed_data_colnames, motif_types_to_be_added) 
 	}
 	
-	## Fix missing motif types in observed data, according the ordering requested
+	## Fix missing motif types in observed data, according to the ordering requested
 	if ( !is.null(ordering) & is.vector(ordering) ) { 
 		motif_types_to_be_added <- setdiff ( ordering,   
 											 unique(colnames( observed_data) )  )
@@ -204,12 +207,56 @@ print_box_plot_observed_vs_random <- function (observed_data, random_data, p_val
 	is_significant <- (observed_data[, "value"] > sum ( observed_data[, "value"] ) * false_positive_counts_threshold)  &
 							(p_values_data[, p_value_column]  < p_value_threshold)
 	
+	names(is_significant) <-  p_values_data[,"motif_type"]
+	
+	return( list (  observed_data=observed_data,  
[…]

### 2017-12-19 Source/GO_terms/count_go_terms.R

@@ -1,0 +1,194 @@
+### Script: count_triplet_motifs_negative_gi_essential_genes.R
+### Author: Ignatius Pang 
+### Date: 27-5-2016
+### Description: Count the observed number of triplet motifs in which the protein products of all three genes are found in the same protein complex. 
+### Repeat the same calculation with randomizated 2000 networks and obtain the bootstrap p-value.
+### Randomization conserves the degree distribution of the network. 
+
+#########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# 
+
+#########################################################
+### Global Parameters 
+
+options <- commandArgs(trailingOnly = TRUE)
+
+### Source the header file here 
+
+if ( length(options) != 0 
+	 & ( options[1] == 'katana' | options[1] == 'clive')  ) {
+	
+	source( "./parameters_file.R" )
+	
+} else {
+	source( "./Common/parameters_file.R")
+}
+
+
+if ( length(options) < 4 ) {
+	
+	go_type  <- "BP"
+	
+} else {
+	go_type <- options[4]
+	
+	if ( ! ( go_type %in% c( "BP", "MF", "CC") )){
+		stop( "count_go_terms: go_type is incorrect")
+	}
+}
+
+supplementary_data_directory <- file.path(results_directory, "Supplementary_Files" ) 
+create_directory_if_not_exists(supplementary_data_directory)
+
+### Local Parameters
+if (is_run_locally) {
+
+	results_directory <- file.path ( results_directory, "Bootstrap_p_values_temp/GO_terms") 
+	create_directory_if_not_exists( results_directory)
+}
+
+observed_counts_go_terms_file    <- paste( "observed_counts_go_terms", go_type,"_in_tri_motifs.tab", sep="")
+randomized_counts_go_terms_file  <- paste( "randomized_counts_go_terms", go_type,"_in_tri_motifs.tab", sep="")
+full_results_go_terms_file  	 <- paste( "full_results_table_go_terms", go_type,"_in_tri_motifs.tab", sep="")
+
+#########################################################
+
+#### Get the actual observed number of triplet motifs
+
+my_join_ac <- c( "query_oln_id_edited" = "oln_id_a")
+my_join_bc <- c( "array_oln_id_edited"= "oln_id_a", "oln_id_b" = "oln_id_b" )
+my_selected_columns <- c("query_oln_id_edited", "array_oln_id_edited", 
[…]

### 2017-12-19 Source/GO_terms/run_triplet_motifs_go_terms_CC_on_katana_array.sh

@@ -1,0 +1,82 @@
+#!/bin/bash
+
+#PBS -N GO_Terms_CC[]
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=100gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+# Clive
+##### PBS -l epilogue=/share/bioinfo/igy/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
+
+## Katana
+#PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
+
+# Command for running array jobs 
+#PBS -t 1-20
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+GO_TYPE="CC"
+PROJECT_DIRECTORY="GO_Terms_${GO_TYPE}"
+MAIN_SCRIPT="count_go_terms.R"
+HPC_CLUSTER="katana"
+NUM_RANDOM_TRIALS=100
+LOG_PREFIX="count_triplet_motif_go_terms_${GO_TYPE}"
+
+if [ $HPC_CLUSTER = 'clive' ] 
+then 
+	## Clive
+	module load openmpi/1.10.3
+	module load R/3.3.2-intel_mkl
+elif [ $HPC_CLUSTER = 'katana' ]
+then 
+	## Katana
+	module load openmpi/1.8.3
+	module load R/3.2.2
+else
+	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
+fi
+
+DATE=$(date +"%Y%m%d")
+
+export PROJECT_DIRECTORY
+
+### Create relevant directories
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}
+fi
+
+if [ ! -d $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID} ]; then
+  mkdir $PBS_O_WORKDIR/../../Results/${PROJECT_DIRECTORY}/Job_${PBS_ARRAYID}
+fi
+
[…]

### 2017-12-19 Source/Negative_Genetic_Interactions/count_triplet_motifs_negative_interactions.R

@@ -4,14 +4,14 @@
 ### Description: Count the observed number of triplet motifs. Randomize the respective networks and count the number triplet motifs, repeat randomization 1000 times.
 ### Obtain the bootstrap p-value
 
-#########################################################
+##########################################################
 # Source location
 
 # psql sbi_triplet_motifs
 # cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
 # 
 
-#########################################################
+##########################################################
 ### Global Parameters 
 
 options <- commandArgs(trailingOnly = TRUE)

### 2017-12-19 Source/Phenotype/collate_results_phenotype.R

@@ -1,0 +1,40 @@
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(reshape2)
+
+#####################################################################								 
+
+### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
+### This setting is for the poster presentation.
+
+options <- commandArgs(trailingOnly = TRUE)
+source( "./Common/parameters_file.R")
+
+source_directory_common <- file.path( source_directory, "Common")
+source( file.path(source_directory_common, "count_triplet_motifs_helper.R") )
+source(  file.path(source_directory_common, "concatenate_result_files.R") )
+
+################################################################################################################################################
+# Counts of Triplet Motifs, all three proteins share the phenotype
+
+results_directory_bp                    <- file.path( results_directory, "Bootstrap_p_values/Phenotype")
+final_results_directory_bp              <- file.path ( results_directory_bp, "Final_Results")
+
+create_directory_if_not_exists(final_results_directory_bp)
+
+triplet_motifs_full_results_file     <- "full_results_table_phenotypes_in_tri_motifs.tab"
+count_triplet_motifs_randomized_file <- "randomized_counts_phenotypes_in_tri_motifs.tab" 
+
+triplet_motifs_file_pattern      	 <- "^randomized_counts_phenotypes.*_in_tri_motifs.tab"
+observed_file_pattern        		 <-  "Job_20/observed_counts_phenotypes_in_tri_motifs.tab"
+final_results_directory_pattern      <- "Final_Results"
+number_of_randomized_samples         <- 2000
+p_values 							 <- 0.05
+
+collated_table <- collate_result_files_helper ( results_directory_bp, triplet_motifs_full_results_file, count_triplet_motifs_randomized_file,
+							  triplet_motifs_file_pattern, observed_file_pattern, final_results_directory_pattern,
+							  number_of_randomized_samples, p_values)
+
+
+################################################################################################################################################

### 2017-12-19 Source/Repeated_GI_in_Motifs/collate_results_repeated_gi_in_motifs_freq_dist.R

@@ -130,8 +130,8 @@ statistical_analysis <- observed_data %>%
 	dplyr::select ( one_of ( c( "motif_type", "counts", "observed_count", "p_value", "adj_p_value", "is_significant") )) %>%
 	dplyr::rename(total_count = observed_count) %>%
 	dplyr::mutate( is_significant_color = factor ( boolean_to_colour(is_significant), levels=c("red", "blue") )) %>%
-	dplyr::mutate( total_count = total_count + 1) %>%  ### Add 1 as a pseudo count for drawing in log scale
-	dplyr::filter( counts <= max_num_overlapping_triplets_to_show )  
+	dplyr::mutate( total_count = total_count + 1) # %>%  ### Add 1 as a pseudo count for drawing in log scale
+	# dplyr::filter( counts <= max_num_overlapping_triplets_to_show )  
      ## For the protein complexes class, there is a genetic interaction with up to ~80 overlapping triplets, so we want to trim the x-axis smaller.
 	
 

### 2018-01-03 Source/More_stringent_network/fitness_scores_quartiles.Rmd
Add files

---
title: "Analysis of the distribution of fitness scores for strigent set (negative interactions only)"
output: html_notebook
---

```{r}

plot (density( filtered_costanzo_stringent[, "genetic_interaction_score"]))

summary( filtered_costanzo_stringent[, "genetic_interaction_score"])

#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# -1.1616 -0.2308 -0.1670 -0.2077 -0.1381 -0.1201

filtered_costanzo_stringent  %>% dplyr::count()
dplyr::filter( filtered_costanzo_stringent,  genetic_interaction_score < -0.1381) %>% dplyr::count()
dplyr::filter( filtered_costanzo_stringent,  genetic_interaction_score < -0.1670) %>% dplyr::count()
dplyr::filter( filtered_costanzo_stringent,  genetic_interaction_score < -0.2308) %>% dplyr::count()

```

```{r}

quantile_threshold <- quantile( filtered_costanzo_stringent[, "genetic_interaction_score"], probs=seq(0.70, 0.95, 0.05))

names( quantile_threshold)

```

### 2018-01-03 Source/More_stringent_network/collate_randomization_results_more_stringent.R

@@ -1,0 +1,61 @@
+
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(reshape2)
+library(purrr)
+
+#####################################################################								 
+
+## Load all the parameters 
+options <- commandArgs(trailingOnly = TRUE)
+source( "./Common/parameters_file.R")
+
+
+### Graphic width and heigth for the boxplots of the randomization results. The observed value is shown in a dot. 
+### This setting is for the poster presentation.
+false_positive_rates <- 0.02
+
+source_directory_common <- file.path( source_directory, "Common")
+source( file.path(source_directory_common, "count_triplet_motifs_helper.R") )
+source(  file.path(source_directory_common, "concatenate_result_files.R") )
+
+################################################################################################################################################
+# Counts of Triplet Motifs 3rd quartile
+
+#folders_list <- Sys.glob ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent*")
+# percentile <- c(100, seq ( 0.7, 0.95, 0.05)*100 )
+
+percentile <- seq( 5, 100, 5) 
+
+folders_list <- map_chr (percentile,  function(x) {
+					 paste ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent_network_", x, sep="") })
+
+
+my_collate_result <- function ( input_directory,  percentile  ) { 
+	results_directory_percentile                    <- input_directory
+	final_results_directory              <- file.path ( results_directory_percentile, "Final_Results")
+	
+	create_directory_if_not_exists(final_results_directory)
+	
+	triplet_motifs_file_pattern      	 <- "^randomized_results_table*"
+	triplet_motifs_full_results_file     <- paste("full_results_triplet_motifs_more_stringent_", percentile ,"pc.tab", sep="")
+	count_triplet_motifs_randomized_file <- paste("randomized_counts_triplet_motifs_more_stringent_", percentile ,"pc.tab",sep="" )
+	
+	job_number <- (percentile / 5*20)
+	
+	observed_file_pattern 	 	 <- paste( "Job_", job_number, "/results_count_triplet_motifs_costanzo.tab", sep="")
+	final_results_directory_pattern  <- "Final_Results"
+	number_of_randomized_samples         <- 2000
+	p_values 						   	 <- 0.05
+	
+	final_results_table_count_triplet_motifs <- collate_result_files_helper ( results_directory_percentile, 
[…]

### 2018-01-03 Source/More_stringent_network/count_triplet_motifs_more_stringent_v2.R

@@ -1,0 +1,173 @@
+### Script: count_triplet_motifs_negative_interactions.R
+### Author: Ignatius Pang 
+### Date: 20-5-2016
+### Description: Count the observed number of triplet motifs. Randomize the respective networks and count the number triplet motifs, repeat randomization 1000 times.
+### Obtain the bootstrap p-value
+
+##########################################################
+# Source location
+
+# psql sbi_triplet_motifs
+# cd '/media/z3371724/PostDoc/2016/Triplet_Motifs/Source/'
+# 
+
+##########################################################
+### Global Parameters 
+
+options <- commandArgs(trailingOnly = TRUE)
+
+### Source the header file here 
+
+if ( length(options) != 0 
+	 & ( options[1] == 'katana' | options[1] == 'clive')  ) {
+	
+	source( "./parameters_file.R" )
+	
+} else {
+	source( "./Common/parameters_file.R")
+}
+
+quantile_chosen  <- 100
+
+
+if ( length(options) >= 4 ) {
+	quantile_chosen <- as.numeric(options[4])
+	print( paste( "quantile_chosen = " , quantile_chosen ))
+	
+	if ( !( quantile_chosen %in%   seq(0.05, 1.00, 0.05)*100) )   {
+		warning( paste( "incorrect quantile chosen", quantile_chosen) )
+	}
+}
+
+quantile_chosen <- paste( quantile_chosen, "%", sep="")
+
+### Local Parameters
+
+output_observed_triplet_motif_counts  <- "results_count_triplet_motifs_costanzo.tab" # "results_count_triplet_motifs_costanzo.tab"
+randomized_results_table_file         <- "randomized_results_table.tab"
+output_enrichment_p_value             <- "enrichment_p_value_fixed.tab"
+output_depletion_p_value              <- "depletion_p_value_fixed.tab"
+output_full_results_table             <- "full_results_table.tab"
+
+if (is_run_locally) {
+
+	results_directory <- file.path( results_directory, "Bootstrap_p_values_temp/Negative_Genetic_Interactions")
+	
+	create_directory_if_not_exists(results_directory)
+}
+
+#########################################################
+
+
+quantile_threshold <- quantile( filtered_costanzo_stringent[, "genetic_interaction_score"], probs=seq(0.05, 1.00, 0.05))
+
+fitness_threshold <- quantile_threshold[[quantile_chosen]]
+
+#### filter the negative genetic interaction networks base on the fitness score threshold
[…]

### 2018-01-03 Source/More_stringent_network/run_triplet_motifs_array_on_katana_enum_pc.sh

@@ -1,0 +1,105 @@
+#!/bin/bash
+
+#PBS -N QuantileEn[]
+#PBS -l nodes=1:ppn=16
+#PBS -l vmem=100gb
+#PBS -l walltime=12:00:00
+#PBS -j oe
+#PBS -M i.pang@unsw.edu.au
+#PBS -m ae
+# Clive
+####PBS -l epilogue=/share/bioinfo/igy/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
+
+## Katana
+# PBS -l epilogue=/srv/scratch/z3371724/Triplet_Motifs/Source/Common/epilogue_array_jobs.sh
+
+# Command for running array jobs 
+#PBS -t 1-400
+
+### To check he status of array jobs, this is the command:
+# qstat  -t -n1 -u z3371724
+
+
+PERCENTAGE_OF_ORIGINAL_NETWORK=$( seq 5 5 100 )
+INNER_LOOP=$(seq 1 1 20)
+PARAMS=()
+
+for PERCENTAGE in $PERCENTAGE_OF_ORIGINAL_NETWORK
+do
+
+	for OUTPUT in $INNER_LOOP
+	do
+		echo $PERCENTAGE
+		PARAMS+=($PERCENTAGE)
+	done
+done
+
+# echo ${PARAMS[*]}
+#exit
+
+ARRAY_POSITION="$((PBS_ARRAYID - 1))"  
+
+network_size_proportion=${PARAMS[${ARRAY_POSITION}]}
+
+QUANTILE=${network_size_proportion}
+PROJECT_DIRECTORY="More_stringent_network_${QUANTILE}"
+MAIN_SCRIPT="count_triplet_motifs_more_stringent_v2.R"
+HPC_CLUSTER="katana"
+NUM_RANDOM_TRIALS=100
+LOG_PREFIX="count_motifs_more_stringent_${QUANTILE}"
+
+
+if [ $HPC_CLUSTER = 'clive' ] 
+then 
+	## Clive
+	module load openmpi/1.10.3
+	module load R/3.3.2-intel_mkl
+elif [ $HPC_CLUSTER = 'katana' ]
+then 
+	## Katana
+	module load openmpi/1.8.3
+	module load R/3.2.2
+else
+	echo "Invalid HPC_CLUSTER = ${HPC_CLUSTER}"
+fi
+
[…]

### 2018-01-19 Source/Figures/paper_figures.Rmd
Update paper figures and supplementary materials

@@
 # install.packages( 'ggpubr')
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(reshape2)
+library(tidyverse)
 library(svglite)
@@
 
+# Whether to use log y-axis
+is_use_log_y_axis <- TRUE
+
 ```
@@
 significant_types_of_motifs <- significant_types_of_motifs[ c("pp", "tutu",  "tdp", "pku", "kuku", "pkd" )]
-
-```
-
-## Analyze how filtering the negative genetic interaction by the stringency in fitness score affects the six types of triplet motifs. 
-```{r}
-
-full_results_file_list   <- Sys.glob ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent*/Final_Results/full*")
-random_results_file_list <- Sys.glob ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent*/Final_Results/random*")
-
-list_of_percentiles <- as.numeric( gsub( ".*More_stringent_network_(\\d+).*", "\\1", full_results_file_list) )
-
-observed_results_file_list <- map_chr( list_of_percentiles,
-	 function(x) { 
-	 		paste( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent_network_", x,"/Job_", 
-	 		   		(x / 5*20),"/results_count_triplet_motifs_costanzo.tab", sep="") 
-	 	 })
-
-input_list <- list( full_results_file_list, 
-			 random_results_file_list, 
-			 observed_results_file_list)
-
-## Test length of inpu
-map ( input_list, length)
-
-results_list <- combine_graphs_using_faceting ( input_list, list_of_percentiles, sort_facet_decreasing=TRUE)
-
-is_significant_tidy <- results_list$is_significant
-observed_data_tidy <- results_list$observed_data
-random_data_tidy <- results_list$random_data
-
- significance_color <- sapply ( is_significant_tidy[,"is_significant"], function(x) {  return(boolean_to_colour(x)) } )
-
- background_colour <- "white"
-
-	return_plot <- ggplot(random_data_tidy, aes(facet_type, value)) + 
-			geom_boxplot() + 
-			geom_point( data=observed_data_tidy, aes(x=facet_type, y=value  )   ## Add the observed values as additional points
-						, color=significance_color, size=2 , alpha=0.5) 	+ # , size=4 , alpha=0.5
-			xlab( "Percentage of Negative Genetic Interactions") 	+ 
-			ylab( "Counts")  + 
-			facet_grid( key ~., scales="free") +
-			theme( plot.background = element_rect(fill = background_colour, color=background_colour), 
-				   axis.text = element_text(colour = axis_text_colour),
-				   axis.title = element_text(colour = axis_text_colour),
-				   strip.text.y=element_text(face="italic"))
-
-	ggsave(file.path(figures_results_directory, paste( "more_stringent_network_all", figure_file_suffix, sep="") ), 
-	   plot=return_plot, width=graphic_width, 
-	   height=graphic_height*2 )
 
@@
 
+# head( as.data.frame(negative_interactions_observed) + 1)
+# temp_random <- negative_interactions_random
+# negative_interactions_random[ is.na(negative_interactions_random)] <- 0
+# head( as.data.frame(temp_random) + 1)
+
 print_box_plot_observed_vs_random(negative_interactions_observed, negative_interactions_random, negative_interactions_full, significant_types_of_motifs,
 								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
-								  axis_text_colour=axis_text_colour)
+								  axis_text_colour=axis_text_colour, log_y_axis=is_use_log_y_axis)
 
@@
 								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
-								  axis_text_colour=axis_text_colour)
+								  axis_text_colour=axis_text_colour, log_y_axis=is_use_log_y_axis)
 
@@
 
-ggplot_analyze_gi_edges <- ggplot(analyze_gi_edges_counts_gathered, aes(edge_type, counts)) +
-	geom_boxplot() +
+analyze_gi_edges_counts_gathered <- dplyr::mutate( analyze_gi_edges_counts_gathered, counts = ifelse( is.na(counts), 1, counts+1) )
+
+joined_table_summarized_filtered <- dplyr::mutate( joined_table_summarized_filtered, observed_counts = observed_counts +1)
+
+ggplot_analyze_gi_edges <- ggplot(analyze_gi_edges_counts_gathered, aes(edge_type, counts))
+
+if (is_use_log_y_axis == TRUE ) {
+
+	ggplot_analyze_gi_edges <- ggplot_analyze_gi_edges + scale_y_log10()
+}
+
+ggplot_analyze_gi_edges <- ggplot_analyze_gi_edges +
+	geom_boxplot( width = 6) +  # The width parameter changes the width of the boxplot and how the boxplot bunch up together.
 	## Add the observed values as additional points
@@
 ### With wrapping
-ggplot_analyze_gi_edges + 
+ggplot_analyze_gi_edges <- ggplot_analyze_gi_edges + 
 	## Add faceting
-	facet_wrap ( ~ motif_type , scales="free") +
+	facet_wrap ( ~ motif_type, scales="free") +
 	xlab( "Types of Motifs") 	+ 
@@
 		   text = element_text(size=20)
-		   )
+		   )  +  
+    scale_x_discrete( )
 
 ggsave(file.path(figures_results_directory, paste( "analyze_gi_edges_wrap", figure_file_suffix, sep="")), 
-	   plot=last_plot(), width=10.3, height=7.5 ) # , width=10, height=7
+	   plot=ggplot_analyze_gi_edges, width=10.3, height=7.5 ) # , width=10, height=7
 ```
@@
 print_box_plot_observed_vs_random(overexpression_c_observed, overexpression_c_random, overexpression_c_full, significant_types_of_motifs,
-								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour )
+								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
+								  log_y_axis=is_use_log_y_axis )
 
@@
 														  result_list$is_significant, 
-														  output_file_name, graphic_width, graphic_height*2)
+														  output_file_name, graphic_width, graphic_height*2, log_y_axis = is_use_log_y_axis )
 
@@
 								  ordering=significant_types_of_motifs, plot_type="boxplot", background_colour=plot_background_colour, 
-								  axis_text_colour=axis_text_colour)
+								  axis_text_colour=axis_text_colour, log_y_axis = is_use_log_y_axis )
 
@@
 ```
+
+## Supplementary Figure 3a. 
+```{r}
+
+# randomization_collated_counts %>% dplyr::select(one_of(c("motif_type"))) %>% distinct()
+# randomization_collated_counts %>% dplyr::filter ( motif_type == "KDKD"  & parameter == 0.2)
+
+motif_types_sorted_by_counts_desc <- c( "PP", "TUTU", "TDP", "PKU",  "KUKU",  "PKD",  
+										"PTU", "KDKU", "TDTD", "KDKD", "TDTU", "TUKD", "TDKD", "TDKU", "TUKU" )
+
+summary_for_heatmap <-  randomization_collated_counts %>%
+	dplyr::filter (  is.na(motif_type) == FALSE ) %>%
+	tidyr::spread( experiment, counts ) %>%
+	dplyr::select( one_of( c( "motif_type", "parameter", "Before", "After"))) %>%
+	dplyr::mutate( Before=ifelse(is.na(Before),0, Before), 
+				   After=ifelse(is.na(After),0, After) ) %>%
+	dplyr::group_by( motif_type, parameter ) %>%
+	dplyr::summarise ( median_before=median(Before), median_after=median(After) ) %>%
+	dplyr::mutate( fold_enrichment_ratio = (median_before + 1)/ (median_after  + 1)) %>%
+	dplyr::ungroup()
+
+summary_for_heatmap <- summary_for_heatmap %>%
+								 dplyr::mutate( motif_type = factor(motif_type, levels = rev(motif_types_sorted_by_counts_desc) ),
+								 				parameter = factor ( parameter, levels = sort ( unique (parameter ))				     ))
+
+stat_test_result_random_edges <- stat_test_result_random_edges %>%
+								 dplyr::mutate( motif_type = factor(motif_type, levels = rev(motif_types_sorted_by_counts_desc) ), 
+								 			   parameter = factor ( parameter, levels = sort ( unique (parameter )))	, 
+								 			   is_significant_star = ifelse( is_significant==1, "*", "")  )
+
+ggplot(summary_for_heatmap, aes(y= motif_type, x= parameter )) +
+	geom_raster(aes(fill=(fold_enrichment_ratio) ) ) +
+	geom_text(data=stat_test_result_random_edges, aes(label=is_significant_star   )) + 
+	scale_fill_gradientn( colors=rev(heat.colors(5))) + #heat.colors
+	theme( axis.text.y = element_text(face = "italic")) + 
+	guides(fill=guide_colourbar(title="Fold enrichment ratio")) + 
+	xlab( "Proportion of negative genetic interactions added or removed") +
+	ylab ('Triplet Motif Types')
+
+ggsave(file.path(figures_results_directory, paste("randomization_collated_results_color_by_fold_enrichment", figure_file_suffix, sep="")), plot=last_plot())
+
+# summary_for_heatmap %>% dplyr::filter ( motif_type == "KDKD"  & parameter == 0.2) 
+#summary_for_heatmap %>% dplyr::filter ( motif_type == "TUKU"  )
+
+```
+
+## Supplementary Figure 3b. 
+```{r}
+
+motif_types_sorted_by_counts_desc <- c( "PP", "TUTU", "TDP", "PKU",  "KUKU",  "PKD",  
+										"PTU", "KDKU", "TDTD", "KDKD", "TDTU", "TUKD", "TDKD", "TDKU", "TUKU" )
+
+stat_test_result_random_edges <- stat_test_result_random_edges %>%
+								 dplyr::mutate( motif_type = factor(motif_type, levels = rev(motif_types_sorted_by_counts_desc) ), 
+								 			   is_significant_star = ifelse( is_significant==1, "*", "")  )
+
+ggplot(stat_test_result_random_edges, aes(y= motif_type, x= parameter )) +
+	geom_raster(aes(fill= -log10(boot_n_counts_adj_p_value+ 1/2000*15 ) )) +
+	scale_fill_gradientn( colors=rev(heat.colors(5))) + # heat.colors
+	theme( axis.text.y = element_text(face = "italic")) + 
+	guides(fill=guide_colourbar(title=expression("-log"[10]*"(adjusted p-value)"))) + 
+	geom_text( aes(label=is_significant_star   ))  + 
+	xlab( "Proportion of negative genetic interactions added or removed") +
+	ylab ('Triplet Motif Types')
+
+ggsave(file.path(figures_results_directory, paste("randomization_collated_results_color_by_p_values", figure_file_suffix, sep="")), plot=last_plot() )
+
+```
+
+## Supplementary Figure 4. Analyze how filtering the negative genetic interaction by the stringency in fitness score affects the six types of triplet motifs. 
+```{r}
+
+full_results_file_list   <- Sys.glob ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent*/Final_Results/full*")
+random_results_file_list <- Sys.glob ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent*/Final_Results/random*")
+
+list_of_percentiles <- as.numeric( gsub( ".*More_stringent_network_(\\d+).*", "\\1", full_results_file_list) )
+
+observed_results_file_list <- map_chr( list_of_percentiles,
+	 function(x) { 
+	 		paste( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent_network_", x,"/Job_", 
+	 		   		(x / 5*20),"/results_count_triplet_motifs_costanzo.tab", sep="") 
+	 	 })
+
+input_list <- list( full_results_file_list, 
+					random_results_file_list, 
+					observed_results_file_list)
+
+## Test length of inpu
+map ( input_list, length)
+
+results_list <- combine_graphs_using_faceting ( input_list, list_of_percentiles, sort_facet_decreasing=TRUE)
+
+is_significant_tidy <- results_list$is_significant
+observed_data_tidy <- results_list$observed_data
+random_data_tidy <- results_list$random_data
+
+ significance_color <- sapply ( is_significant_tidy[,"is_significant"], function(x) {  return(boolean_to_colour(x)) } )
+
+ background_colour <- "white"
+
+	return_plot <- ggplot(random_data_tidy, aes(facet_type, value)) + 
+			geom_boxplot() + 
+			geom_point( data=observed_data_tidy, aes(x=facet_type, y=value  )   ## Add the observed values as additional points
+						, color=significance_color, size=2 , alpha=0.5) 	+ # , size=4 , alpha=0.5
+			xlab( "Percentage of Negative Genetic Interactions") 	+ 
+			ylab( "Counts")  + 
+			facet_grid( key ~., scales="free") +
+			theme( plot.background = element_rect(fill = background_colour, color=background_colour), 
+				   axis.text = element_text(colour = axis_text_colour),
+				   axis.title = element_text(colour = axis_text_colour),
+				   strip.text.y=element_text(face="italic"))
+
+	ggsave(file.path(figures_results_directory, paste( "more_stringent_network_all", figure_file_suffix, sep="") ), 
+	   plot=return_plot, width=graphic_width, 
+	   height=graphic_height*2 )
+
+```

### 2018-01-19 Source/Supplementary_Files/percentage_of_network_analyzed.Rmd
Update paper figures and supplementary materials

---
title: "percentage_of_network_analyzed.Rmd"
author: "Ignatius Pang"
date: "31 August 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries
```{r}
library(dplyr)
library(tibble)
library(tidyr)
```

## Global Parameters
```{r}
local_base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs"
options <- commandArgs(trailingOnly = TRUE)

source( file.path( local_base_directory, "Source/Common/parameters_file.R") ) 
source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))

# data_directory <- "/media/z3371724/PostDoc/2016/Triplet_Motifs/Data/Triplet_Motifs_R_data/"

load( paste(data_directory, "network_data_library.Rdata", sep=""))

triplet_motifs_costanzo <- readRDS( file=paste(data_directory, "triplet_motifs_costanzo_2016.Rdata", sep="") )

filtered_costanzo_stringent <- filtered_costanzo_stringent_2016

colnames( filtered_costanzo_stringent)

significant_types_of_motifs <- c("pp", "tutu" ,"pku" ,"kuku","tdp", "pkd"  )

```

## Get all unique negative genetic interactions

Fact check: The six types of triplet motifs are associated with 80% of the negative genetic interactions present in triplet motifs, and 8% of the known negative genetic interactions.

```{r}

all_negative_gi_helper_a <- filtered_costanzo_stringent[ , c("query_oln_id_edited", "array_oln_id_edited") ] %>%
							dplyr::rename( oln_id_a=query_oln_id_edited) %>%
							dplyr::rename( oln_id_b=array_oln_id_edited)

all_negative_gi_helper_b <- filtered_costanzo_stringent[ , c("query_oln_id_edited", "array_oln_id_edited") ] %>%
							dplyr::rename( oln_id_b=query_oln_id_edited) %>%
							dplyr::rename( oln_id_a=array_oln_id_edited)

all_negative_gi <- dplyr::union  (all_negative_gi_helper_a, all_negative_gi_helper_b ) %>%
					dplyr::distinct() %>%
				   dplyr::filter( oln_id_a >= oln_id_b ) 
```

## how many genes are in the negative genetic interaction network

```{r}
dplyr::union ( all_negative_gi[, "oln_id_b"], all_negative_gi[, "oln_id_a"] ) %>% 
	unique() %>% 
	length()

# as.data.frame(filtered_costanzo_stringent[, "query_oln_id_edited"])  %>% 
# 	rename( array_oln_id_edited=query_oln_id_edited) %>% 
# 	dplyr::union ( as.data.frame(filtered_costanzo_stringent[, "array_oln_id_edited"]) ) %>% 
# 	distinct() %>% 
# 	count()

```

## Get the unique genetic interactions in triplet motifs 
```{r}
all_gi_in_triplet_motifs_helper_a <- triplet_motifs_costanzo[, c("oln_id_a", "oln_id_b", "type_ac", "type_bc")]

all_gi_in_triplet_motifs_helper_b <- triplet_motifs_costanzo[, c("oln_id_b", "oln_id_a", "type_ac", "type_bc")] %>%
										dplyr::rename( temp=oln_id_b) %>%
										dplyr::rename( oln_id_b=oln_id_a)  %>%
										dplyr::rename( oln_id_a=temp)

all_gi_in_triplet_motifs <- dplyr::union ( all_gi_in_triplet_motifs_helper_a, 
										   all_gi_in_triplet_motifs_helper_b) %>%
							dplyr::filter( oln_id_a >= oln_id_b )  %>%
							dplyr::mutate( motif_type = ifelse( type_ac >= type_bc,
																paste (type_ac, type_bc, sep="" ) ,  
																paste (type_bc, type_ac, sep="" ) ) ) %>%
							dplyr::select(one_of( c("oln_id_a", "oln_id_b", "motif_type")))

## In significant triplet motifs 
all_gi_in_sig_triplet_motifs <- all_gi_in_triplet_motifs %>%
								dplyr::filter ( motif_type %in% significant_types_of_motifs ) %>%
								dplyr::select(one_of( c("oln_id_a", "oln_id_b"))) %>%
								dplyr::distinct()

## In all triplet motifs
all_gi_in_triplet_motifs <- all_gi_in_triplet_motifs %>%
							dplyr::select(one_of( c("oln_id_a", "oln_id_b"))) %>%
							dplyr::distinct()

```

## Perform counting 
```{r}
all_gi_in_sig_triplet_motifs_count_check <- dplyr::count( dplyr::intersect ( all_gi_in_sig_triplet_motifs, all_negative_gi))[[1]]

all_gi_in_sig_triplet_motifs_count <- dplyr::count ( all_gi_in_sig_triplet_motifs)[[1]]

if( all_gi_in_sig_triplet_motifs_count_check != all_gi_in_sig_triplet_motifs_count) {
	stop ('Something is wrong with the counts for gi in triplet motifs.')
}

all_gi_in_triplet_motifs_counts <- dplyr::count(all_gi_in_triplet_motifs)[[1]]

all_negative_gi_counts <- dplyr::count( all_negative_gi)[[1]]

print ( "Number of unique negative genetic interactions in total: ")
all_negative_gi_counts

print ( "Number of unique negative genetic interactions in all 15 triplet motifs: ")
all_gi_in_triplet_motifs_counts

print ( "Number of unique genetic interactions in the six overrepresented triplet motifs: ")
all_gi_in_sig_triplet_motifs_count

```

## Calculate fractions
```{r}

print ( "Proportion of unique negative genetic interactions in all 15 triplet motifs: ")
all_gi_in_triplet_motifs_counts/all_negative_gi_counts*100

print ( "Proportion of unique negative genetic interactions in the six overrepresented triplet motifs: ")
all_gi_in_sig_triplet_motifs_count/all_negative_gi_counts*100

print( "Proportion of the unique negative genetic interactions in triplet motifs that are part of significant triplet motifs: ")
all_gi_in_sig_triplet_motifs_count/all_gi_in_triplet_motifs_counts*100
```

## There was one triplet motif that was of the type TUKU
```{r}

triplet_motifs_costanzo %>% 
	dplyr::filter( ( type_ac == 'tu' & type_bc == 'ku' ) |
				   	( type_ac == 'ku' & type_bc == 'tu' )  )

```

## Count negative genetic interactions where either gene is essential
```{r}

essential_genes_edited <- essential_genes %>% dplyr::mutate ( is_essential=1)

## No. of all negative genetic interactions in which either one of the interacting genes are essential
count_ngi_essential <- all_negative_gi %>%
	dplyr::left_join ( essential_genes_edited, by=c("oln_id_a" = "oln_id")) %>%
	dplyr::left_join ( essential_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_essential.x == 1 | is_essential.y == 1) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_essential

## No. of all negative genetic interactions in triplet motifs in which either one of the interacting genes are essential
count_ngi_triplets_essential <- all_gi_in_triplet_motifs %>%
	dplyr::left_join ( essential_genes_edited, by=c("oln_id_a" = "oln_id")) %>%
	dplyr::left_join ( essential_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_essential.x == 1 | is_essential.y == 1) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_triplets_essential

## No. of all negative genetic interactions in significant triplet motifs in which either one of the interacting genes are essential
count_ngi_sig_triplets_essential <- all_gi_in_sig_triplet_motifs  %>%
	dplyr::left_join ( essential_genes_edited, by=c("oln_id_a" = "oln_id")) %>%
	dplyr::left_join ( essential_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_essential.x == 1 | is_essential.y == 1) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_sig_triplets_essential

## No. of all negative genetic interactions in triplet motifs but neither of the protein in the interacting pair are essential
count_ngi_triplets_not_essential <- all_gi_in_triplet_motifs %>%
	dplyr::setdiff ( all_gi_in_triplet_motifs %>%
	dplyr::left_join ( essential_genes_edited, by=c("oln_id_a" = "oln_id")) %>%
	dplyr::left_join ( essential_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_essential.x == 1 | is_essential.y == 1) %>%
	dplyr::select ( oln_id_a, oln_id_b)) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_triplets_not_essential

## Fishers exact test
# Does the negative interacting pair contain at least one protein that is essential = TRUE, is the negative genetic interaction within triplet = TRUE
essential_fisher_exact_test_a <- count_ngi_triplets_essential

# Does the negative interacting pair contain at least one protein that is essential = FALSE, is the negative genetic interaction within triplet = TRUE
essential_fisher_exact_test_b <- count_ngi_triplets_not_essential

# Does the negative interacting pair contain at least one protein that is essential = TRUE, is the negative genetic interaction within triplet = FALSE
essential_fisher_exact_test_c <- count_ngi_essential - count_ngi_triplets_essential

# Does the negative interacting pair contain at least one protein that is essential = FALSE, is the negative genetic interaction within triplet = FALSE

all_genetic_interactions_count <- (all_negative_gi %>% dplyr::count() %>% as.numeric())
essential_fisher_exact_test_d <- all_genetic_interactions_count - essential_fisher_exact_test_a - essential_fisher_exact_test_b - essential_fisher_exact_test_c

essential_matrix <- matrix( c( essential_fisher_exact_test_a, essential_fisher_exact_test_b, 
						       essential_fisher_exact_test_c, essential_fisher_exact_test_d), 2, 2 )

essential_matrix

fisher.test ( essential_matrix)

```

## Count negative genetic interactions where either gene is toxic upon overexpression

```{r}

overexpressed_toxic_genes_edited <- overexpressed_toxic_genes %>% dplyr::mutate ( is_toxic_upon_ox =1)

## No. of all negative genetic interactions in which either one of the interacting genes are toxic upon overexpression
count_ngi_toxic <- all_negative_gi %>%
	dplyr::left_join ( overexpressed_toxic_genes_edited, by=c("oln_id_a" = "oln_id"))%>%
	dplyr::left_join ( overexpressed_toxic_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_toxic_upon_ox.x == 1 | is_toxic_upon_ox.y == 1) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_toxic

## No. of all negative genetic interactions in triplet motifs in which either one of the interacting genes are toxic upon overexpression
count_ngi_triplets_toxic <- all_gi_in_triplet_motifs %>%
	dplyr::left_join ( overexpressed_toxic_genes_edited, by=c("oln_id_a" = "oln_id"))%>%
	dplyr::left_join ( overexpressed_toxic_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_toxic_upon_ox.x == 1 | is_toxic_upon_ox.y == 1) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_triplets_toxic

## No. of all negative genetic interactions in significant triplet motifs in which either one of the interacting genes are toxic upon overexpression
count_ngi_sig_triplets_toxic <- all_gi_in_sig_triplet_motifs  %>%
	dplyr::left_join ( overexpressed_toxic_genes_edited, by=c("oln_id_a" = "oln_id"))%>%
	dplyr::left_join ( overexpressed_toxic_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_toxic_upon_ox.x == 1 | is_toxic_upon_ox.y == 1) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_sig_triplets_toxic

## No. of all negative genetic interactions in triplet motifs but neither of the proteins in the interacting pair are toxic upon overexpression
count_ngi_triplets_not_toxic <- all_gi_in_triplet_motifs %>%
	dplyr::setdiff ( all_gi_in_triplet_motifs %>%
	dplyr::left_join ( overexpressed_toxic_genes_edited, by=c("oln_id_a" = "oln_id"))%>%
	dplyr::left_join ( overexpressed_toxic_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_toxic_upon_ox.x == 1 | is_toxic_upon_ox.y == 1) %>%
	dplyr::select ( oln_id_a, oln_id_b)) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_triplets_not_toxic

## Fishers exact test
# Does the negative interacting pair contain at least one protein that is toxic upon overexpression = TRUE, is the negative genetic interaction within triplet = TRUE
toxic_fisher_exact_test_a <- count_ngi_triplets_toxic

# Does the negative interacting pair contain at least one protein that is toxic upon overexpression = FALSE, is the negative genetic interaction within triplet = TRUE
toxic_fisher_exact_test_b <- count_ngi_triplets_not_toxic

# Does the negative interacting pair contain at least one protein that is toxic upon overexpression = TRUE, is the negative genetic interaction within triplet = FALSE
toxic_fisher_exact_test_c <- count_ngi_toxic - count_ngi_triplets_toxic

# Does the negative interacting pair contain at least one protein that is toxic upon overexpression = FALSE, is the negative genetic interaction within triplet = FALSE

all_genetic_interactions_count <- (all_negative_gi %>% dplyr::count() %>% as.numeric())
toxic_fisher_exact_test_d <- all_genetic_interactions_count - toxic_fisher_exact_test_a - toxic_fisher_exact_test_b - toxic_fisher_exact_test_c

toxic_matrix <- matrix( c( toxic_fisher_exact_test_a, toxic_fisher_exact_test_b, 
						   toxic_fisher_exact_test_c, toxic_fisher_exact_test_d), 2, 2 )

toxic_matrix

fisher.test ( toxic_matrix)

```

## Count negative genetic interactions where either gene is cell-cycle regulated
```{r}

periodically_expressed_genes_edited <- periodically_expressed_genes %>% dplyr::mutate ( is_periodic =1)

## No. of all negative genetic interactions in which either one of the interacting genes are cell-cycle regulated
count_ngi_cell_cycle <- all_negative_gi %>%
	dplyr::left_join ( periodically_expressed_genes_edited, by=c("oln_id_a" = "oln_id"))%>%
	dplyr::left_join ( periodically_expressed_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_periodic.x == 1 | is_periodic.y == 1) %>%
	dplyr::count()  %>%
	as.numeric()

count_ngi_cell_cycle

## No. of all negative genetic interactions in triplet motifs in which either one of the interacting genes are cell-cycle regulated
count_ngi_triplets_cell_cycle <- all_gi_in_triplet_motifs %>%
	dplyr::left_join ( periodically_expressed_genes_edited, by=c("oln_id_a" = "oln_id"))%>%
	dplyr::left_join ( periodically_expressed_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_periodic.x == 1 | is_periodic.y == 1) %>%
	dplyr::count()  %>%
	as.numeric()

count_ngi_triplets_cell_cycle

## No. of all negative genetic interactions in significant triplet motifs in which either one of the interacting genes are cell-cycle regulated
count_ngi_sig_triplets_cell_cycle <- all_gi_in_sig_triplet_motifs  %>%
	dplyr::left_join ( periodically_expressed_genes_edited, by=c("oln_id_a" = "oln_id"))%>%
	dplyr::left_join ( periodically_expressed_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_periodic.x == 1 | is_periodic.y == 1) %>%
	dplyr::count()  %>%
	as.numeric()

count_ngi_sig_triplets_cell_cycle

## No. of all negative genetic interactions in triplet motifs but neither of the proteins in interacting pair are cell-cycle regulated
count_ngi_triplets_not_cell_cycle <- all_gi_in_triplet_motifs %>%
	dplyr::setdiff ( all_gi_in_triplet_motifs %>%
	dplyr::left_join ( periodically_expressed_genes_edited, by=c("oln_id_a" = "oln_id"))%>%
	dplyr::left_join ( periodically_expressed_genes_edited, by=c("oln_id_b" = "oln_id")) %>%
	dplyr::filter ( is_periodic.x == 1 | is_periodic.y == 1) %>%
	dplyr::select ( oln_id_a, oln_id_b)) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_triplets_not_cell_cycle

## Fishers exact test

# Does the negative interacting pair contain at least one periodically expressed gene = TRUE, is the negative genetic interaction within triplet = TRUE
cell_cycle_fisher_exact_test_a <- count_ngi_triplets_cell_cycle

# Does the negative interacting pair contain at least one periodically expressed gene = FALSE, is the negative genetic interaction within triplet = TRUE
cell_cycle_fisher_exact_test_b <- count_ngi_triplets_not_cell_cycle

# Does the negative interacting pair contain at least one periodically expressed gene = TRUE, is the negative genetic interaction within triplet = FALSE
cell_cycle_fisher_exact_test_c <- count_ngi_cell_cycle - count_ngi_triplets_cell_cycle

# Does the negative interacting pair contain at least one periodically expressed gene = FALSE, is the negative genetic interaction within triplet = FALSE
all_genetic_interactions_count <- (all_negative_gi %>% dplyr::count() %>% as.numeric())

cell_cycle_fisher_exact_test_d <- all_genetic_interactions_count - cell_cycle_fisher_exact_test_a - cell_cycle_fisher_exact_test_b - cell_cycle_fisher_exact_test_c

cell_cycle_matrix <- matrix( c( cell_cycle_fisher_exact_test_a, cell_cycle_fisher_exact_test_b, 
						        cell_cycle_fisher_exact_test_c, cell_cycle_fisher_exact_test_d), 2, 2 )

cell_cycle_matrix

fisher.test ( cell_cycle_matrix)

```

## Count negative genetic interactions where both genes are paralogs or ohnologs

```{r}

orthomcl_paralogs <- clean_graph_table  (orthomcl_paralogs,  "oln_id_a", "oln_id_b", directed=FALSE )

sgd_paralogs 	  <- clean_graph_table  (sgd_paralogs,  "oln_id_a", "oln_id_b", directed=FALSE )

orthomcl_paralogs <- dplyr::distinct ( dplyr::union ( orthomcl_paralogs, sgd_paralogs) )

orthomcl_paralogs <- clean_graph_table  (orthomcl_paralogs,  "oln_id_a", "oln_id_b", directed=FALSE )

orthomcl_paralogs_edited <- orthomcl_paralogs %>% dplyr::mutate ( is_paralog =1)

num_of_paralogs_pair <- orthomcl_paralogs_edited %>% dplyr::distinct() %>% dplyr::count() %>% as.numeric()

num_of_paralogs_pair

## No. of all negative genetic interactions in which the interacting pair are paralogs or ohnologs
count_ngi_paralogs <- all_negative_gi %>%
	dplyr::left_join ( orthomcl_paralogs_edited , by = c( "oln_id_a" = "oln_id_b", "oln_id_b" = "oln_id_a")) %>%
	dplyr::left_join ( orthomcl_paralogs_edited , by = c( "oln_id_b" = "oln_id_b", "oln_id_a" = "oln_id_a")) %>%
	dplyr::filter ( is_paralog.x == 1 | is_paralog.y==1 ) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_paralogs

## No. of all negative genetic interactions in triplet motifs in which the interacting pair are paralogs or ohnologs
count_ngi_triplets_paralogs <- all_gi_in_triplet_motifs %>%
	dplyr::left_join ( orthomcl_paralogs_edited , by = c( "oln_id_a" = "oln_id_b", "oln_id_b" = "oln_id_a"))%>%
	dplyr::left_join ( orthomcl_paralogs_edited , by = c( "oln_id_b" = "oln_id_b", "oln_id_a" = "oln_id_a"))%>%
	dplyr::filter ( is_paralog.x == 1 | is_paralog.y==1 ) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_triplets_paralogs

## No. of all negative genetic interactions in the six significant triplet motifs in which the interacting pair are paralogs or ohnologs
count_ngi_sig_triplets_paralogs <- all_gi_in_sig_triplet_motifs  %>%
	dplyr::left_join ( orthomcl_paralogs_edited , by = c( "oln_id_a" = "oln_id_b", "oln_id_b" = "oln_id_a"))%>%
	dplyr::left_join ( orthomcl_paralogs_edited , by = c( "oln_id_b" = "oln_id_b", "oln_id_a" = "oln_id_a"))%>%
	dplyr::filter ( is_paralog.x == 1 | is_paralog.y==1 ) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_sig_triplets_paralogs

## No. of all negative genetic interactions in triplet motifs but the interacting pair are not paralogs or ohnologs
count_ngi_triplets_not_paralogs <- all_gi_in_triplet_motifs %>%
	dplyr::setdiff ( all_gi_in_triplet_motifs %>%
	dplyr::left_join ( orthomcl_paralogs_edited , by = c( "oln_id_a" = "oln_id_b", "oln_id_b" = "oln_id_a"))%>%
	dplyr::left_join ( orthomcl_paralogs_edited , by = c( "oln_id_b" = "oln_id_b", "oln_id_a" = "oln_id_a"))%>%
	dplyr::filter ( is_paralog.x == 1 | is_paralog.y ==1 ) %>%
	dplyr::select ( oln_id_a, oln_id_b)) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_triplets_not_paralogs

## Fishers exact test

# Does the negative interacting pair contain a paralog = TRUE, is the negative genetic interaction within triplet = TRUE
paralog_fisher_exact_test_a <- count_ngi_triplets_paralogs

# Does the negative interacting pair contain a paralog = FALSE, is the negative genetic interaction within triplet = TRUE
paralog_fisher_exact_test_b <- count_ngi_triplets_not_paralogs

# Does the negative interacting pair contain a paralog = TRUE, is the negative genetic interaction within triplet = FALSE
paralog_fisher_exact_test_c <- count_ngi_paralogs - count_ngi_triplets_paralogs

# Does the negative interacting pair contain a paralog = FALSE, is the negative genetic interaction within triplet = FALSE
all_genetic_interactions_count <- (all_negative_gi %>% dplyr::count() %>% as.numeric())
paralog_fisher_exact_test_d <- all_genetic_interactions_count - paralog_fisher_exact_test_a - paralog_fisher_exact_test_b - paralog_fisher_exact_test_c

paralog_matrix <- matrix( c( paralog_fisher_exact_test_a, paralog_fisher_exact_test_b, 
						  paralog_fisher_exact_test_c, paralog_fisher_exact_test_d), 2, 2 )

paralog_matrix

fisher.test ( paralog_matrix)

```

## Negative genetic interactions overlapping with other types of interactions
```{r}

all_interactions <- read.table ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Supplementary_Files/all_interactions.tab", 
 								 header=TRUE, sep="\t", quote="", stringsAsFactors = FALSE)

# Total number of negative genetic interactions
all_interactions %>%
	dplyr::filter( oln_id_a > oln_id_b) %>%
	dplyr::select(one_of( c( "oln_id_a", "oln_id_b", "interaction_type_abbrev" ))) %>%
	dplyr::mutate( count = 1) %>%
	tidyr::spread( "interaction_type_abbrev", "count") %>%
	dplyr::filter( ifelse ( is.na(ng), FALSE,  ng == 1) ) %>%
	dplyr::count() %>%
	as.numeric()

all_genetic_interactions_count <- (all_negative_gi %>% dplyr::count() %>% as.numeric())

# Total number of negative genetic interactions which overlap with at least one other type of interaction 
count_ngi_overlap <- all_interactions %>%
	dplyr::filter( oln_id_a > oln_id_b) %>%
	dplyr::select(one_of( c( "oln_id_a", "oln_id_b", "interaction_type_abbrev" ))) %>%
	dplyr::mutate( count = 1) %>%
	tidyr::spread( "interaction_type_abbrev", "count") %>%
	dplyr::filter(   ifelse ( is.na(ng), FALSE,  ng == 1) & 
					 	( ifelse ( is.na(kd), FALSE, kd >= 1) |
					 	  ifelse ( is.na(ku), FALSE, ku >= 1) |
					 	  ifelse ( is.na(p ), FALSE, p  >= 1) |
					 	  ifelse ( is.na(td), FALSE, td >= 1) |
					 	  ifelse ( is.na(tu), FALSE, tu >= 1)  ) ) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_overlap

# Total number of interactions, including all types of interactions. Overlapping interactions were only counted once.
count_ngi_triplets_overlap <- all_interactions %>%
	dplyr::filter( oln_id_a > oln_id_b & is_part_of_triplet_motif == 1) %>%
	dplyr::select(one_of( c( "oln_id_a", "oln_id_b", "interaction_type_abbrev" ))) %>%
	dplyr::mutate( count = 1) %>%
	tidyr::spread( "interaction_type_abbrev", "count") %>%
	dplyr::filter( ng == 1 & ( 	kd == 1 | ku == 1 | p == 1 | td == 1 | tu == 1) ) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_triplets_overlap

# Total number of interactions where , including all types of interactions. Overlapping interactions were only counted once.
count_ngi_sig_triplets_overlap <- all_interactions %>%
	dplyr::inner_join(all_gi_in_sig_triplet_motifs ) %>%
	dplyr::filter( oln_id_a > oln_id_b & is_part_of_triplet_motif == 1) %>%
	dplyr::select(one_of( c( "oln_id_a", "oln_id_b", "interaction_type_abbrev" ))) %>%
	dplyr::mutate( count = 1) %>%
	tidyr::spread( "interaction_type_abbrev", "count") %>%
	dplyr::filter( ng == 1 & ( 	kd == 1 | ku == 1 | p == 1 | td == 1 | tu == 1) ) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_sig_triplets_overlap

## No. of all negative genetic interactions in triplet motifs but the interacting pair do not overlap with other types of interactions 
count_ngi_triplets_not_overlap <- all_gi_in_triplet_motifs %>%
	dplyr::setdiff ( all_interactions %>%
	dplyr::filter( oln_id_a > oln_id_b & is_part_of_triplet_motif == 1) %>%
	dplyr::select(one_of( c( "oln_id_a", "oln_id_b", "interaction_type_abbrev" ))) %>%
	dplyr::mutate( count = 1) %>%
	tidyr::spread( "interaction_type_abbrev", "count") %>%
	dplyr::filter( ng == 1 & ( 	kd == 1 | ku == 1 | p == 1 | td == 1 | tu == 1) ) %>%
	dplyr::select ( oln_id_a, oln_id_b)) %>%
	dplyr::count() %>%
	as.numeric()

count_ngi_triplets_not_overlap

## Fishers exact test

# Does the negative interacting pair ovelap with other types of interactions = TRUE, is the negative genetic interaction within triplet = TRUE
overlap_fisher_exact_test_a <- count_ngi_triplets_overlap

# Does the negative interacting pair ovelap with other types of interactions = FALSE, is the negative genetic interaction within triplet = TRUE
overlap_fisher_exact_test_b <- count_ngi_triplets_not_overlap

# Does the negative interacting pair ovelap with other types of interactions = TRUE, is the negative genetic interaction within triplet = FALSE
overlap_fisher_exact_test_c <- count_ngi_overlap - count_ngi_triplets_overlap

# Does the negative interacting pair ovelap with other types of interactions = FALSE, is the negative genetic interaction within triplet = FALSE
all_genetic_interactions_count <- (all_negative_gi %>% dplyr::count() %>% as.numeric())
overlap_fisher_exact_test_d <- all_genetic_interactions_count - overlap_fisher_exact_test_a - overlap_fisher_exact_test_b - overlap_fisher_exact_test_c

overlap_matrix <- matrix( c( overlap_fisher_exact_test_a, overlap_fisher_exact_test_b, 
						  overlap_fisher_exact_test_c, overlap_fisher_exact_test_d), 2, 2 )

overlap_matrix

fisher.test ( overlap_matrix)

```

## Calculating the number of paralog pairs that are int tiplets and show a negative interaction: 
I'll need to calculate the number of interactions that overlap with pairs of paralogous proteins. 
```{r}
triplet_motifs_costanzo_2016 <- read.table ( file.path( data_directory, "triplet_motifs_costanzo_2016.txt"), 
											 header =TRUE , stringsAsFactors = FALSE)

gene_a <- as.character( as.vector(c( t(triplet_motifs_costanzo_2016[,1]) ,
									 t(triplet_motifs_costanzo_2016[,1]) , 
									 t(triplet_motifs_costanzo_2016[,2]) ) ))

gene_b <- as.character( as.vector(c( t(triplet_motifs_costanzo_2016[,2]) ,
									 t(triplet_motifs_costanzo_2016[,3])    , 
									 t(triplet_motifs_costanzo_2016[,3]) ) ))

edge_type_attributes <- as.character( as.vector( c( 
		rep( "ng", length(triplet_motifs_costanzo_2016[,1] )),
		t(triplet_motifs_costanzo_2016[, c("type_ac")]),
		t(triplet_motifs_costanzo_2016[, c("type_bc")])
	)  ) )

interactions_from_triplet_motifs_left <- data.frame( oln_id_a = gene_a, oln_id_b = gene_b, type_of_interaction = edge_type_attributes  )

interactions_from_triplet_motifs_right <- data.frame( oln_id_a = gene_b, oln_id_b = gene_a, type_of_interaction = edge_type_attributes  )

interactions_from_triplet_motifs <- interactions_from_triplet_motifs_left %>%
	dplyr::union( interactions_from_triplet_motifs_right) %>%
	dplyr::filter ( oln_id_a > oln_id_b ) %>%
	dplyr::distinct()

interactions_match_paralogs <-  interactions_from_triplet_motifs %>%
								dplyr::left_join( orthomcl_paralogs_edited, by = c( "oln_id_a" = "oln_id_b", "oln_id_b" = "oln_id_a")) %>%
								dplyr::left_join( orthomcl_paralogs_edited, by = c( "oln_id_b" = "oln_id_b", "oln_id_a" = "oln_id_a")) %>%
								dplyr::filter( is_paralog.x ==1 | is_paralog.y==1 ) %>%
								dplyr::distinct()

# all unique pairs of paralogs overlapping biological interactions
paralogs_unique_pairs_overlap_interactions <- interactions_match_paralogs %>%
												dplyr::select ( one_of( c( "oln_id_a", "oln_id_b"))) %>%
												dplyr::distinct()

dplyr::count(paralogs_unique_pairs_overlap_interactions) # 101 pairs

## What do the ones that are not negative genetic interactions consists of:
negative_genetic_interaction_paralog <- interactions_match_paralogs %>% 
										dplyr::filter ( type_of_interaction != "ng" ) %>% 	 
										dplyr::select ( one_of( c( "oln_id_a", "oln_id_b"))) %>%
										dplyr::distinct()

dplyr::count(negative_genetic_interaction_paralog) # 38 rows

other_biological_interactions_paralog <- interactions_match_paralogs %>% 
										 dplyr::filter ( type_of_interaction == "ng" )  %>% 	
										 dplyr::select ( one_of( c( "oln_id_a", "oln_id_b"))) %>%
										 dplyr::distinct()

dplyr::count( other_biological_interactions_paralog ) # 80 rows

# Paris of Paralogs that form negative genetic interactions and other biological interactions: 17 rows
dplyr::intersect( negative_genetic_interaction_paralog, other_biological_interactions_paralog)

80 + 38 - 17 == 101

```

### 2018-01-19 Source/Common/parameters_file.R

@@ -51,6 +51,8 @@ source_directory 		<- "./"
 results_directory 		<- "./"
 source_directory_common <- "./"
 
+
+
 if ( length(options) != 0 &
 	 ! (  options[1] == 'katana' | options[1] == 'clive' | options[1] == 'local'  )  ) {
 	stop ( 'First command line parameter must either by katana, clive, or local') 
@@ -107,6 +109,7 @@ if (is_run_locally == TRUE) {
 	source_directory <- paste( local_base_directory, "Source/", sep="")
 	results_directory <- paste( local_base_directory, "Results/", sep="")
 	source_directory_common <- paste( source_directory, "Common/",  sep="")
+	
 }
 
 source( paste(source_directory_common, "count_triplet_motifs_helper.R", sep="") )

### 2018-01-19 Source/Negative_Genetic_Interactions/count_triplet_motifs_negative_interactions.R

@@ -75,12 +75,12 @@ if (is_run_locally) {
 	
 	if ( use_costanzo_2010_dataset == TRUE) {
 		# Backup all the triplet motifs in the data directory
-		saveRDS( triplet_motifs_costanzo, file=file.path(list_of_triplets_directory, "triplet_motifs_costanzo_2010.Rdata") ) 
-		write.table( triplet_motifs_costanzo, file=file.path(list_of_triplets_directory, "triplet_motifs_costanzo_2010.txt"), row.names=FALSE ) 
+		saveRDS( triplet_motifs_costanzo, file=file.path(data_directory, "triplet_motifs_costanzo_2010.Rdata") ) 
+		write.table( triplet_motifs_costanzo, file=file.path(data_directory, "triplet_motifs_costanzo_2010.txt"), row.names=FALSE ) 
 		
 	} else {
-		saveRDS( triplet_motifs_costanzo, file=file.path(list_of_triplets_directory, "triplet_motifs_costanzo_2016.Rdata") ) 
-		write.table( triplet_motifs_costanzo, file=file.path(list_of_triplets_directory, "triplet_motifs_costanzo_2016.txt"), row.names=FALSE ) 
+		saveRDS( triplet_motifs_costanzo, file=file.path(data_directory, "triplet_motifs_costanzo_2016.Rdata") ) 
+		write.table( triplet_motifs_costanzo, file=file.path(data_directory, "triplet_motifs_costanzo_2016.txt"), row.names=FALSE ) 
 		
 	}
 }

### 2018-01-19 Source/Supplementary_Files/supplementary_files.Rmd
Update paper figures and supplementary materials
Complete Supplementary Table S8 in script format

@@
 
-## Negative Genetic interactions 
+## Supplementary Table S1. Negative Genetic interactions 
 ```{r}
@@
 
-## Protein interaction networks
+## Supplementary Table S2. Protein interaction networks
 ```{r}
@@
 
-## Kinase-substrate network
+## Supplementary Table S3. Kinase-substrate network
 ```{r}
@@
 
-## Transcriptional regulatory network
+## Supplementary Table S4. Transcriptional regulatory network
 ```{r}
@@
 
-## Build phenotype master table 
+## Helper Codes: Build phenotype master table 
 ```{r}
@@
 
-## Paralogs and Ohnologs
+## Supplementary Table S6. Paralogs and Ohnologs
 ```{r}
@@
 
-## All interactions combined together  (part 1)
+## Helper Codes: All interactions combined together  (part 1)
 ```{r}
@@
 
-## Get densely annotated triplets 
+## Table S9.
+The list of all the triplets in the filtered integrated network and triplets with genes that are cell cycle-regulated, essential and toxic on overexpression, and their shared phenotype on knockout and GO slim terms.
 ```{r}
@@
 
-## Interactions that are part of triplets, excluding those that are not part of triplets
+## Helper Codes: Interactions that are part of triplets, excluding those that are not part of triplets
 ```{r}
@@
 
-## All interactions combined together  (part 2)
+## Supplementary Table S7: All interactions combined together  (part 2)
 ```{r}
@@
 ```
+
+## Supplementary Table S8. The number of interactions in the integrated biological network. (Part 1)
+```{r}
+
+## Full Integrated Newtork
+
+# Genetic interactions
+
+all_negative_gi_helper_a <- filtered_costanzo_stringent[ , c("query_oln_id_edited", "array_oln_id_edited") ] %>%
+							dplyr::rename( oln_id_a=query_oln_id_edited) %>%
+							dplyr::rename( oln_id_b=array_oln_id_edited)
+
+all_negative_gi_helper_b <- filtered_costanzo_stringent[ , c("query_oln_id_edited", "array_oln_id_edited") ] %>%
+							dplyr::rename( oln_id_b=query_oln_id_edited) %>%
+							dplyr::rename( oln_id_a=array_oln_id_edited)
+
+all_negative_gi <- dplyr::union  (all_negative_gi_helper_a, all_negative_gi_helper_b ) %>%
+					dplyr::distinct() %>%
+				   dplyr::filter( oln_id_a >= oln_id_b )
+
+# Number of interactions
+all_negative_gi_counts <- dplyr::count( all_negative_gi)[[1]]
+all_negative_gi_counts
+
+# Number of proteins
+ c( all_negative_gi [, "oln_id_a"], all_negative_gi [, "oln_id_b"] ) %>% unique() %>% length()
+
+# Kinase-substrate network
+
+ # Number of interactions
+ kinase_network_filtered %>%
+     dplyr::select (one_of(c("kinase_oln_id", "target_oln_id"))) %>%
+     dplyr::distinct()%>%
+     dplyr::count()
+
+ # Number of proteins
+ c( kinase_network_filtered [, "kinase_oln_id"], kinase_network_filtered [, "target_oln_id"] ) %>% unique() %>% length()
+
+ # Number of kinases 
+ kinase_network_filtered [, "kinase_oln_id"]  %>% unique() %>% length()
+
+ # Protein interaction network
+  # Number of interactions
+ sbi_interactome %>%
+     dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
+     dplyr::filter( oln_id_a > oln_id_b) %>%
+     dplyr::distinct()%>%
+     dplyr::count()
+
+  # Number of proteins
+ c( sbi_interactome [, "oln_id_a"], sbi_interactome [, "oln_id_b"] ) %>% unique() %>% length()
+
+# Transcriptional regulatory network
+
+# Number of interactions
+ tf_network_collated %>%
+    dplyr::filter( interaction_type_abbrev == 'td' ) %>%
+     dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
+     dplyr::distinct()%>%
+     dplyr::count()
+
+# Number of proteins
+ c( tf_network_collated [, "oln_id_a"][[1]], tf_network_collated [, "oln_id_b"][[1]] ) %>% unique() %>% length()
+
+# Number of transcription factors
+ tf_network_collated %>%
+    dplyr::filter( interaction_type_abbrev == 'td' ) %>%
+     dplyr::select (one_of(c("oln_id_a"))) %>%
+     dplyr::distinct()%>%
+     dplyr::count()
+
+# Total Number of Interactions (Unique Pairs of Proteins)
+interactions_combined %>%
+  dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
+  dplyr::filter (oln_id_a > oln_id_b) %>%
+  dplyr::distinct()%>%
+  dplyr::count()
+
+# Total Number of Proteins 
+ c( interactions_combined [, "oln_id_a"], interactions_combined [, "oln_id_b"] ) %>% unique() %>% length()
+
+# Total Number of Interactions (Non-unique pairs and direction)
+interactions_combined %>%
+  dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
+  dplyr::filter (oln_id_a > oln_id_b) %>%
+  dplyr::count()
+
+```
+
+## Supplementary Table S8. The number of interactions in the integrated biological network. (Part 2)
+```{r}
+
+### Filtered Newtork: triplets with a single negative genetic interaction
+
+interactions_from_triplet_motifs_simp <- interactions_from_triplet_motifs %>%
+                                         dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b", "interaction_type_abbrev")))
+
+ ###################
+# Genetic interactions
+
+triplets_negative_gi_helper_a <- interactions_from_triplet_motifs_simp %>%
+                            dplyr::filter(interaction_type_abbrev == "ng" )  %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))
+
+triplets_negative_gi_helper_b <- interactions_from_triplet_motifs_simp %>%
+                            dplyr::filter(interaction_type_abbrev == "ng" )  %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
+              							dplyr::rename( temp=oln_id_a) %>%
+              							dplyr::rename( oln_id_a=oln_id_b) %>%
+                            dplyr::rename( oln_id_b=temp)
+
+triplets_negative_gi <- dplyr::union  (triplets_negative_gi_helper_a, triplets_negative_gi_helper_b ) %>%
+					dplyr::distinct() %>%
+				   dplyr::filter( oln_id_a >= oln_id_b )
+
+# Number of interactions
+triplets_negative_gi_counts <- dplyr::count( triplets_negative_gi)[[1]]
+triplets_negative_gi_counts
+
+# Number of proteins
+ c( triplets_negative_gi [, "oln_id_a"], triplets_negative_gi [, "oln_id_b"] ) %>% unique() %>% length()
+
+ ###################
+# Kinase-substrate network
+
+ kinase_network_filtered_triplets_a <- interactions_from_triplet_motifs_simp %>%
+                            dplyr::filter(interaction_type_abbrev == "kd" )  %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))
+
+  kinase_network_filtered_triplets_b <- interactions_from_triplet_motifs_simp %>%
+                            dplyr::filter(interaction_type_abbrev == "ku" )  %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
+              							dplyr::rename( temp=oln_id_a) %>%
+              							dplyr::rename( oln_id_a=oln_id_b) %>%
+                            dplyr::rename( oln_id_b=temp)
+
+  kinase_network_filtered_triplets <- dplyr::union  (kinase_network_filtered_triplets_a, kinase_network_filtered_triplets_b ) %>%
+					dplyr::distinct()
+
+ # Number of interactions
+ kinase_network_filtered_triplets  %>%
+     dplyr::distinct()%>%
+     dplyr::count()
+
+ # Number of proteins
+ c( kinase_network_filtered_triplets [, "oln_id_a"], kinase_network_filtered_triplets [, "oln_id_b"] ) %>% unique() %>% length()
+
+ # Number of kinases 
+ kinase_network_filtered_triplets [, "oln_id_a"]  %>% unique() %>% length()
+
+ ###################
+ # Protein interaction network
+  sbi_interactome_triplets_a <- interactions_from_triplet_motifs_simp %>%
+                            dplyr::filter(interaction_type_abbrev == "p" )  %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))
+
+  sbi_interactome_triplets_b <- interactions_from_triplet_motifs_simp %>%
+                            dplyr::filter(interaction_type_abbrev == "p" )  %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
+              							dplyr::rename( temp=oln_id_a) %>%
+              							dplyr::rename( oln_id_a=oln_id_b) %>%
+                            dplyr::rename( oln_id_b=temp)
+
+  sbi_interactome_triplets <- dplyr::union  (sbi_interactome_triplets_a, sbi_interactome_triplets_b ) %>%
+					                    dplyr::distinct() %>%
+				                      dplyr::filter( oln_id_a > oln_id_b )
+
+  # Number of interactions
+ sbi_interactome_triplets  %>%
+     dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
+     dplyr::filter( oln_id_a > oln_id_b) %>%
+     dplyr::distinct()%>%
+     dplyr::count()
+
+  # Number of proteins
+ c( sbi_interactome_triplets [, "oln_id_a"], sbi_interactome_triplets [, "oln_id_b"] ) %>% unique() %>% length()
+
+# Transcriptional regulatory network
+
+  tf_network_collated_triplets_a <- interactions_from_triplet_motifs_simp %>%
+                            dplyr::filter(interaction_type_abbrev == "td" )  %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))
+
+  tf_network_collated_triplets_b <- interactions_from_triplet_motifs_simp %>%
+                            dplyr::filter(interaction_type_abbrev == "tu" )  %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
+              							dplyr::rename( temp=oln_id_a) %>%
+              							dplyr::rename( oln_id_a=oln_id_b) %>%
+                            dplyr::rename( oln_id_b=temp)
+
+  tf_network_collated_triplets <- dplyr::union  (tf_network_collated_triplets_a, tf_network_collated_triplets_b ) %>%
+					dplyr::distinct()
+
+# Number of interactions
+ tf_network_collated_triplets %>%
+     dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
+     dplyr::distinct()%>%
+     dplyr::count()
+
+# Number of proteins
+ c( tf_network_collated_triplets [, "oln_id_a"], tf_network_collated_triplets [, "oln_id_b"] ) %>% unique() %>% length()
+
+# Number of transcription factors
+ tf_network_collated_triplets %>%
+     dplyr::select (one_of(c("oln_id_a"))) %>%
+     dplyr::distinct()%>%
+     dplyr::count()
+
+# Total Number of Interactions (Unique Pairs of Proteins)
+  interactions_from_triplet_motifs_simp_a <- interactions_from_triplet_motifs_simp %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))
+
+  interactions_from_triplet_motifs_simp_b <- interactions_from_triplet_motifs_simp %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
+              							dplyr::rename( temp=oln_id_a) %>%
+              							dplyr::rename( oln_id_a=oln_id_b) %>%
+                            dplyr::rename( oln_id_b=temp)
+
+  unique_interactions_from_triplet_motifs <- dplyr::union  (interactions_from_triplet_motifs_simp_a, interactions_from_triplet_motifs_simp_b ) %>%
+					dplyr::distinct()  %>%
+				  dplyr::filter( oln_id_a > oln_id_b )
+
+ unique_interactions_from_triplet_motifs %>%
+  dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
+  dplyr::distinct() %>%
+  dplyr::count()
+
+# Total Number of Proteins 
+ c( unique_interactions_from_triplet_motifs [, "oln_id_a"], unique_interactions_from_triplet_motifs [, "oln_id_b"] ) %>% unique() %>% length()
+
+# Total Number of Interactions (Non-unique pairs and direction)
+ triplets_negative_gi %>% 
+ dplyr::bind_rows( kinase_network_filtered_triplets ) %>%
+ dplyr::bind_rows(sbi_interactome_triplets ) %>%
+ dplyr::bind_rows( tf_network_collated_triplets ) %>%
+  dplyr::count()
+
+```

### 2018-01-20 Source/Supplementary_Files/supplementary_files.Rmd
Update README file, parameters file, and codes for supplementary files

@@
 
+## Import Libraries
 ```{r}
@@
 ```
+
+## Codes for Supplementary Figures S1-4 can be found in the following file: Source/Figures/paper_figures.Rmd
 
@@
 
-## Helper Codes: Build phenotype master table 
+## Supplementary Table S5: Build phenotype master table 
 ```{r}
@@
 
-## Table S9.
+## Supplementary Table S9.
 The list of all the triplets in the filtered integrated network and triplets with genes that are cell cycle-regulated, essential and toxic on overexpression, and their shared phenotype on knockout and GO slim terms.
@@
   # Number of interactions
- sbi_interactome %>%
+ sbi_interactome_collated %>%
      dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
-     dplyr::filter( oln_id_a > oln_id_b) %>%
+     dplyr::filter( oln_id_a >= oln_id_b) %>%
      dplyr::distinct()%>%
@@
   # Number of proteins
- c( sbi_interactome [, "oln_id_a"], sbi_interactome [, "oln_id_b"] ) %>% unique() %>% length()
+ c( sbi_interactome_collated [, "oln_id_a"][[1]], sbi_interactome_collated [, "oln_id_b"][[1]] ) %>% unique() %>% length()
 
@@
 # Total Number of Interactions (Unique Pairs of Proteins)
-interactions_combined %>%
+  interactions_combined_a <- interactions_combined %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))
+
+  interactions_combined_b <- interactions_combined %>%
+                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
+              							dplyr::rename( temp=oln_id_a) %>%
+              							dplyr::rename( oln_id_a=oln_id_b) %>%
+                            dplyr::rename( oln_id_b=temp)
+
+  unique_interactions_combined <- dplyr::union  (interactions_combined_a, interactions_combined_b ) %>%
+					dplyr::distinct()  %>%
+				  dplyr::filter( oln_id_a >= oln_id_b )
+
+ unique_interactions_combined %>%
   dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
-  dplyr::filter (oln_id_a > oln_id_b) %>%
-  dplyr::distinct()%>%
+  dplyr::distinct() %>%
   dplyr::count()
@@
 interactions_combined %>%
-  dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
-  dplyr::filter (oln_id_a > oln_id_b) %>%
+  dplyr::select (one_of(c("oln_id_a", "oln_id_b", "interaction_type_abbrev"))) %>%
+  dplyr::filter (oln_id_a >= oln_id_b) %>%
+    dplyr::filter ( !(oln_id_a == oln_id_b & interaction_type_abbrev == "tu") ) %>%
+    dplyr::filter ( !(oln_id_a == oln_id_b & interaction_type_abbrev == "ku") ) %>%
+  dplyr::distinct() %>%
   dplyr::count()
@@
 ```
+
+## Supplementary Table S10
+Results for Supplementary Table S10 can be found in the following file: Results/Bootstrap_p_values/Negative_Genetic_Interactions/Final_Results/full_results_triplet_motifs_costanzo_2016_collated.tab
+
+## Supplementary Table S11
+Codes for Supplementary Table S11 can be found in the following R Notebook (in the same directory as this script): Source/Supplementary_Files/percentage_of_network_analyzed.Rmd

### 2018-01-20 Source/Common/parameters_file.R

@@ -31,27 +31,47 @@ sessionInfo()
 #  script.R <compute location (katana|clive|local)>  <array job ID> <number of randomized trials>
 
 #########################################################
-### Parameters 
-
-is_run_locally 			     <- TRUE
-array_job_id 			     <- NULL 
-random_number_seed 		     <- 1985
-number_of_cores_to_use 		 <- 24
-number_of_randomized_trials  <- 100
-num_iteration_rewire_network <- NULL # Number of times each network is rewired before counting the triplet motifs.
-									 # If null, this is equal to the number of edges in the network. 
-use_costanzo_2010_dataset 	 <- FALSE
-
-
+## Default directories
 local_base_directory  <-  "/home/ignatius/PostDoc/2016/Triplet_Motifs/"
-
-
 data_directory 			<- "./"
 source_directory 		<- "./"
 results_directory 		<- "./"
 source_directory_common <- "./"
 
+######################################################################
+### ***************************************************************###
+### IMPORTANT PARAMETERS TO SETUP BEFORE USING ANY OF THE SCRIPTS  ###
+### ***************************************************************###
+######################################################################
 
+is_run_locally 			         <- TRUE
+array_job_id 			           <- NULL 
+random_number_seed 		       <- 1985
+number_of_cores_to_use 		   <- 24
+number_of_randomized_trials  <- 100
+num_iteration_rewire_network <- NULL # Number of times each network is rewired before counting the triplet motifs.
+									 # If null, this is equal to the number of edges in the network. 
+use_costanzo_2010_dataset 	 <- FALSE
+
+if ( length(options) != 0 
+     & ( options[1] == 'katana' | options[1] == 'clive')  ) {
+  is_run_locally <- FALSE
+}
+
+## Deal with parameters with the code are to be ran locally
+if (is_run_locally == TRUE) {
+  random_number_seed <- 1985
+  number_of_cores_to_use <- 4
+  number_of_randomized_trials <- 4
+  num_iteration_rewire_network <- 0.001 # Number of times each network is rewired before counting the triplet motifs
+  
+  data_directory <- paste( local_base_directory, "Data/Triplet_Motifs_R_data/", sep="")
+  source_directory <- paste( local_base_directory, "Source/", sep="")
+  results_directory <- paste( local_base_directory, "Results/", sep="")
+  source_directory_common <- paste( source_directory, "Common/",  sep="")
+}
+
[…]

### 2018-02-13 Source/Figures/paper_figures.Rmd
paper figures minor update
Update figures

@@
 
-local_base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source"
+local_base_directory <- "/home/ignatius/PostDoc/2017/Triplet_Motifs/Source"
 source( file.path( local_base_directory, "./Common/parameters_file.R") ) 
@@
 
-motif_types_sorted_by_counts_desc <- c( "PP", "TUTU", "TDP", "PKU",  "KUKU",  "PKD",  
-										"PTU", "KDKU", "TDTD", "KDKD", "TDTU", "TUKD", "TDKD", "TDKU", "TUKU" )
-
-stat_test_result_random_edges <- stat_test_result_random_edges %>%
-								 dplyr::mutate( motif_type = factor(motif_type, levels = rev(motif_types_sorted_by_counts_desc) ), 
-								 			   is_significant_star = ifelse( is_significant==1, "*", "")  )
-
 ggplot(stat_test_result_random_edges, aes(y= motif_type, x= parameter )) +

### 2018-02-13 Source/Common/parameters_file.R

@@ -32,7 +32,7 @@ sessionInfo()
 
 #########################################################
 ## Default directories
-local_base_directory  <-  "/home/ignatius/PostDoc/2016/Triplet_Motifs/"
+local_base_directory  <-  "/home/ignatius/PostDoc/2017/Triplet_Motifs/"
 data_directory 			<- "./"
 source_directory 		<- "./"
 results_directory 		<- "./"
